\documentclass[12pt,dvipdfmx]{article}



\usepackage{epsf}
\oddsidemargin 0. true cm
\topmargin -1 true cm
\textheight 24 true cm
\textwidth 16 true cm


\usepackage{color}
\pagecolor{white}
\setcounter{secnumdepth}{1}
\usepackage{times}

\usepackage[unicode=true,
% \usepackage[hypertex], % use for activating links in DVI file
 dvipdfmx, % use for bookmarks in final (pdf) version
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=true,
 breaklinks=false,pdfborder={0 0 0},backref=false,colorlinks=true]
 {hyperref}
\hypersetup{pdftitle={HYDHEL Documentation},linkcolor=blue, citecolor=blue, urlcolor=blue, filecolor=blue}
 \usepackage{bookmark} % use only together with dvipdfm option of hyperref package!




\begin{document}
\parindent 0pt
%titelpage
{\LARGE \bf \center
\vspace*{3truecm}

The data file HYDHEL: \\
Atomic and Molecular Data for EIRENE \\
based upon: Janev, Langer, Evans, Post, \\
``Elementary
Processes in Hydrogen-Helium Plasmas", \\
Springer 1987
\vspace*{3truecm}

D. Reiter \\
FZJ, Forschungszentrum J\"ulich GmbH \\
52425 J\"ulich \\
%Post-box 1917 \\
Germany
\vspace{3truecm}

Version: \today
\vspace{1truecm}

Available via E-mail from d.reiter@fz-juelich.de, or as part of the
EIRENE code git-repository hosted at FZ J\"ulich
}
\pagenumbering{Roman}
\newpage
\renewcommand\thesection{\Roman{section}}
\newpage
\addcontentsline{toc}{section}{Table of contents}
\tableofcontents
%ende titelpage
\newpage
\section{Errata, list of modifications as compared to the original 1987 book \cite{kn:Janev87}}
%\addcontentsline{toc}{section}{Errata, list of modifications}

A first set of corrections, errata, modifications was published by Reiter et al,
in \cite{kn:Reiter92}.
Most of them are also contained in the following, more comprehensive list.
\begin{itemize}
\item{Reaction 2.2.5}

The cross section and rate coefficients for this reaction are about a
factor 3 too low. This error has been introduced between the draft version and
the final printed version of the book in 1987. Here we have corrected this error,
i.e., the fit coefficients from the (unpublished) draft version of the book are
given here, whereas the erroneous fit coefficients from the printed version
of the book are retained in the database AMJUEL, (reaction 2.2.5o), for reference
purposes.
\item{Reaction 3.1.8}

The cross section H.1, 3.1.8 has been improved by adding
the low energy extrapolation coefficients.

The fit H.3, 3.1.8 has been replaced with a better one, such that
it becomes more consistent with the cross section H.1 3.1.8.
This leads to significantly improved energy balance in case of
tracklength estimators for the CX energy loss.

The original fits from the 1987 book have been kept in file amjuel.tex,
under H.3, 3.1.8org

In Aug. 2017 the cross section fit was further improved. It had a tiny remaining discontinuity
at E=0.1 eV, which is now removed.
\item{Feb 2013}

Some reaction and species formulas in section headers slightly changed to permit automated CR
model construction (species and reaction type identification) for HYDKIN online tool
\item{Mar 2013}

Added: H.1 (cross sections): \textbf{\emph{Eth}} (threshold energy), used for online plots and Maxwellian rate integration

Added: H.1 (cross sections) \textbf{\emph{Mcross}} (Mass as used in energy scale. Electron mass (kg), or heavy particle mass, (AMU).)

\item{Reaction 2.1.3}

cross section and reaction rate of electron-impact process 2.1.3 (Chibisov) are both
a factor 10 too small.
Also Chibisov analytic formula for cross section given in 1987 book:
factor 10 too small.
Not yet corrected here in fits.
(Can be done by a modification of coefficients $a_0$ and $b_0$)
The corresponding proton-impact data (3.1.3) seem to be correct.

\item{Reaction 2.2.13}

The cross section and rate coefficient plotted on page 61 of the 1987 version of the book are both by
a factor 10 too large.
The fitting coefficients for  cross section and rate coefficient appear to be correct, however.

\item{Reaction 3.1.7}

The BEA cross section formula given in text give cross section results that are by a factor 4 too small,
due to a corresponding error in numerical factors given (page 126)

\item{Reaction 7.3.1}

Both the cross section and rate coefficient for this reaction are incorrect, by several orders of magnitude.
Do not use these data !

\item{Reaction 2.1.8}

In the original book a closed form expression is given for the radiative recombination rate coefficients for protons
into the \emph{nl} states of H atom. Added in Jan. 2014:  H.2 rate coefficient polynomial fitting of these rate coefficients, for recombination into
$1s, 2s$ and $2p$ states, to allow
automated processing with same format as for other cross sections and rate coefficients in this data-base

\item{June 2015: H.2 for Reaction 3.1.8}

A single parameter fit: H.2  3.1.8 is added, vs. proton temperature only and for ``stationary" H(1s). It has been derived
algebraically from the H.3 fit, evaluated at
E=0.1 eV, and this procedure was verified by independent Maxwellian averaging
of the asymptotically correct cross section fit H.1  3.1.8, (vs. E)
The mass used on the temperature scale is the proton mass.

\item{July 2015-I}

Some state notations, in particular for He excited states in section headers slightly changed to permit automated CR
model construction (species and reaction type identification) for HYDKIN online tool. Notation also now consistent with
AMJUEL He CR model data.

\item{July 2015-II,  2.2.14}

Reaction 2.2.14: In AMJUEL the reaction fits for H.1 and H.2 are reduced to be linear in log-log scale and hence $\ln \sigma(E) = a_0 + a_1 \ln(T)$ and $\ln \langle\sigma v\rangle(T) = b_0 + b_1 \ln(T)$, respectively,
because higher non-
zero coefficients in original book \cite{kn:Janev87} seem to be spurious for this reaction. In this simpler (AMJUEL) form for the rate coefficient H.2 the corresponding H.8 fit
is exact: $\ln \langle\sigma v E_{elec}\rangle(T) = h_0 +h_1 \ln(T)$ with $h_0 = b_0+\ln(3/2+b_1)$ and $h_1=b_1+1$, see H.8  2.2.14 in AMJUEL.
An independently computed H.8 fit using a table from the full H.2 rate fit is still retained in the present HYDHEL file here, (formerly at AMJUEL H.8),
for backward compatibility

\item{Sept. 2015: state notation for process 2.3.4b: final state notation was wrong.}
Now corrected

\item{Jan 16: asymptotically better cross sections for some processes.}
Reaction H.1:  3.3.2,  3.3.6a,  3.3.6b, 6.2.1,  6.3.1  fitted to a wider energy range, asymptotically correct
at high collision energies.
The corresponding new cross sections are labeled: 3.3.2n, 3.3.6an 3.3.6bn, 6.2.1n and 6.3.1n

\item{H.8  2.2.14 added here, consistent with H.2 2.2.14 dissociative. recomb.}
A better representation is given in AMJUEL. from the linearity on a log-log scale exact consistency
can be achieved, and is stored there, and is also the hard coded EIRENE default for process 2.2.14

\item{Feb 16 added for various cross sections: ELABMAX and high energy end extrapolation:
H.1:  3.1.1, 3.1.2, 3.1.6, 3.1.8, 3.1.9, 3.1.11b, 3.2.1b, 3.2.4a, 3.2.5, 3.2.6, 3.3.1, 3.3.6a, 3.3.6b,
4.2.1, 4.3.1, 4.3.3,  4.4.1, 5.2.3, 6.1.6, and 7.2.2}

\item{May 2016: H.2  3.2.3}
added: H.2 for 3.2.3. same as earlier done (June 15) for 3.1.8: thermal rate coefficient, evaluated at Eb =0.1 eV $\approx 0.0$ eV
Ebmin of H.3 fit for 3.2.3 is about 0.1 eV.

\item{May 2016 H.2 2.2.10 and 2.2.12:}

Process 2.2.12, starting from bound state H$_2^+$, is not contained in two step process 2.2.10,
which starts from H$_2$,
because in 2.2.10 the transition from H$_2$ to H + H$^+$ proceeds either via the repulsive part
of the H$_2^+$ ground state,
or by direct transition from H$_2$ to the first excited H$_2^+$  B state, without an intermediate bound H$_2^+$ state.
\end{itemize}

\section{to be done}
%\addcontentsline{toc}{section}{to be done}

\begin{itemize}
\item {2.1.8  and 2.3.13 missing fits for H.2 rate coeffs. (for stationary (E0=0.0) beam)}

\item {H.2 rad rec coeff:}

In original monograph only closed form analytic expressions are given for H+ and He+ rad rec. rate coefficients.
(and nothing for the cross sections).
2.1.8, 2.1.8a and 2.1.8b fits for H.2 rad rec rate coefficients had already been added earlier (see list of changes/errata in previous section).
The same is needed still for
2.3.13 (helium rad. rec), in particular since the closed form
expression from the book is hard wired as default recombination rate in EIRENE code for He$^+$.

Perhaps the closed form expression allows a direct (analytical)
translation into polynomial fit?
It seems to be the case indeed from
the new 2.1.8 fits that only two coefficients may be needed.
No: two different slopes Te**s at low Te and at high Te. Cannot be accomodated
by a single fit which is linear in log-log scale.

\item {H.8 rates for recombination processes}

for the closed form expressions for 2.1.8 and 2.3.13 these rates can be given also in closed form (and are coded in
the EIRENE default A\&M model routines). It might be desirable to add them also as H.8
into the database. Same for 2.2.14 (diss. rec of H2+).
This latter is already here in HYDHEL (update from July 2015),
and EIRENE default was 0.88*Te times rate 2.2.14.
So the H.8  2.2.14 was approximately, but not exactly, the previous EIRENE default.
The H.8 fit can not be derived from the H.2 fit exactly.
H.8 follows from H.2 directly, if only the b0 and b1 coefficients in the H.2 fit are non-zero, see: AMJUEL.tex
For 2.2.14: Change EIRENE default (H.2 and H.8) to that 2 parameter fit
from AMJUEL for H.8, Done.

In Sept. 18  a fit for recombination: H.8 2.1.8 has been added, using only the first 2 coefficients b0 and b1 from
the corresponding H.2 fit. (In an attempt to mimik the closed form analytical default model in EIRENE):
However: in case of process 2.1.8 this turns out to be unsatisfactory.
Apparently the higher coefficients in H.2, although small, matter, to provide the
T**-3/2 decay of the rate at high Te (rather than the near T**-1/2 decay at low Te.


\item{process 2.2.15 is linear in log log scale. }

Check coefficients, make H.8, set spurious coeffs. to zero
\item{H.2  5.3.1 and 6.3.1 to be added, at Eb=0.1}

m\_lab=4,  but m\_reduced=2 for these processes
\item {Maxrate: sigma * v\_lab }

started to implement the maximum of product sigma * v\_lab,
for heavy particle process cross sections:
Done for 7.2.2
\item{corrections from 1992 PSI paper (Reiter, Bogen, Samm, \cite{kn:Reiter92})}

various KER values....

\end{itemize}
\newpage

This next string is searched by EIRENE in subroutine SLREAC
to initialize search for a particular set of fit coefficients.

\bigskip
\begin{small}\begin{verbatim}
...........................................
.                                         .
.       ##BEGIN DATA HERE##               .
.                                         .
...........................................
\end{verbatim}\end{small}
\newpage
\renewcommand{\theHsection}{arabicsection.\thesection}
\renewcommand\thesection{\arabic{section}}
%\renewcommand{\thesection}{\arabic{section}}
%\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}
%\renewcommand{\thesubsubsection}{\thesection.\thesubsection.\arabic{subsubsection}}
\pagenumbering{arabic}
\setcounter{section}{0}

\section{H.1  FITS FOR $\sigma$}

\subsection{
Reaction 2.1.1 $   e + H(1s) \rightarrow e + H(2p) $}


\begin{small}\begin{verbatim}
   a0 -4.991816994666e+02    a1  6.320402753550e+02    a2 -3.652213752597e+02
   a3  1.165699645892e+02    a4 -2.250557133404e+01    a5  2.695101794905e+00
   a6 -1.958839549072e-01    a7  7.917154881015e-03    a8 -1.365267533573e-04
       Emin  1.08e+01   s(Emin)  1.00e-19   smax  7.50e-17   Error  2.36e-01
       Eth 10.2
       Mcross 9.1093826E-31


       aBorn,1= 1.68301e-16  nBorn,1= 8.44454e-01

       Emin  1.08e+01    s(Emin)  1.00e-19    Error  5.16e-01



       aBorn,2= 2.08151e-16  nBorn,2= 9.18070e-01

       Emin  1.08e+01    s(Emin)  1.00e-19    Error  3.95e-01
\end{verbatim}\end{small}


\newpage
\subsection{
Reaction 2.1.2 $   e + H(1s) \rightarrow e + H(2s) $}

\begin{small}\begin{verbatim}
   a0 -1.773223143614e+03    a1  2.868021256119e+03    a2 -2.019174875577e+03
   a3  7.913558639288e+02    a4 -1.890880793711e+02    a5  2.824418882926e+01
   a6 -2.579116350676e+00    a7  1.318146425812e-01    a8 -2.890652428531e-03
       Emin  1.08e+01   s(Emin)  1.00e-19   smax  1.91e-17   Error  3.00e-01
       Eth 10.2
       Mcross 9.1093826E-31
\end{verbatim}\end{small}



\newpage
\subsection{
Reaction 2.1.3 $   e + H(2s) \rightarrow e + H(2p)$}


\begin{small}\begin{verbatim}
   a0 -3.015144307129e+01    a1 -8.929446571004e-01    a2 -5.730368414517e-03
   a3  4.111473087803e-04    a4 -3.370055284368e-05    a5  2.817934394179e-06
   a6 -1.944521853229e-07    a7  8.570956054828e-09    a8 -1.688382595819e-10
       Emin  1.00e-01   s(Emin)  6.06e-13   smax  6.06e-13   Error  1.75e-10
       Eth 1.934e-5
       Mcross 9.1093826E-31

          A more extensive analytic formula is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.1.4 $   e + H(n) \rightarrow e + H(m)  (m > n, m \neq 2)$}

\begin{small}\begin{verbatim}
          An analytic formula is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.1.5 $   e + H(1s) \rightarrow e + H^+ + e$}



\begin{small}\begin{verbatim}
   a0 -7.778213049931e+02    a1  9.540190857268e+02    a2 -5.227766973807e+02
   a3  1.592701052833e+02    a4 -2.952557198074e+01    a5  3.413024145539e+00
   a6 -2.405520814365e-01    a7  9.465181268476e-03    a8 -1.594325350979e-04
       Emin  1.43e+01   s(Emin)  1.00e-19   smax  7.15e-17   Error  1.11e-01
        Eth 13.6
        Mcross 9.1093826E-31


       aBorn,1= 1.53753e-16  nBorn,1= 8.61942e-01

       Emin  1.43e+01    s(Emin)  1.00e-19    Error  8.84e-01



       aBorn,2= 2.34616e-16  nBorn,2= 1.02119e+00

       Emin  1.43e+01    s(Emin)  1.00e-19    Error  5.01e-01

\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 2.1.6 $   e + H(2s) \rightarrow e + H^+ + e$}



\begin{small}\begin{verbatim}
   a0 -1.323829114032e+02    a1  1.651239202115e+02    a2 -1.140121644712e+02
   a3  4.230980472378e+01    a4 -9.296147227462e+00    a5  1.243911606504e+00
   a6 -9.947722917370e-02    a7  4.367280737208e-03    a8 -8.092922245217e-05
       Emin  3.58e+00   s(Emin)  1.00e-19    smax  8.30e-16   Error  2.93e-01
        Eth 3.4
        Mcross 9.1093826E-31


       aBorn,1= 1.87046e-15  nBorn,1= 8.93875e-01

       Emin  3.58e+00    s(Emin)  1.00e-19    Error  7.51e-01



       aBorn,2= 2.57396e-15  nBorn,2= 1.01823e+00

       Emin  3.58e+00    s(Emin)  1.00e-19    Error  7.62e-01


\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.1.7 $   e + H(n=3) \rightarrow e + H^+ + e$}



\begin{small}\begin{verbatim}
   a0 -5.210905240460e+01    a1  4.541756148570e+01    a2 -3.994563990284e+01
   a3  1.774554892576e+01    a4 -4.490170942194e+00    a5  6.717581547587e-01
   a6 -5.875054514668e-02    a7  2.774373803025e-03    a8 -5.460792035331e-05
       Emin  1.55e+00   s(Emin)  1.00e-19   smax  5.76e-15   Error  5.89e-01
       Eth  1.5111
       Mcross 9.1093826E-31

       A more extensive analytic formula for all n > 2 is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.2.1a $   e + H_2(v=0) \rightarrow e + H_2(v=1)$}



\begin{small}\begin{verbatim}
   a0 -4.063959689566e+01    a1  1.636189705461e+01    a2 -3.342841685940e+01
   a3  3.479549344686e+01    a4 -2.082704506646e+01    a5  7.301916128338e+00
   a6 -1.477679988432e+00    a7  1.596127782326e-01    a8 -7.118499383243e-03
       Emin  8.95e-01   s(Emin)  1.00e-19   smax  4.79e-17   Error  3.82e-02
       Eth  0.5
       Mcross 9.1093826E-31
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.2.1b $   e + H_2(v=0) \rightarrow e + H_2(v=2)$}



\begin{small}\begin{verbatim}
   a0 -4.401593275820e+01    a1 -5.428337849062e+00    a2  2.781894563620e+01
   a3 -3.059898206514e+01    a4  1.618430684710e+01    a5 -4.799622608369e+00
   a6  8.162961901622e-01    a7 -7.445555845412e-02    a8  2.825425451852e-03
       Emin  1.38e+00   s(Emin)  1.00e-19   smax  8.61e-18   Error  7.10e-04
       Eth  1.0
       Emax 3.0E+02
       Mcross 9.1093826E-31

       Not valid for E < 1.1 or E > 300 eV.
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 2.2.2 $e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2(B^1\Sigma_u^+2p\sigma)$}






%        1 +         *  1 +
%e + H (X S ) T e + H (B S 2ps)
%     2    g         2    u








\begin{small}\begin{verbatim}
   a0 -4.293519441750e+02    a1  5.112210939087e+02    a2 -2.848127939455e+02
   a3  8.831033879636e+01    a4 -1.665959177505e+01    a5  1.957960915869e+00
   a6 -1.401282416514e-01    a7  5.591134833381e-03    a8 -9.537010324465e-05
       Emin  1.25e+01   s(Emin)  1.00e-19   smax  2.94e-17   Error  1.04e-01
       Eth  11.37
       Mcross 9.1093826E-31


       aBorn,1= 1.10665e-17  nBorn,1= 8.08245e-01

       Emin  1.38e+00    s(Emin)  1.00e-19    Error  1.52e+00



       aBorn,2= 4.71632e-17  nBorn,2= 1.37760e+00

       Emin  1.38e+00    s(Emin)  1.00e-19    Error  1.86e+00
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 2.2.3 $e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2(C^1\Pi_u2p\pi) $}






%        1 +         *  1
%e + H (X S ) T e + H (C < 2p!)
%     2    g         2    u








\begin{small}\begin{verbatim}
   a0 -8.194268487911e+02    a1  9.870509999996e+02    a2 -5.309554319119e+02
   a3  1.591702330888e+02    a4 -2.912103674573e+01    a5  3.332102780153e+00
   a6 -2.330596118299e-01    a7  9.119178195801e-03    a8 -1.529895022672e-04
       Emin  1.58e+01   s(Emin)  1.00e-19   smax  3.80e-17   Error  1.18e-01
        Eth  11.7
        Mcross 9.1093826E-31


       aBorn,1= 6.74162e-17  nBorn,1= 8.01562e-01

       Emin  1.58e+01    s(Emin)  1.00e-19    Error  4.64e-01



       aBorn,2= 1.15646e-16  nBorn,2= 1.00587e+00

       Emin  1.58e+01    s(Emin)  1.00e-19    Error  1.15e+00
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.2.4 $e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2(E,F^1\Sigma_g^+)$}






%        1 +         *    1 +
%e + H (X S ) T e + H (E,F S )
%     2    g         2      g








\begin{small}\begin{verbatim}
   a0 -1.285300373043e+03    a1  1.791037396609e+03    a2 -1.109180722424e+03
   a3  3.858482892334e+02    a4 -8.239751178005e+01    a5  1.105885445011e+01
   a6 -9.113361334764e-01    a7  4.218997111854e-02    a8 -8.407951365268e-04
       Emin  1.65e+01   s(Emin)  1.00e-19   smax  4.77e-18   Error  2.51e-02
       Eth  12.2
       Mcross 9.1093826E-31
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.2.5 $e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2(b^3\Sigma_u^+, a^3\Sigma_g^+, c^3\Pi_u) \rightarrow e + H(1s) + H(1s)$}






%        1 +         *  3 +   3 +       3
%e + H (X S ) T e + H (b S , a S , and c < )
%     2    g         2    u     g         u
%
%             T e + H(1s) + H(1s)








\begin{small}\begin{verbatim}
   a0 -1.019870329452e+05    a1  2.252601430192e+05    a2 -2.158143676206e+05
   a3  1.171042848075e+05    a4 -3.936494849617e+04    a5  8.395340835067e+03
   a6 -1.109486871647e+03    a7  8.308421522823e+01    a8 -2.699781210407e+00
       Emin  1.08e+01   s(Emin)  1.00e-19   smax  8.84e-17   Error  5.39e-01
       Eth  8.5
       Mcross 9.1093826E-31
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.2.6 $e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2(1s\sigma_g,nl\lambda|^1\Lambda) \rightarrow e +  H(1s) + H(2s)$}






%        1 +         *          1                  *
%e + H (X S ) T e + H (1ss ,nPg| G) T e + H(1s) + H (2s)
%     2    g         2    g










\begin{small}\begin{verbatim}
   a0 -1.157041752123e+03    a1  1.501936271844e+03    a2 -8.611938700508e+02
   a3  2.754926257351e+02    a4 -5.380465012731e+01    a5  6.573972423327e+00
   a6 -4.912318139657e-01    a7  2.054926773000e-02    a8 -3.689035889972e-04
       Emin  1.65e+01   s(Emin)  1.00e-19   smax  1.64e-17   Error  1.12e-01
        Eth  14.9
        Mcross 9.1093826E-31

       aBorn,1= 3.90596e-17  nBorn,1= 9.29053e-01

       Emin  1.65e+01    s(Emin)  1.00e-19    Error  3.41e-01



       aBorn,2= 4.72962e-17  nBorn,2= 1.00759e+00

       Emin  1.65e+01    s(Emin)  1.00e-19    Error  2.72e-01
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 2.2.7 $ e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2(2p\sigma_u, nl\lambda|Q_2^1\Pi_u) \rightarrow e + H(2p) + H(2s)$}






%        1 +         *            1           *        *
%e + H (X S ) T e + H (2ps ;nPg|Q  < ) T e + H (2p) + H (2s)
%     2    g         2    u      2  u










\begin{small}\begin{verbatim}
   a0 -2.057786420733e+04    a1  2.950256031919e+04    a2 -1.831052572622e+04
   a3  6.414232477826e+03    a4 -1.387462186158e+03    a5  1.898300554210e+02
   a6 -1.604843781908e+01    a7  7.667894395976e-01    a8 -1.585946768503e-02
       Emin  2.88e+01   s(Emin)  1.00e-19   smax  3.19e-18   Error  1.73e-02
        Eth  23.0
        Mcross 9.1093826E-31


       aBorn,1= 1.14191e-17  nBorn,1= 1.29810e+00

       Emin  2.88e+01    s(Emin)  1.00e-19    Error  9.63e-02



       aBorn,2= 1.05756e-17  nBorn,2= 1.25115e+00

       Emin  2.88e+01    s(Emin)  1.00e-19    Error  7.37e-02
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.2.8 $e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2(2p\sigma_u;n=3) \rightarrow e + H(1s) + H(n=3)$}






%        1 +         *                           *
%e + H (X S ) T e + H (2ps ; n=3) T e + H(1s) + H (n=3)
%     2    g         2    u










\begin{small}\begin{verbatim}
   a0 -3.287645365957e+03    a1  5.014406168806e+03    a2 -3.348881857725e+03
   a3  1.262084567851e+03    a4 -2.934110683163e+02    a5  4.308239201745e+01
   a6 -3.902409019508e+00    a7  1.994401403354e-01    a8 -4.405117731369e-03
       Emin  1.90e+01   s(Emin)  1.00e-19   smax  1.79e-18   Error  5.54e-03
        Eth  19.0
        Mcross 9.1093826E-31


       aBorn,1= 4.23517e-18  nBorn,1= 9.45107e-01

       Emin  1.90e+01    s(Emin)  1.00e-19    Error  1.02e-01



       aBorn,2= 6.12160e-18  nBorn,2= 1.10089e+00

       Emin  1.90e+01    s(Emin)  1.00e-19    Error  1.17e-01

\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.2.9 $e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2^+(v) + e$}






%        1 +         +
%e + H (X S ) T e + H (v) + e
%     2    g         2










\begin{small}\begin{verbatim}
   a0 -1.387609624141e+03    a1  1.699141305899e+03    a2 -9.108411850551e+02
   a3  2.719534700245e+02    a4 -4.949789923430e+01    a5  5.628121884179e+00
   a6 -3.908551117391e-01    a7  1.517692897197e-02    a8 -2.526183660091e-04
       Emin  1.87e+01   s(Emin)  1.00e-19   smax  1.11e-16   Error  1.94e-01
        Eth  15.4
        Mcross 9.1093826E-31


       aBorn,2= 3.58910e-16  nBorn,2= 1.01326e+00

       Emin  1.87e+01    s(Emin)  1.00e-19    Error  7.46e-01

\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.2.10 $e + H_2(X^1\Sigma_g^+) \rightarrow e + [H_2^+(\Sigma_g, \Sigma_u) + e] \rightarrow e + H^+ + H(1s) + e$}






%         1 +          +                        +
%e  + H (X S ) T e + [H (S  and S ) + e] T e + H  + H(1s) + e
%      2    g          2  g      u










\begin{small}\begin{verbatim}
   a0 -3.833822745947e+03    a1  5.694871055047e+03    a2 -3.683040395270e+03
   a3  1.338526896657e+03    a4 -2.988408134179e+02    a5  4.197687137005e+01
   a6 -3.624797562843e+00    a7  1.760638946986e-01    a8 -3.685905968490e-03
       Emin  2.11e+01   s(Emin)  1.00e-19   smax  5.75e-18   Error  2.17e-02

       Eth  18.0
       Mcross 9.1093826E-31
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 2.2.11 $e + H_2^+(v) \rightarrow e + H^+ + H^+ + e, (v=0\ldots 9)$}






%     +           +    +
%e + H (v) T e + H  + H  + e   (v=0-9)
%     2








\begin{small}\begin{verbatim}
   a0 -7.175166253949e+02    a1  8.527284836302e+02    a2 -4.615650223553e+02
   a3  1.402626692658e+02    a4 -2.611719315325e+01    a5  3.047273508837e+00
   a6 -2.175218173132e-01    a7  8.689141623830e-03    a8 -1.488365280435e-04
       Emin  1.79e+01   s(Emin)  1.00e-19   smax  1.74e-17   Error  2.37e-02
       Eth  14.7
       Mcross 9.1093826E-31
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.2.12 $e + H_2^+(v) \rightarrow e + H_2^+(2p\sigma_u) \rightarrow e + H^+ + H(1s), (v=0\ldots 9)$}






%     +           +*              +
%e + H (v) T e + H  (2ps ) T e + H  + H(1s), (v = 0 - 9)
%     2           2     u








\begin{small}\begin{verbatim}
   a0 -8.734971153234e+01    a1  1.018145800541e+02    a2 -7.763161913681e+01
   a3  3.095286370113e+01    a4 -7.178129093553e+00    a5  1.001376002948e+00
   a6 -8.276605899370e-02    a7  3.731813613454e-03    a8 -7.068946002778e-05
       Emin  2.70e+00   s(Emin)  1.00e-19   smax  1.01e-15   Error  6.04e-01
       Eth  2.4
       Mcross 9.1093826E-31
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.2.13 $ e + H_2^+(v) \rightarrow e + H_2^+(2p\pi_u) \rightarrow e + H^+ + H(n=2),  (v=0\ldots 9)$}



\begin{small}\begin{verbatim}
   a0 -1.261570316476e+03    a1  1.600546555479e+03    a2 -8.875792683132e+02
   a3  2.730297710707e+02    a4 -5.103300875879e+01    a5  5.943996543464e+00
   a6 -4.220104525394e-01    a7  1.672668012176e-02    a8 -2.838410215959e-04
       Emin  1.44e+01   s(Emin)  1.00e-19   smax 5.06e-17   Error 4.05e-02
        Eth  14.0
        Mcross 9.1093826E-31

       aBorn,1= 1.35488e-16  nBorn,1= 1.04143e+00

       Emin  1.44e+01   s(Emin)  1.00e-19  Error 4.20e-01



       aBorn,2= 1.38216e-16  nBorn,1= 1.04143e+00

       Emin  1.44e+01   s(Emin)  1.00e-19  Error 4.20e-01

\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.2.14 $   e + H_2^+(v) \rightarrow H(1s) + H(n), (v=0\ldots 9, n\geq 2)$}



\begin{small}\begin{verbatim}
   a0 -3.479249259777e+01    a1 -1.103564847459e+00    a2 -1.817595501089e-13
   a3  1.913718292296e-13    a4 -8.296778314084e-15    a5 -3.945007662626e-14
   a6  1.480375530361e-14    a7 -2.096231848232e-15    a8  1.067937159826e-16
       Emin  1.00e-01   s(Emin)  9.85e-15   smax  9.85e-15   Error  1.74e-25
       Eth  0.0
       Mcross 9.1093826E-31
\end{verbatim}\end{small}


\newpage
\subsection{
Reaction 2.2.15 $   e + H_3^+ \rightarrow  H + H + H$ or $\rightarrow H_2(v > 5) + H(n=2)$}





\begin{small}\begin{verbatim}
   a0 -3.497403537065e+01    a1 -9.050073352581e-01    a2 -6.875577121635e-13
   a3  1.212286779103e-13    a4  1.320680420105e-13    a5 -6.368710212825e-14
   a6  1.136465595184e-14    a7 -9.184755712215e-16    a8  2.814743077081e-17
       Emin  1.00e-01   s(Emin)  5.20e-15   smax  5.20e-15   Error  1.12e-24
       Eth  0.0
       Mcross 9.1093826E-31
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 2.2.16 $ e + H_3^+ \rightarrow e + H^+ + 2H$}



\begin{small}\begin{verbatim}
   a0 -1.180802127731e+03    a1  1.469242595864e+03    a2 -8.010903182743e+02
   a3  2.427879961198e+02    a4 -4.477455604823e+01    a5  5.150533546464e+00
   a6 -3.613881605497e-01    a7  1.416168832727e-02    a8 -2.376509206426e-04
       Emin  1.65e+01   s(Emin)  1.00e-19   smax  7.36e-16   Error  5.22e-01
        Eth  14.0
        Mcross 9.1093826E-31


       aBorn,1= 1.38785e-15  nBorn,1= 7.41773e-01

       Emin  1.65e+01    s(Emin)  1.00e-19    Error  9.17e-01



       aBorn,2= 1.75195e-15  nBorn,2= 8.18483e-01

       Emin  1.65e+01    s(Emin)  1.00e-19    Error  9.58e-01

\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.2.17 $   e + H_2(v \geq 4) \rightarrow (H_2^-) \rightarrow H^- + H$}



\begin{small}\begin{verbatim}
   a0 -3.533068072400e+01    a1 -1.305146001161e+00    a2 -5.402400752335e-01
   a3 -1.929128735755e-01    a4 -3.998229471894e-01    a5 -2.442412657121e-01
   a6  7.577527589687e-03    a7  4.268454076562e-02    a8  9.029646852927e-03
       Emin  1.00e-01   s(Emin)  8.94e-16   smax  1.03e-15   Error  6.40e-04

    Eth  0.1
    Emax 5.0E+00
    Mcross 9.1093826E-31

            Not valid for E > 5 eV.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.1a $e + He(1s^21S) \rightarrow e + He(1s^12p^11P)$}






%         2 1            *      1
%e + He(1s | S) T e  + He (1s2p| P)
%










\begin{small}\begin{verbatim}
   a0 -1.035570462579e+03    a1  1.215931704603e+03    a2 -6.359454827397e+02
   a3  1.861198276080e+02    a4 -3.333317507125e+01    a5  3.741542708002e+00
   a6 -2.572201220135e-01    a7  9.910988972511e-03    a8 -1.640390854438e-04
       Emin  2.18e+01   s(Emin)  1.00e-19   smax  9.79e-18   Error  3.00e-02
        Eth  21.217
        Mcross 9.1093826E-31


       aBorn,1= 1.92235e-17  nBorn,1= 7.83233e-01

       Emin  2.18e+01    s(Emin)  1.00e-19    Error  1.78e-01



       aBorn,2= 2.57557e-17  nBorn,2= 8.83509e-01

       Emin  2.18e+01    s(Emin)  1.00e-19    Error  1.03e-01

            A more extensive analytic formula for transition to (1snl|1P) is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.1b $e + He(1s^21S) \rightarrow e + He(1s^13p^11P)$}






%         2 1           *      1
%e + He(1s | S) T e + He (1s3p| P)











\begin{small}\begin{verbatim}
   a0 -2.634840114580e+03    a1  3.509384108909e+03    a2 -2.045577442205e+03
   a3  6.707125167844e+02    a4 -1.352829871406e+02    a5  1.719155337173e+01
   a6 -1.344786986986e+00    a7  5.923822227197e-02    a8 -1.125813888453e-03
       Emin  2.50e+01   s(Emin)  1.00e-19   smax  2.35e-18   Error  1.62e-02
        Eth  23.086
        Mcross 9.1093826E-31


       aBorn,1= 4.99196e-18  nBorn,1= 8.11369e-01

       Emin  2.50e+01    s(Emin)  1.00e-19    Error  1.08e-01



       aBorn,2= 6.56234e-18  nBorn,2= 9.07863e-01

       Emin  2.50e+01    s(Emin)  1.00e-19    Error  9.15e-02

            A more extensive analytic formula for transition to (1snl|1P) is given in the text.
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 2.3.2 $e + He(1s^21S) \rightarrow e + He(1s^12s^11S)$}






%         2 1           *      1
%e + He(1s | S) T e + He (1s2s| S)











\begin{small}\begin{verbatim}
   a0 -1.340229681600e+04    a1  2.117221297932e+04    a2 -1.450345815377e+04
   a3  5.610930330567e+03    a4 -1.341090060181e+03    a5  2.028369172741e+02
   a6 -1.896426422663e+01    a7  1.002440728214e+00    a8 -2.294532805220e-02
       Emin  2.17e+01   s(Emin)  1.00e-19   smax  2.72e-18   Error  1.23e-01
        Eth  20.614
        Mcross 9.1093826E-31


       aBorn,1= 1.16605e-17  nBorn,1= 1.52195e+00

       Emin  2.17e+01    s(Emin)  1.00e-19    Error  2.30e-01



       aBorn,2= 1.01757e-17  nBorn,2= 1.42944e+00

       Emin  2.17e+01    s(Emin)  1.00e-19    Error  1.68e-01

       An analytic formula for s for transition to this and
       other nl|1L states is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.3a $e + He(1s^21S) \rightarrow e + He(1s^12s^13S)$}






%         2 1           *      3
%e + He(1s | S) T e + He (1s2s| S)











\begin{small}\begin{verbatim}
   a0 -5.203190079746e+07    a1  1.114126390950e+08    a2 -1.041333130230e+08
   a3  5.549110256155e+07    a4 -1.843990770358e+07    a5  3.912927216807e+06
   a6 -5.177965474575e+05    a7  3.906790796143e+04    a8 -1.286793467718e+03
       Emin  2.17e+01   s(Emin)  1.00e-19   smax  3.08e-18   Error  3.46e-01
        Eth  19.818
        Mcross 9.1093826E-31

       This fit is not recommended.



       aBorn,1= 2.57061e-17  nBorn,1= 4.07784e+00




                               17



       Emin  2.17e+01    s(Emin)  1.00e-19    Error  6.90e-01



       aBorn,2= 4.23197e-17  nBorn,2= 5.18074e+00

       Emin  2.17e+01    s(Emin)  1.00e-19    Error  1.32e+00

       An analytic formula for s for transition to this and other nl|3L states is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.3b $e + He(1s^21S) \rightarrow e + He(1s^12p^13P)$}






%         2 1           *      3
%e + He(1s | S) T e + He (1s2p| P)











\begin{small}\begin{verbatim}
   a0 -4.793169045161e+06    a1  9.882446793715e+06    a2 -8.888886013658e+06
   a3  4.555681859005e+06    a4 -1.455138589620e+06    a5  2.966235458426e+05
   a6 -3.768463275632e+04    a7  2.728166188657e+03    a8 -8.616903005294e+01
       Emin  2.17e+01   s(Emin)  1.00e-19   smax  2.89e-18   Error  1.70e-01
        Eth  20.936
        Mcross 9.1093826E-31


       aBorn,1= 1.87693e-17  nBorn,1= 2.84919e+00

       Emin  2.17e+01    s(Emin)  1.00e-19    Error  6.02e-01



       aBorn,2= 2.73848e-17  nBorn,2= 3.37724e+00

       Emin  2.17e+01    s(Emin)  1.00e-19    Error  6.43e-01

       An analytic formula for s for transition to this and other nl|3L states is given in the text.
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 2.3.3c $e + He(1s^21S) \rightarrow e + He(1s^13s^13S)$}






%         2 1           *      3
%e + He(1s | S) T e + He (1s3s| S)











\begin{small}\begin{verbatim}
   a0 -4.788014731830e+08    a1  1.022518413821e+09    a2 -9.540217735841e+08
   a3  5.079285422983e+08    a4 -1.687812725605e+08    a5  3.584473999432e+07
   a6 -4.751258664024e+06    a7  3.593838762943e+05    a8 -1.187665518764e+04
       Emin  2.50e+01   s(Emin)  1.00e-19   smax  8.49e-19   Error  9.16e-02
        Eth  22.717
        Mcross 9.1093826E-31

       This fit is not recommended.



       aBorn,1= 6.73891e-18  nBorn,1= 3.38203e+00

       Emin  2.50e+01    s(Emin)  1.00e-19    Error  2.57e-01



       aBorn,2= 8.73337e-18  nBorn,2= 3.82261e+00

       Emin  2.50e+01    s(Emin)  1.00e-19    Error  3.10e-01

       An analytic formula for s for transition to this and other (nl|3L) states is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.3d $e + He(1s^21S) \rightarrow e + He(1s^13p^13P)$}






%         2 1           *      3
%e + He(1s | S) T e + He (1s3p| P)











\begin{small}\begin{verbatim}
   a0 -3.936065650971e+07    a1  8.116028811410e+07    a2 -7.306391247418e+07
   a3  3.750824079156e+07    a4 -1.200982299576e+07    a5  2.456048818627e+06
   a6 -3.132802195794e+05    a7  2.278831373521e+04    a8 -7.237641204949e+02
       Emin  2.50e+01   s(Emin)  1.00e-19   smax  1.62e-18   Error  1.85e-01
        Eth  23.006
        Mcross 9.1093826E-31

       This fit is not recommended.



       aBorn,1= 1.32373e-17  nBorn,1= 3.41922e+00

       Emin  2.50e+01    s(Emin)  1.00e-19    Error  3.91e-01



       aBorn,2= 1.67554e-17  nBorn,2= 3.81681e+00

       Emin  2.50e+01    s(Emin)  1.00e-19    Error  4.46e-01

       An analytic formula for s for transition to this and other nl|3L states is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.4a $e + He(1s^12s^13S) \rightarrow e + He(1s^12s^11S)$}






%      *      3           *      1
%e + He (1s2s| S) T e + He (1s2s| S)











\begin{small}\begin{verbatim}
   a0 -3.767284614946e+01    a1  1.242374777500e+01    a2 -1.733730671197e+01
   a3  1.065193441154e+01    a4 -3.545021903004e+00    a5  6.760042577381e-01
   a6 -7.381907066438e-02    a7  4.291139737209e-03    a8 -1.029193004464e-04
       Emin  8.96e-01   s(Emin)  1.00e-19   smax  6.14e-16   Error  4.84e-01
        Eth 0.796
        Mcross 9.1093826E-31


       aBorn,1= 2.18988e-15  nBorn,1= 1.34842e+00

       Emin  8.96e-01    s(Emin)  1.00e-19    Error  1.14e+00



       aBorn,2= 2.23252e-15  nBorn,2= 1.36293e+00

       Emin  8.96e-01    s(Emin)  1.00e-19    Error  1.23e+00

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}







\newpage
\subsection{
Reaction 2.3.4b $e + He(1s^12s^13S) \rightarrow e + He(1s^12p^11P)$}






%      *      3           *      1
%e + He (1s2s| S) T e + He (1s2p| P)











\begin{small}\begin{verbatim}
   a0 -5.319933965992e+01    a1  4.744554023140e+01    a2 -4.844985223676e+01
   a3  2.500468700294e+01    a4 -7.374551620285e+00    a5  1.290076459738e+00
   a6 -1.322635763531e-01    a7  7.335813534997e-03    a8 -1.698321860588e-04
       Emin  1.56e+00   s(Emin)  1.00e-19   smax  3.07e-16   Error  4.17e-01
        Eth  1.399
        Mcross 9.1093826E-31

       aBorn,1= 1.10118e-15  nBorn,1= 1.35219e+00

       Emin  1.56e+00    s(Emin)  1.00e-19    Error  9.62e-01



       aBorn,2= 1.11692e-15  nBorn,2= 1.36330e+00

       Emin  1.56e+00    s(Emin)  1.00e-19    Error  1.02e+00

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.4c $e + He(1s^12s^11S) \rightarrow e + He(1s^12p^13P)$}






%      *      1           *      3
%e + He (1s2s| S) T e + He (1s2p| P)











\begin{small}\begin{verbatim}
   a0 -3.317860766309e+01    a1 -5.306038723803e-01    a2 -2.695255954243e+00
   a3  2.632267872941e+00    a4 -1.099156687924e+00    a5  2.377305480208e-01
   a6 -2.790496421908e-02    a7  1.688187005669e-03    a8 -4.125774276276e-05
       Emin  3.90e-01   s(Emin)  1.00e-19   smax  2.41e-15   Error  6.04e-01
        Eth  0.349
        Mcross 9.1093826E-31

       aBorn,1= 8.65146e-15  nBorn,1= 1.35184e+00

       Emin  3.90e-01    s(Emin)  1.00e-19    Error  1.57e+00



       aBorn,2= 8.78111e-15  nBorn,2= 1.36352e+00

       Emin  3.90e-01    s(Emin)  1.00e-19    Error  1.67e+00

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.4d $e + He(1s^12p^13P) \rightarrow e + He(1s^12p^11P)$}






%      *      3           *      1
%e + He (1s2p| P) T e + He (1s2p| P)











\begin{small}\begin{verbatim}
   a0 -3.550958147337e+01    a1 -2.148096190520e+00    a2  3.301727694779e-01
   a3  1.489817873888e+00    a4 -1.281057689191e+00    a5  4.334863480750e-01
   a6 -7.269238026113e-02    a7  6.015845378859e-03    a8 -1.962092219181e-04
       Emin  2.62e-01   s(Emin)  1.00e-19   smax  4.39e-16   Error  2.60e-01
        Eth  0.254
        Mcross 9.1093826E-31

       aBorn,1= 1.62992e-15  nBorn,1= 1.37522e+00

       Emin  2.62e-01    s(Emin)  1.00e-19    Error  1.37e+00



       aBorn,2= 1.59075e-15  nBorn,2= 1.36145e+00

       Emin  2.62e-01    s(Emin)  1.00e-19    Error  1.29e+00

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}







\newpage
\subsection{
Reaction 2.3.5a $   e + He(1s^12s^11S) \rightarrow e + He(1s^12p^11P)$}





\begin{small}\begin{verbatim}
   a0 -3.325138159927e+01    a1  6.965673711167e+00    a2 -9.102522690164e+00
   a3  5.178880611636e+00    a4 -1.570251042131e+00    a5  2.686249148763e-01
   a6 -2.602715945748e-02    a7  1.332101581144e-03    a8 -2.797505613652e-05
       Emin  6.77e-01   s(Emin)  1.00e-19   smax  1.44e-14   Error  7.36e-01
        Eth  0.602
        Mcross 9.1093826E-31

       aBorn,2= 4.26417e-14  nBorn,2= 8.79209e-01

       Emin  6.87e-01    s(Emin)  1.00e-19    Error  1.56e+00

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.5b $   e + He(1s^12s^13S) \rightarrow e + He(1s^12p^13P)$}





\begin{small}\begin{verbatim}
   a0 -4.190861763587e+01    a1  2.589117787777e+01    a2 -2.543442341964e+01
   a3  1.224262304780e+01    a4 -3.287256784979e+00    a5  5.142698379467e-01
   a6 -4.655881399807e-02    a7  2.259789810984e-03    a8 -4.548031395449e-05
       Emin  1.15e+00   s(Emin)  1.00e-19   smax  7.52e-15   Error  5.53e-01
        Eth  1.145
        Mcross 9.1093826E-31

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.6a $   e + He(1s^12s^11S) \rightarrow e + He(1s^13p^11P)$}





\begin{small}\begin{verbatim}
   a0 -7.945340796384e+01    a1  7.952123040074e+01    a2 -5.901873964305e+01
   a3  2.336041841867e+01    a4 -5.418217641105e+00    a5  7.574234290606e-01
   a6 -6.273863245111e-02    a7  2.833779484304e-03    a8 -5.374700574749e-05
       Emin  2.72e+00   s(Emin)  1.00e-19   smax  2.68e-16   Error  2.62e-01
        Eth  2.472
        Mcross 9.1093826E-31

       An analytic formula for s for transition to this and other np|1P states is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.6b $  e + He(1s^12s^13S) \rightarrow e + He(1s^13p^13P)$}





\begin{small}\begin{verbatim}
   a0 -8.720058224600e+01    a1  8.669127167337e+01    a2 -6.125632963824e+01
   a3  2.323452528088e+01    a4 -5.206449941296e+00    a5  7.082705099324e-01
   a6 -5.741257577852e-02    a7  2.548456501150e-03    a8 -4.765136776607e-05
       Emin  3.14e+00   s(Emin)  1.00e-19   smax  7.66e-17   Error  1.61e-01
        Eth  3.188
        Mcross 9.1093826E-31

       aBorn,2= 1.95245e-16  nBorn,2= 8.39781e-01

       Emin  3.14e+00    s(Emin)  1.00e-19    Error  5.55e-01

       An analytic formula for s for transition to this and other np|3P states is given in the text.
\end{verbatim}\end{small}









\newpage
\subsection{
Reaction 2.3.7a $e + He(1s^12p^11P) \rightarrow e + He(1s^13d^11D)$}






%      *      1           *      1
%e + He (1s2p| P) T e + He (1s3d| D)











\begin{small}\begin{verbatim}
   a0 -6.380148486246e+01    a1  6.207791717177e+01    a2 -5.009739526736e+01
   a3  2.108909461860e+01    a4 -5.130498771379e+00    a5  7.448846309387e-01
   a6 -6.362451646494e-02    a7  2.947637642636e-03    a8 -5.710909679690e-05
       Emin  2.05e+00   s(Emin)  1.00e-19   smax  2.73e-15   Error  6.02e-01
        Eth  1.856
        Mcross 9.1093826E-31

       aBorn,2= 7.85272e-15  nBorn,2= 8.59826e-01

       Emin  2.05e+00    s(Emin)  1.00e-19    Error  1.21e+00

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.7b $e + He(1s^12p^13P) \rightarrow e + He(1s^13d^13D)$}






%      *      3           *      3
%e + He (1s2p| P) T e + He (1s3d| D)











\begin{small}\begin{verbatim}
   a0 -7.355382422374e+01    a1  7.757733939986e+01    a2 -6.021028662561e+01
   a3  2.456897613696e+01    a4 -5.830267812736e+00    a5  8.299661528547e-01
   a6 -6.978241370066e-02    a7  3.191768833116e-03    a8 -6.118911403921e-05
       Emin  2.35e+00   s(Emin)  1.00e-19   smax  2.01e-15   Error  5.79e-01
        Eth  2.109
        Mcross 9.1093826E-31

       aBorn,2= 5.69936e-15  nBorn,2= 8.78100e-01

       Emin  2.35e+00    s(Emin)  1.00e-19    Error  1.12e+00

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.9 $   e + He(1s^21S) \rightarrow e + He^+(1s) + e$}




\begin{small}\begin{verbatim}
   a0 -1.864515653677e+03    a1  2.200039160012e+03    a2 -1.13502043008e+03
   a3  3.275368136458e+02    a4 -5.782773248653e+01    a5  6.398861014578e+00
   a6 -4.337092983841e-01    a7  1.647885719077e-02    a8 -2.690038700620e-04
       Emin  2.50e+01   s(Emin)  1.00e-19   smax  3.75e-17   Error  5.25e-02
        Eth  24.588
        Mcross 9.1093826E-31

       aBorn,2= 2.66551e-15  nBorn,2= 1.02404e+00

       Emin  5.45e+00    s(Emin)  1.00e-19    Error  8.86e-01
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.10a $ e + He(1s^12s^11S) \rightarrow e + He^+(1s) + e$}





\begin{small}\begin{verbatim}
   a0 -1.588165958608e+02    a1  2.025096794972e+02    a2 -1.359677027927e+02
   a3  4.931464639049e+01    a4 -1.062291122924e+01    a5  1.397102480527e+00
   a6 -1.100503977820e-01    a7  4.767747225791e-03    a8 -8.732475392853e-05
       Emin  4.11e+00   s(Emin)  1.00e-19   smax  8.05e-16   Error  4.12e-01
        Eth 3.973
        Mcross 9.1093826E-31

       aBorn,1= 1.76528e-15  nBorn,1= 8.45023e-01

       Emin  4.11e+00    s(Emin)  1.00e-19    Error  8.55e-01



       aBorn,2= 2.22317e-15  nBorn,2= 9.31407e-01

       Emin  4.11e+00    s(Emin)  1.00e-19    Error  6.68e-01

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}







\newpage
\subsection{
Reaction 2.3.10b $e + He(1s^12p^11P) \rightarrow e + He^+(1s) + e$}






%      *      1           +
%e + He (1s2p| P) T e + He (1s) + e











\begin{small}\begin{verbatim}
   a0 -1.307379836148e+02    a1  1.632174408167e+02    a2 -1.129614525216e+02
   a3  4.199589716864e+01    a4 -9.233643615441e+00    a5  1.235205673096e+00
   a6 -9.868890735893e-02    a7  4.326993699443e-03    a8 -8.006280122436e-05
       Emin  3.58e+00   s(Emin)  1.00e-19   smax  1.14e-15   Error  3.47e-01
        Eth  3.371
        Mcross 9.1093826E-31

       aBorn,1= 2.44771e-15  nBorn,1= 8.44077e-01

       Emin  3.58e+00    s(Emin)  1.00e-19    Error  1.02e+00



       aBorn,2= 3.10641e-15  nBorn,2= 9.33260e-01

       Emin  3.58e+00    s(Emin)  1.00e-19    Error  8.13e-01

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.10c $e + He(1s^12s^13S) \rightarrow e + He^+(1s) + e$}






%      *      3           +
%e + He (1s2s| S) T e + He (1s) + e











\begin{small}\begin{verbatim}
   a0 -2.339247199323e+02    a1  3.108263537901e+02    a2 -2.004035199806e+02
   a3  7.013664348852e+01    a4 -1.464607997646e+01    a5  1.875537708304e+00
   a6 -1.443996329241e-01    a7  6.134194672052e-03    a8 -1.104612714554e-04
       Emin  5.45e+00   s(Emin)  1.00e-19   smax  9.37e-16   Error  5.07e-01
        Eth  4.769
        Mcross 9.1093826E-31

       aBorn,1= 2.44417e-15  nBorn,1= 9.85122e-01

       Emin  5.45e+00    s(Emin)  1.00e-19    Error  8.95e-01



       aBorn,2= 2.66551e-15  nBorn,2= 1.02404e+00

       Emin  5.45e+00    s(Emin)  1.00e-19    Error  8.86e-01

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.10d $e + He(1s^12p^13P) \rightarrow e + He^+(1s) + e$}






%      *      3           +
%e + He (1s2p| P) T e + He (1s) + e








\begin{small}\begin{verbatim}
   a0 -1.514909720389e+02    a1  1.917899987253e+02    a2 -1.291695579859e+02
   a3  4.694225725512e+01    a4 -1.012623462168e+01    a5  1.333169086771e+00
   a6 -1.050969063989e-01    a7  4.555911465700e-03    a8 -8.348482513741e-05
       Emin  4.14e+00   s(Emin)  1.00e-19   smax  9.85e-16   Error  4.18e-01
        Eth  3.625
        Mcross 9.1093826E-31

       aBorn,1= 2.09009e-15  nBorn,1= 8.39105e-01

       Emin  4.14e+00    s(Emin)  1.00e-19    Error  1.16e+00



       aBorn,2= 2.72108e-15  nBorn,2= 9.37659e-01

       Emin  4.14e+00    s(Emin)  1.00e-19    Error  9.35e-01

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}









\newpage
\subsection{
Reaction 2.3.12 $e + He(1s^1nl^1  \{2S+1\}L) \rightarrow e + He^+(nl)+e$}






%      *      2S+1           +*
%e + He (1snP|    L) T e + He  (nP) + e











\begin{small}\begin{verbatim}
   a0 -2.149046249050e+04    a1  2.587653680045e+04    a2 -1.349616963351e+04
   a3  3.975822003764e+03    a4 -7.236994991416e+02    a5  8.336945178595e+01
   a6 -5.937449760897e+00    a7  2.390910599514e-01    a8 -4.169354418025e-03
       Emin  5.71e+01   s(Emin)  1.00e-19   smax  1.10e-17   Error  1.27e-01
        Eth 54.4
        Mcross 9.1093826E-31

       aBorn,1= 4.41503e-17  nBorn,1= 1.48779e+00

       Emin  5.71e+01    s(Emin)  1.00e-19    Error  3.50e-01



       aBorn,2= 4.20803e-17  nBorn,2= 1.45655e+00

       Emin  5.71e+01    s(Emin)  1.00e-19    Error  2.98e-01

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.13 $  e + He^+(1s) \rightarrow He(1s^1nl^1  \{2S+1\}L) + hv$}

       See text for analytic formulas.



\newpage
\subsection{
Reaction 2.3.14 $   e + He^+(1s) \rightarrow e + He^+(2p)$}





\begin{small}\begin{verbatim}
   a0 -4.215091396506e+03    a1  4.764415543278e+03    a2 -2.333572119719e+03
   a3  6.411861251368e+02    a4 -1.081470970453e+02    a5  1.147267078966e+01
   a6 -7.480739782521e-01    a7  2.743315170494e-02    a8 -4.335336435784e-04
       Emin  4.32e+01   s(Emin)  1.00e-19   smax  1.70e-17   Error  1.66e-01
        Eth  40.8
        Mcross 9.1093826E-31

       aBorn,1= 4.51430e-17  nBorn,1= 9.28386e-01

       Emin  4.32e+01    s(Emin)  1.00e-19    Error  1.96e-01



       aBorn,2= 4.19403e-17  nBorn,2= 8.97086e-01

       Emin  4.32e+01    s(Emin)  1.00e-19    Error  2.07e-01

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 2.3.15 $   e + He^+(1s) \rightarrow e + He^+(2s)$}





\begin{small}\begin{verbatim}
   a0 -4.363513156598e+04    a1  6.029422825525e+04    a2 -3.615014929003e+04
   a3  1.227349742282e+04    a4 -2.581215777982e+03    a5  3.443868798585e+02
   a6 -2.847203555533e+01    a7  1.333878006451e+00    a8 -2.711798666500e-02
       Emin  4.33e+01   s(Emin)  1.00e-19   smax  3.29e-18   Error  1.27e-01
        Eth 40.8
        Mcross 9.1093826E-31

       aBorn,1= 1.55600e-17  nBorn,1= 1.68750e+00

       Emin  4.33e+01    s(Emin)  1.00e-19    Error  3.88e-01



       aBorn,2= 1.31202e-17  nBorn,2= 1.55578e+00

       Emin  4.33e+01    s(Emin)  1.00e-19    Error  2.24e-01

       An analytic formula for s is given in the text.
\end{verbatim}\end{small}









\newpage
\subsection{
Reaction 2.3.19 $   e + He^+(1s) \rightarrow e + He^{++} + e$}


\begin{small}\begin{verbatim}
   a0 -6.397975729831e+03    a1  7.234572604639e+03    a2 -3.553226640490e+03
   a3  9.838309068727e+02    a4 -1.679762955979e+02    a5  1.811299630401e+01
   a6 -1.205027911620e+00    a7  4.524170259779e-02    a8 -7.342485039293e-04
       Emin  5.74e+01   s(Emin)  1.00e-19   smax  4.84e-18   Error  6.16e-02
        Eth  54.4
        Mcross 9.1093826E-31

       aBorn,1= 1.11824e-17  nBorn,1= 8.89614e-01
       Emin  5.74e+01    s(Emin)  1.00e-19    Error  1.88e-01

       aBorn,2= 1.35777e-17  nBorn,2= 9.66349e-01
       Emin  5.74e+01    s(Emin)  1.00e-19    Error  1.70e-01
\end{verbatim}\end{small}


\newpage
\subsection{
Reaction 3.1.1 $   p + H(1s) \rightarrow p + H(2p)$}


\begin{small}\begin{verbatim}
   a0  1.498711267601e+03    a1 -1.883748471843e+03    a2  9.798674598591e+02
   a3 -2.840533664327e+02    a4  5.025004769585e+01    a5 -5.555355513127e+00
   a6  3.748565821577e-01    a7 -1.412032135035e-02    a8  2.274926861613e-04
  ar0 -1.196915681000E+02   ar1  1.572533096000E+01   ar2 -7.444839514000E-01
ELABMAX=  1.20000E+05 eV
       Emin  5.01e+01   s(Emin)  1.00e-19   smax  3.09e-17   Error  2.54e-03
       Eth  10.2
       Mcross 1.0E+00
       Not valid for E < 30 eV.
\end{verbatim}\end{small}


\newpage
\subsection{
Reaction 3.1.2 $   p + H(1s) \rightarrow p + H(2s)$}


\begin{small}\begin{verbatim}
   a0  2.829875237564e+03    a1 -6.116917512897e+03    a2  3.922809899060e+03
   a3 -1.246183868116e+03    a4  2.285990672320e+02    a5 -2.546914306461e+01
   a6  1.706611319064e+00    a7 -6.339871351017e-02    a8  1.005024483671e-03
  ar0 -8.703695946000E+01   ar1  9.315160999000E+00   ar2 -4.461712204000E-01
ELABMAX=  8.00000E+04 eV
       Emin  6.00e+02   s(Emin)  1.00e-19   smax  9.15e-18   Error  1.95e-03
       Eth  10.2
       Mcross 1.0E+00
       Not valid for E < 400 eV.
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 3.1.3 $   p + H(2s) \rightarrow p + H(2p)$}


\begin{small}\begin{verbatim}
   a0 -7.074596259394e+01    a1  1.053200029604e+02    a2 -9.022427163873e+01
   a3  3.938090329805e+01    a4 -9.804841353212e+00    a5  1.447083362703e+00
   a6 -1.251503545319e-01    a7  5.855600339770e-03    a8 -1.143715732966e-04
       Emin  1.76e+00   s(Emin)  1.00e-19   smax  3.61e-11   Error  2.20e+00
       Eth    0.0
       Mcross 1.0E+00
       This fit is not recommended.  Use the analytic formula for s given in the
       text (Chibisov,1969).
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 3.1.6 $   p + H(1s) \rightarrow p + H^+ + e$}


\begin{small}\begin{verbatim}
   a0 -3.476414561951e+06    a1  2.961782930805e+06    a2 -1.100587541308e+06
   a3  2.329850579421e+05    a4 -3.073181275800e+04    a5  2.586508086362e+03
   a6 -1.356488358412e+02    a7  4.053120293214e+00    a8 -5.282803274226e-02
  al0 -7.104410581000E+01   al1  5.699173611000E+00   al2 -2.002816430000E-01
  ar0 -4.489505659000E+01   ar1  1.926156466000E+00   ar2 -1.091588336000E-01
ELABMIN=  2.00000E+03 eV
ELABMAX=  2.25000E+04 eV
       Emin  1.52e+03   s(Emin)  1.00e-19   smax  1.53e-16   Error  1.16e-02
       Eth   13.6
       Mcross 1.0E+00
       An analytic formula for s is given in the text.
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.1.8 $   p + H(1s) \rightarrow H(1s) + p$}


\begin{small}\begin{verbatim}
   a0 -3.274123792568e+01    a1 -8.916456579806e-02    a2 -3.016990732025e-02
   a3  9.205482406462e-03    a4  2.400266568315e-03    a5 -1.927122311323e-03
   a6  3.654750340106e-04    a7 -2.788866460622e-05    a8  7.422296363524e-07
  al0 -3.294589600000E+01   al1 -1.713112000000E-01   al2  0.000000000000e+00
  ar0 -5.787734011000E+01   ar1  7.671416829000E+00   ar2 -5.208376804000E-01
ELABMIN=  0.10000E 00 eV
ELABMAX=  5.00000E+05 eV
       Emin  1.00e-01   s(Emin)  7.00e-15   smax  7.00e-15   Error  2.25e-03
       Eth  0.0
       Mcross 1.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 3.1.9 $   p + H(1s) \rightarrow H(2p) + p$}


\begin{small}\begin{verbatim}
   a0 -2.197571949935e+01    a1 -4.742502251260e+01    a2  3.628013140596e+01
   a3 -1.423003075866e+01    a4  3.273090240144e+00    a5 -4.557928912260e-01
   a6  3.773588347458e-02    a7 -1.707904867106e-03    a8  3.251203344615e-05
  ar0 -5.861021344000E+01   ar1  5.229876071000E+00   ar2 -3.222657437000E-01
ELABMAX=  6.50000E+04 eV
       Emin  1.90e+01   s(Emin)  1.00e-19   smax  2.97e-17   Error  3.29e-03
       Eth  10.2
       Mcross 1.0E+00
       Not valid for E < 10 eV.
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 3.1.10 $   p + H(1s) \rightarrow H(2s) + p$}


\begin{small}\begin{verbatim}
   a0 -1.327325087764e+04    a1  1.317576614520e+04    a2 -5.683932157858e+03
   a3  1.386309780149e+03    a4 -2.089794561307e+02    a5  1.992976245274e+01
   a6 -1.173800576157e+00    a7  3.902422810767e-02    a8 -5.606240339932e-04
       Emin  2.62e+02   s(Emin)  1.00e-19   smax  3.20e-17   Error  1.03e-03
       Eth  10.2
       Mcross 1.0E+00
\end{verbatim}\end{small}


\newpage
\subsection{
Reaction 3.1.11a $   p + H(n=2) \rightarrow H(n=2) + p$}


\begin{small}\begin{verbatim}
   a0 -3.160064085208e+01    a1 -1.063971267559e-01    a2  1.758632420708e-02
   a3 -1.343032128288e-02    a4 -2.158483440621e-03    a5  2.016888852861e-03
   a6 -3.768535435172e-04    a7  2.790447577960e-05    a8 -7.334007645451e-07
       Emin  1.00e-01   s(Emin)  2.50e-14   smax  2.50e-14   Error  9.57e-04
       Eth  0.0
       Mcross 1.0E+00
\end{verbatim}\end{small}


\newpage
\subsection{
Reaction 3.1.11b $p + H(n=3) \rightarrow H(n=3) + p$}






%     *       *
%p + H (n=3) T H (n=3) + p









\begin{small}\begin{verbatim}
   a0 -3.007479360386e+01    a1 -1.033159234538e-01    a2 -5.813424077828e-03
   a3  3.520834872493e-03    a4 -1.498488713106e-04    a5 -4.614034275366e-04
   a6  1.226477420816e-04    a7 -1.180475816996e-05    a8  3.892872672032e-07
  ar0 -3.732339082000E+01   ar1  1.751199692000E+00   ar2 -1.246752946000E-01
ELABMAX=  2.00000E+04 eV
       Emin  1.00e-01   s(Emin)  1.07e-13   smax  1.07e-13   Error  2.04e-04
       Eth  0.0
       Mcross 1.0E+00
\end{verbatim}\end{small}


\newpage
\subsection{
Reaction 3.2.1a $   p + H_2(j=0) \rightarrow p + H_2(j')   (j' \geq 2)$}


\begin{small}\begin{verbatim}
   a0 -3.351219959966e+01    a1 -1.635225977493e-01    a2 -6.547019337483e-02
   a3 -2.075062265158e-03    a4 -4.874756961659e-03    a5 -4.660550753949e-03
   a6  2.817993595595e-04    a7  2.508118915628e-04    a8 -2.791892312099e-05
       Emin  1.00e-01   s(Emin)  3.23e-15   smax  3.23e-15   Error  8.28e-04
       Eth  0.05
       Mcross 1.0E+00
\end{verbatim}\end{small}







\newpage
\subsection{
Reaction 3.2.1b $   p + H_2(j=1) \rightarrow p + H_2(j')   (j' \geq 3)$}


\begin{small}\begin{verbatim}
   a0 -3.393406708822e+01    a1 -1.040291133860e-01    a2 -2.235808125213e-02
   a3 -3.320456299848e-02    a4 -2.081525199080e-02    a5  1.897906681845e-03
   a6  1.657385114123e-03    a7 -3.410682026726e-04    a8  1.868694684385e-05
  ar0 -3.098471597000E+01   ar1 -1.645306432000E+00   ar2 -1.849934446000E-02
ELABMAX=  1.00000E+02 eV
       Emin  1.00e-01   s(Emin)  2.19e-15   smax  2.19e-15   Error  4.08e-04
       Eth  0.05
       Emax 2.0E+03
       Mcross 1.0E+00
       Not valid for E > 2000 eV.
\end{verbatim}\end{small}


\newpage
\subsection{
Reaction 3.2.2 $   p + H_2(v=0) \rightarrow p + H_2(v > 0)$}


\begin{small}\begin{verbatim}
   a0 -4.048908822949e+01    a1  3.404344799771e+00    a2 -1.787578523150e+00
   a3  1.394845302080e+00    a4 -5.775848321190e-01    a5  1.183902638008e-01
   a6 -1.276577600153e-02    a7  6.983034334039e-04    a8 -1.531189559106e-05
       Emin  6.02e-01   s(Emin)  1.00e-19   smax  1.24e-15   Error  2.22e-02
       Eth  0.5
       Mcross 1.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 3.2.3 $   p + H_2 \rightarrow H(1s) + H_2^+$}


\begin{small}\begin{verbatim}
   a0 -8.965985910240e+01    a1  1.057326823133e+02    a2 -8.364373343149e+01
   a3  3.396650519934e+01    a4 -7.931279499027e+00    a5  1.110667708159e+00
   a6 -9.213077375317e-02    a7  4.170940125995e-03    a8 -7.937779949951e-05
       Emin  2.72e+00   s(Emin)  1.00e-19   smax  1.03e-15   Error  2.46e-01
       Eth  1.83
       Mcross 1.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 3.2.4a $   p + D_2 \rightarrow D^+ + HD (\mbox{or}~ H + D)$}


\begin{small}\begin{verbatim}
   a0 -3.514598267631e+01    a1 -1.638772651981e+00    a2 -3.145916075331e-01
   a3  2.614991388325e-01    a4  2.453621020680e-03    a5 -2.572795334322e-02
   a6  5.870493979209e-03    a7 -5.239437578054e-04    a8  1.696795511874e-05
  ar0 -3.711342385000E+01   ar1 -4.917503936000E-01   ar2 -2.634191267000E-02
ELABMAX=  5.00000E+03 eV
       Emin  1.00e-01   s(Emin)  2.47e-15   smax  2.47e-15   Error  3.74e-02
       Eth  0.04
       Mcross 1.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 3.2.4b $   p + D_2 \rightarrow D + HD^+$}


\begin{small}\begin{verbatim}
   a0 -3.793844403725e+03    a1  1.562579182141e+04    a2 -2.785112864175e+04
   a3  2.778553560654e+04    a4 -1.698201826254e+04    a5  6.517141981195e+03
   a6 -1.535237801461e+03    a7  2.031763319972e+02    a8 -1.157681794201e+01
       Emin  2.72e+00   s(Emin)  1.00e-19   smax  2.33e-17   Error  3.79e-01
       Eth  1.87
       Mcross 1.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 3.2.5 $   p + H_2 \rightarrow p + H_2^+(v \leq 9) + e$}


\begin{small}\begin{verbatim}
   a0  1.681920096116e+01    a1 -8.751084517093e+01    a2  5.024534132103e+01
   a3 -1.560982391827e+01    a4  2.931478842554e+00    a5 -3.421137108600e-01
   a6  2.429148918124e-02    a7 -9.612735627840e-04    a8  1.625014598463e-05
  ar0 -8.067212059000E+01   ar1  8.148943513000E+00   ar2 -3.720218589000E-01
ELABMAX=  1.00000E+05 eV
       Emin  4.36e+01   s(Emin)  1.00e-19   smax  1.19e-16   Error  2.51e-04
       Eth  15.41
       Mcross 1.0E+00

       Not valid for E < 30 eV.
\end{verbatim}\end{small}







\newpage
\subsection{
Reaction 3.2.6 $   p + H_2^+(v) \rightarrow p + H(1s) + H^+$}


\begin{small}\begin{verbatim}
   a0 -5.100296089295e+01    a1 -7.618139241529e+00    a2  9.925169617893e+00
   a3 -4.105615029225e+00    a4  9.552023306824e-01    a5 -1.333440043499e-01
   a6  1.095282998853e-02    a7 -4.868705304669e-04    a8  9.034188174517e-06
  ar0 -3.914276949000E+01   ar1  1.668753218000E+00   ar2 -1.266187689000E-01
ELABMAX=  2.00000E+04 eV
       Emin  1.90e+01   s(Emin)  1.00e-19   smax  1.79e-15   Error  9.54e-04
       Eth  6.0
       Mcross 1.0E+00

       Not valid for E < 10 eV.
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 3.3.1 $   p + He \rightarrow  H + He^+(1s)$}


\begin{small}\begin{verbatim}
   a0 -4.883734637847e+01    a1 -7.864577316892e+00    a2  1.051518602966e+01
   a3 -4.731600895321e+00    a4  1.169830752883e+00    a5 -1.750344914778e-01
   a6  1.574934435872e-02    a7 -7.784849464356e-04    a8  1.611953487366e-05
  ar0 -6.990672456000E+01   ar1  7.540193740000E+00   ar2 -4.130236463000E-01
ELABMAX=  8.00000E+04 eV
       Emin  1.73e+01   s(Emin)  1.00e-19   smax  1.79e-16   Error  8.53e-04
       Eth  11.2
       Mcross 1.0E+00

       Not valid for E < 10 eV.
\end{verbatim}\end{small}


\newpage
\subsection{
Reaction 3.3.2 $    p + He \rightarrow p + He^+(1s) + e$}


\begin{small}\begin{verbatim}
   a0  4.624871765081e+03    a1 -4.745692532499e+03    a2  2.081508647511e+03
   a3 -5.150987820537e+02    a4  7.872087768079e+01    a5 -7.611766573851e+00
   a6  4.549589444268e-01    a7 -1.537511000653e-02    a8  2.250170199350e-04
       Emin 2.00e+02   s(Emin)  1.00e-19   smax  7.90e-17   Error 1.58e-04
       Eth  24.58
       Mcross 1.0E+00
\end{verbatim}\end{small}


\subsection{
Reaction 3.3.2n $    p + He \rightarrow p + He^+(1s) + e$}
revised version 2016, new fit. Better asymptotics

\begin{small}\begin{verbatim}
   a0  4.195044321889E+02    a1 -3.711223698781E+02    a2  1.209086460598E+02
   a3 -2.057942831375E+01    a4  1.924450806836E+00    a5 -8.969801627503E-02
   a6  8.987363020501E-04    a7  7.919962773841E-05    a8 -2.232174653859E-06
       Eth  24.58

\end{verbatim}\end{small}


\newpage
\subsection{
Reaction 3.3.3 $p + He(1s^21S) \rightarrow p + He(1s^12p^11P)$}






%          2 1           *      1
% p + He(1s | S) T p + He (1s2p| P)









\begin{small}\begin{verbatim}
   a0 -1.817859864600e+03    a1  1.862928035048e+03    a2 -8.556804144556e+02
   a3  2.228609435255e+02    a4 -3.580573984427e+01    a5  3.624830875484e+00
   a6 -2.255912682713e-01    a7  7.890547281314e-03    a8 -1.188134235646e-04
       Emin  1.38e+02   s(Emin)  1.00e-19   smax  7.73e-17   Error  1.91e-05
       Eth  19.819
       Mcross 1.0E+00

       A more extensive analytic formula is given in the text.
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 3.3.6a $   p + He(1s^12s^11S) \rightarrow H(2s) + He^+(1s)$}


\begin{small}\begin{verbatim}
   a0 -4.488921384477e+01    a1  4.960932531533e+00    a2 -3.262576803403e-01
   a3 -2.936130156727e-01    a4  9.830719566023e-02    a5 -1.436613419090e-02
   a6  1.109137228313e-03    a7 -4.365781757124e-05    a8  6.819428318304e-07
  ar0 -1.490705981000E+02   ar1  2.580229694000E+01   ar2 -1.245093082000E+00
ELABMAX=  1.00000E+08 eV
       Emin  1.26e+00   s(Emin)  1.00e-19   smax  2.13e-15   Error  6.71e-04
       Eth  0.57
       Mcross 1.0E+00
\end{verbatim}\end{small}


\subsection{
Reaction 3.3.6an $   p + He(1s^12s^11S) \rightarrow H(2s) + He^+(1s)$}
revised version 2016, better asymptotics

\begin{small}\begin{verbatim}
   a0 -4.538332073827E+01    a1  7.170783239771E+00    a2 -3.297134523000E+00
   a3  1.487270508093E+00    a4 -4.585715075309E-01    a5  8.239364319341E-02
   a6 -8.248906041886E-03    a7  4.255246239358E-04    a8 -8.812571753203E-06
       Eth  0.57
\end{verbatim}\end{small}




\newpage
\subsection{
Reaction 3.3.6b $   p + He(1s^12s^13S) \rightarrow H(2s) + He^+(1s)$}


\begin{small}\begin{verbatim}
   a0 -4.848650583528e+01    a1 -3.932691714215e+00    a2  7.523124596576e+00
   a3 -3.127572865354e+00    a4  6.776405973062e-01    a5 -8.713461726775e-02
   a6  6.707424051145e-03    a7 -2.863198766538e-04    a8  5.218187112892e-06
  ar0 -3.785059671000E+01   ar1  9.686976447000E-01   ar2 -5.936675659000E-02
ELABMAX=  1.00000E+05 eV
       Emin  6.06e+00   s(Emin)  1.00e-19   smax  1.85e-15   Error  7.93e-04
       Eth  1.369
       Mcross 1.0E+00

       Not valid for E < 5.
\end{verbatim}\end{small}


\subsection{
Reaction 3.3.6bn $   p + He(1s^12s^13S) \rightarrow H(2s) + He^+(1s)$}
revised version,  better asymptotics

\begin{small}\begin{verbatim}
   a0 -8.074074443551E+01    a1  5.555156807550E+01    a2 -3.738101128542E+01
   a3  1.501104472390E+01    a4 -3.618982367308E+00    a5  5.256859236453E-01
   a6 -4.485164096934E-02    a7  2.062076755012E-03    a8 -3.933113737905E-05
Eth  1.369
\end{verbatim}\end{small}
\newpage

\subsection{
Reaction 3.3.7a $   p + He(1s^12p^11P) \rightarrow H(2p) + He^+(1s)$}


\begin{small}\begin{verbatim}
   a0 -3.761174237974e+01    a1  3.151158037643e+00    a2 -9.333114666012e-01
   a3  2.699732305042e-01    a4 -7.727620729277e-02    a5  1.499779990623e-02
   a6 -1.669176505953e-03    a7  9.612733086019e-05    a8 -2.222038029912e-06
       Emin  3.02e-01   s(Emin)  1.00e-19   smax  1.07e-14   Error  6.71e-03
       Eth  0.0
       Mcross 1.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 3.3.7b $   p + He(1s^12p^13P) \rightarrow H(2p) + He^+(1s)$}


\begin{small}\begin{verbatim}
   a0 -3.567086579938e+01    a1  2.166873578000e+00    a2 -8.322452040300e-01
   a3  3.967778327802e-01    a4 -1.418439656872e-01    a5  2.883195206911e-02
   a6 -3.206621198950e-03    a7  1.828199967957e-04    a8 -4.182687867891e-06
       Emin  2.61e-01   s(Emin)  1.00e-19   smax  1.32e-14   Error  7.49e-02
       Eth  0.225
       Mcross 1.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 4.2.1 $H_2^+(v) + H(1s) \rightarrow H_2^+(2p\sigma_u) + H(1s) \rightarrow H^+ + H + H(1s), (v=0\ldots 9)$}






% +                    +*
%H N1ss ;vO + H(1s) T H  N2ps O + H(1s) T
% 2    g               2     u
%                      +
%                   T H  + H + H(1s), (v = 0 - 9)






\begin{small}\begin{verbatim}
   a0  1.885518121144e+04    a1 -1.730109845144e+04    a2  6.789143089426e+03
   a3 -1.495308617111e+03    a4  2.025858786888e+02    a5 -1.731165351422e+01
   a6  9.120053117120e-01    a7 -2.709481429950e-02    a8  3.476220959653e-04
  ar0 -1.032118444000E+03   ar1  1.641681892000E+02   ar2 -6.789412670000E+00
ELABMAX=  1.00000E+06 eV
       Emin  3.96e+02   s(Emin)  1.00e-19   smax  1.99e-16   Error  2.02e-03
       Eth  6.0
       Mcross 2.0E+00

       Not valid for E < 300 eV.
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 4.3.1 $   H_2^+ + H_2 \rightarrow H_2 + H_2^+$}


\begin{small}\begin{verbatim}
   a0 -3.427958758517e+01    a1 -7.121484125189e-02    a2  4.690466187943e-02
   a3 -8.033946660540e-03    a4 -2.265090924593e-03    a5 -2.102414848737e-04
   a6  1.948869487515e-04    a7 -2.208124950005e-05    a8  7.262446915488e-07
  ar0 -7.463331048000E+01   ar1  8.629058909000E+00   ar2 -4.691006442000E-01
ELABMAX=  1.00000E+05 eV
       Emin  1.00e-01   s(Emin)  2.10e-15   smax  2.10e-15   Error  3.91e-04
       Eth  0.
       Mcross 2.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 4.3.2 $   H_2^+ + H_2 \rightarrow H_2^+ + H_2^+ + e$}


\begin{small}\begin{verbatim}
   a0 -2.383489439121e+02    a1  2.384368432909e+02    a2 -1.263102889116e+02
   a3  3.746454397894e+01    a4 -6.767700946931e+00    a5  7.629123486032e-01
   a6 -5.246096809457e-02    a7  2.014116839267e-03    a8 -3.310073123768e-05
       Emin  3.67e+01   s(Emin)  1.00e-19   smax  3.30e-16   Error 1.11e-04
       Eth  15.4
       Mcross 2.0E+00
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 4.3.3 $   H_2^+ + H_2 \rightarrow H_3^+ + H$}


\begin{small}\begin{verbatim}
   a0 -3.422188283057e+01    a1 -7.733921420462e-01    a2 -4.625452844356e-01
   a3 -2.307540053739e-01    a4  3.188925541844e-02    a5  3.622033742962e-02
   a6 -5.093822617734e-03    a7 -2.420060478318e-03    a8  4.634259500837e-04
  ar0 -3.242526389000E+01   ar1 -2.753789651000E+00   ar2 -9.217068775000E-02
ELABMAX=  3.00000E+01 eV
       Emin  1.00e-01   s(Emin)  4.26e-15   smax  4.26e-15   Error  2.99e-04
       Eth  0.0
       Emax 4.0E+01
       Mcross 2.0E+00
       Not valid for E > 40 eV.
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 4.4.1 $   H_2^+ + He \rightarrow H_2^+ + He^+(1s) + e$}


\begin{small}\begin{verbatim}
   a0 -1.279183240553e+02    a1  7.851907373534e+01    a2 -3.133748457688e+01
   a3  6.817786375262e+00    a4 -8.395843945734e-01    a5  5.456579807937e-02
   a6 -1.161799515932e-03    a7 -5.185457132932e-05    a8  2.416658401748e-06
  ar0 -4.780235129000E+01   ar1  2.462576818000E+00   ar2 -1.322702144000E-01
ELABMAX=  1.00000E+05 eV
       Emin  4.52e+01   s(Emin)  1.00e-19   smax  1.30e-16   Error  1.34e-04
       Eth  24.58
       Mcross 2.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 5.2.1 $   He^+(1s) + H_2 \rightarrow He^+(1s) + H_2^+ + e$}


\begin{small}\begin{verbatim}
   a0 -2.325294713788e+02    a1  2.137835372191e+02    a2 -1.060826620181e+02
   a3  3.048034248334e+01    a4 -5.472938698614e+00    a5  6.242016892196e-01
   a6 -4.400795546393e-02    a7  1.751040972949e-03    a8 -3.008006324086e-05
       Emin  1.90e+01   s(Emin)  1.00e-19   smax  5.51e-17   Error  3.94e-03
       Eth  15.4
       Mcross 4.0E+00

\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 5.2.2 $   He^+(1s) + H_2 \rightarrow He(1s^21S) + H_2^+$}


\begin{small}\begin{verbatim}
   a0 -1.108066480195e+04    a1  1.008755280085e+04    a2 -4.018540037373e+03
   a3  9.114656395741e+02    a4 -1.288151812962e+02    a5  1.162404023738e+01
   a6 -6.543944103705e-01    a7  2.101966590407e-02    a8 -2.949737399468e-04
       Emin  5.84e+02   s(Emin)  1.00e-19   smax  1.39e-16   Error  1.86e-04
       Eth  0.0
       Mcross 4.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 5.2.3 $   He^+(1s) + H_2 \rightarrow He(1s^21S) + H^+ + H$}


\begin{small}\begin{verbatim}
   a0 -4.311350879235e+01    a1  5.515944942674e-02    a2 -5.606069194725e-01
   a3  1.291230751283e-01    a4  1.533686418592e-01    a5 -6.125769782521e-02
   a6  8.886802346189e-03    a7 -5.806431060224e-04    a8  1.440125514216e-05
  ar0 -5.560154242000E+01   ar1  5.037170638000E+00   ar2 -3.585460009000E-01
ELABMAX=  2.00000E+04 eV
       Emin  2.33e-01   s(Emin)  1.00e-19   smax  1.33e-16   Error  2.66e-02
       Eth  0.0
       Mcross 4.0E+00

       Not valid for E < 0.3 eV.
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 5.3.1 $   He^+(1s) + He \rightarrow He + He^+(1s)$}


\begin{small}\begin{verbatim}
   a0 -3.369296194290e+01    a1 -8.324653178943e-02    a2  6.660151719388e-03
   a3 -3.592504363592e-03    a4 -1.745382918016e-04    a5  1.497204460315e-04
   a6 -2.152122621503e-05    a7  1.473684503283e-06    a8 -4.401831552698e-08
       Emin  1.00e-01   s(Emin)  3.00e-15   smax  3.00e-15   Error  5.63e-05
       Eth  0.0
       Mcross 4.0E+00
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 5.3.2 $   He^+ + He \rightarrow He^+ + He^+ + e$}


\begin{small}\begin{verbatim}
   a0 -1.126408326504e+03    a1  1.221414787395e+03    a2 -5.910936989464e+02
   a3  1.609170847736e+02    a4 -2.693537704047e+01    a5  2.837798810047e+00
   a6 -1.837630539164e-01    a7  6.688462818228e-03    a8 -1.048046510736e-04
       Emin  2.88e+01   s(Emin)  1.00e-19   smax  6.12e-17   Error  1.13e-02
       Eth  24.58
       Mcross 4.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 6.1.1 $   He^{++} + H(1s) \rightarrow He^{++} + H(2p)$}


\begin{small}\begin{verbatim}
   a0 -3.935171502778e+03    a1  3.121350934839e+03    a2 -1.090958722369e+03
   a3  2.154761368634e+02    a4 -2.615076564408e+01    a5  1.988438495730e+00
   a6 -9.217310084360e-02    a7  2.372722474405e-03    a8 -2.585687269696e-05
       Emin  7.18e+02   s(Emin)  1.00e-19   smax  1.03e-16   Error  1.19e-05
       Eth  10.275
       Mcross 4.0E+00

       A more extensive analytic formula for all n >= 2 is given in the text.
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 6.1.3 $   He^{++} + H(1s) \rightarrow He^{++} + H^+ + e$}


\begin{small}\begin{verbatim}
   a0 -4.108092972648e+05    a1  3.538162825295e+05    a2 -1.328131904744e+05
   a3  2.837637619784e+04    a4 -3.774364805704e+03    a5  3.200454272008e+02
   a6 -1.689565219222e+01    a7  5.077317110574e-01    a8 -6.650084296041e-03
       Emin  1.34e+03   s(Emin)  1.00e-19   smax  1.60e-16   Error 9.63e-04
       Eth  13.6
       Mcross 4.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 6.1.4 $   He^{++} + H(n) \rightarrow  He^{++} + H^+ + e   (n \geq 2)$}

\begin{small}\begin{verbatim}
       An analytic formula for the cross section for all n is given in the text.
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 6.1.5 $   He^{++} + H(2s) \rightarrow  He^{++} + H(2p)   $}

\begin{small}\begin{verbatim}
       An analytic formula for cross section is given in the text.
       Neutral particle at rest, charged particle energy E_lab(eV)

       cross_cm = $6.336e-10/E_{lab}*log(0.5515*E_{lab})$
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 6.1.6 $   He^{++} + H \rightarrow He^+(n=2) + H^+$}


\begin{small}\begin{verbatim}
   a0 -4.315145081040e+01    a1  1.153902751649e+00    a2 -1.770607674796e-03
   a3 -4.249237424243e-02    a4  2.552430939448e-02    a5 -6.612097121922e-03
   a6  8.587538946329e-04    a7 -5.501612272760e-05    a8  1.373936349802e-06
  ar0 -4.052049207000E+01   ar1  1.753255540000E+00   ar2 -1.110727227000E-01
ELABMAX=  1.00000E+05 eV
       Emin  6.00e-01   s(Emin)  1.00e-19   smax  1.36e-15   Error  2.92e-04
       Eth  0
       Mcross 4.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 6.1.7 $   He^{++} + H(n) \rightarrow  He^+(n') + H^+$}

\begin{small}\begin{verbatim}
       An analytic formula for s is given in the text.
       Neutral particle at rest, charged particle energy E_{lab}(eV)

       Transition: n --> n',   with n'=2n, n=2,4,6,....; E_th=0

              v = 3.1623e-3*sqrt(E_lab)
       cross_cm = 4.69e-16*n**4/(1.+0.8*(n*v)**0.4+2.6*n*v)

       Transition: n --> n',   with n'=2n-1, n=2,4,6,....; E_th=...

       cross(2 --> 3) =  0.75* cross(2 --> 4)
       cross(3 --> 5) =  0.80* cross(3 --> 6)
       cross(4 --> 7) =  0.85* cross(4 --> 8)
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 6.2.1 $   He^{++} + H_2 \rightarrow He^{++} + H_2^+(v) + e$}


\begin{small}\begin{verbatim}
   a0 -3.888955469991e+01    a1 -9.866429655660e+00    a2  5.655068418984e+00
   a3 -1.577966214613e+00    a4  2.645599512156e-01    a5 -2.758466438253e-02
   a6  1.761704594534e-03    a7 -6.345561877676e-05    a8  9.903373373326e-07
       Emin  3.31e+01   s(Emin)  1.00e-19   smax  3.87e-16   Error  6.85e-05
       Eth  15.4
       Mcross 4.0E+00

       Not valid for E < 30 eV.
\end{verbatim}\end{small}

\subsection{
Reaction 6.2.1n $   He^{++} + H_2 \rightarrow He^{++} + H_2^+(v) + e$}
revised version, better asymptotics

\begin{small}\begin{verbatim}
   a0 -1.348256538024E+02    a1  9.118284774788E+01    a2 -3.835314779831E+01
   a3  8.719939323071E+00    a4 -1.142249374234E+00    a5  8.618810448200E-02
   a6 -3.470340641765E-03    a7  5.759492568234E-05    a8 -9.734400000000E-24
       Eth  15.4
\end{verbatim}\end{small}


\newpage
\subsection{
Reaction 6.3.1 $   He^{++} + He \rightarrow He + He^{++}$}


\begin{small}\begin{verbatim}
   a0 -3.459818117569e+01    a1 -8.748942423786e-02    a2 -2.445604128495e-02
   a3  2.392295193337e-03    a4  9.876388162277e-04    a5 -2.282012750308e-04
   a6  3.598361283629e-06    a7  1.940270105613e-06    a8 -1.105794797036e-07
       Emin  1.00e-01   s(Emin)  1.03e-15   smax  1.03e-15   Error  1.74e-04
       Eth  0
       Mcross 4.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 6.3.2 $   He^{++} + He \rightarrow He^{++} + He^+(1s) + e$}


\begin{small}\begin{verbatim}
   a0  1.416740796235e+06    a1 -1.119008170939e+06    a2  3.857965046775e+05
   a3 -7.583813526516e+04    a4  9.297450568358e+03    a5 -7.279675981729e+02
   a6  3.555154263032e+01    a7 -9.901755546104e-01    a8  1.204251833183e-02
       Emin  4.75e+03   s(Emin)  1.00e-19   smax  2.50e-17   Error 3.33e-05
       Eth  24.588
       Mcross 4.0E+00
\end{verbatim}\end{small}


\subsection{
Reaction 6.3.2n $   He^{++} + He \rightarrow He^{++} + He^+(1s) + e$}
revised version, better asymptotics

\begin{small}\begin{verbatim}
   a0 -1.055124995647E+04    a1  7.814313871085E+03    a2  -2.525546560126E+03
   a3  4.623987021985E+02    a4 -5.238841605982E+01    a5   3.757793036669E+00
   a6 -1.665366765547E-01    a7  4.167057779117E-03    a8  -4.505951553161E-05
       Eth  24.588
\end{verbatim}\end{small}


\newpage
\subsection{
Reaction 7.1.1 $   e + H^- \rightarrow e + H(1s) + e$}


\begin{small}\begin{verbatim}
   a0 -3.934913643088e+01    a1  7.492484197616e+00    a2 -6.138735352362e+00
   a3  3.326569253609e+00    a4 -1.040328294213e+00    a5  1.834296974839e-01
   a6 -1.814008493227e-02    a7  9.403286251360e-04    a8 -1.989848289161e-05
       Emin  9.06e-01   s(Emin)  1.00e-19   smax  3.75e-15   Error  2.64e-01
       Eth  0.75
       Mcross 9.1093826E-31
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 7.1.2 $   e + H^- \rightarrow e + H^+ + 2e$}


\begin{small}\begin{verbatim}
   a0 -7.448448227127e+02    a1  8.696721447863e+02    a2 -4.584681915725e+02
   a3  1.353555608991e+02    a4 -2.446848674683e+01    a5  2.771980281770e+00
   a6 -1.922085761453e-01    a7  7.462384021984e-03    a8 -1.243029551161e-04
       Emin  1.66e+01   s(Emin)  1.00e-19   smax  5.06e-17   Error  3.39e-02
       Eth  14.35
       Mcross 9.1093826E-31
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 7.2.1 $   p + H^- \rightarrow p + H + e$}


\begin{small}\begin{verbatim}
   a0 -1.050889816750e+04    a1  1.054502629910e+04    a2 -4.618343915803e+03
   a3  1.147184656009e+03    a4 -1.766806773292e+02    a5  1.727351520643e+01
   a6 -1.046726308683e+00    a7  3.593652631660e-02    a8 -5.350831095528e-04
       Emin  2.25e+02   s(Emin)  1.00e-19   smax  4.76e-15   Error  1.18e-03
       Eth  0.75
       Mcross 1.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 7.2.2 $   p + H^- \rightarrow H(n=2) + H(1s)$}


\begin{small}\begin{verbatim}
   a0 -3.498808881328e+01    a1  2.152450508307e-01    a2 -2.356286641829e-02
   a3  5.494715530438e-02    a4  5.379328883390e-03    a5 -6.055070213687e-03
   a6  9.991683287907e-04    a7 -6.636255640130e-05    a8  1.612283845094e-06
  ar0 -2.918073629000e+01   ar1 -1.327281071000e-01   ar2 -4.679898982000e-02
ELABMAX=  2.00000E+04 eV
       Emin  1.00e-01   s(Emin)  3.30e-16   smax  1.38e-14   Error  2.29e-03
       Eth  0.
       Mcross 1.0E+00
       Maxrate (sigma * vlab) = 2.730823e-13 at Elab= 7.479523e+02
\end{verbatim}\end{small}








\newpage
\subsection{
Reaction 7.2.3 $   p + H^- \rightarrow H(n=3) + H(1s)$}


\begin{small}\begin{verbatim}
   a0 -3.114793359560e+01    a1 -7.730205271965e-01    a2  5.492043775127e-02
   a3 -2.733249841523e-03    a4 -1.228312883866e-03    a5  4.350498278844e-04
   a6 -6.216595007254e-05    a7  4.120468065072e-06    a8 -1.039784996359e-07
       Emin  1.00e-01   s(Emin)  2.25e-13   smax  2.25e-13   Error  5.93e-05
       Eth  0.
       Mcross 1.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 7.3.1 $   H^- + H(1s) \rightarrow H(1s) + H^-(1s)$}


\begin{small}\begin{verbatim}
   a0 -3.896158248196e+01    a1 -2.677306137623e-03    a2 -6.353177906590e-03
   a3 -7.238847698066e-03    a4  1.297916639224e-03    a5  5.654591683916e-04
   a6 -2.351925503212e-04    a7  2.913484058046e-05    a8 -1.229505901932e-06
       Emin  1.00e-01   s(Emin)  1.23e-17   smax  1.23e-17   Error  4.04e-04
       Eth  0.
       Mcross 1.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 7.3.2a $   H^- + H \rightarrow H_2^-(\Sigma_g) \rightarrow H + H + e$}


\begin{small}\begin{verbatim}
   a0 -3.617990822381e+01    a1  1.166151722958e+00    a2 -1.419286024586e-01
   a3 -1.111959587916e-02    a4 -1.725059947629e-03    a5  1.590403561378e-03
   a6 -2.531961443012e-04    a7  1.669782349801e-05    a8 -4.097257966950e-07
       Emin  1.00e-01   s(Emin)  6.09e-18   smax  1.54e-15   Error  3.23e-04
       Eth  0.
       Mcross 1.0E+00
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 7.3.2b $   H^- + H \rightarrow H_2^-(\Sigma_u) \rightarrow H_2 + e$}


\begin{small}\begin{verbatim}
   a0 -3.441529065653e+01    a1 -3.393482086017e-01    a2  5.665917047817e-02
   a3 -9.051504593339e-03    a4  7.660604175354e-04    a5 -4.271264623381e-05
   a6 -1.572737493346e-07    a7  2.576076771707e-07    a8 -1.200719193800e-08
       Emin  1.00e-01   s(Emin)  3.84e-15   smax  3.84e-15   Error  9.90e-05
       Eth  0.
       Mcross 1.0E+00
\end{verbatim}\end{small}






\newpage
\section{H.2  POLYNOMIAL FITS FOR $<\sigma v>$ FOR FIXED $E$}


\subsection{
Reaction 2.1.1 $   e + H(1s) \rightarrow e + H(2p)$}


\begin{small}\begin{verbatim}
   b0 -2.814949375869e+01    b1  1.009828023274e+01    b2 -4.771961915818e+00
   b3  1.467805963618e+00    b4 -2.979799374553e-01    b5  3.861631407174e-02
   b6 -3.051685780771e-03    b7  1.335472720988e-04    b8 -2.476088392502e-06
    Tmin 1.26e+00   <sv>(Tmin) 4.78e-12   <sv>max 3.18e-08   Error 1.51e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.1.2 $   e + H(1s) \rightarrow e + H(2s)$}


\begin{small}\begin{verbatim}
   b0 -2.833259375256e+01    b1  9.587356325603e+00    b2 -4.833579851041e+00
   b3  1.415863373520e+00    b4 -2.537887918825e-01    b5  2.800713977946e-02
   b6 -1.871408172571e-03    b7  6.986668318407e-05    b8 -1.123758504195e-06
    Tmin 1.26e+00   <sv>(Tmin) 3.54e-12   <sv>max 3.22e-09   Error 3.33e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.1.3 $   e + H(2s) \rightarrow e + H(2p)$}


\begin{small}\begin{verbatim}
   b0 -1.219616012805e+01    b1 -3.859057071006e-01    b2 -6.509976401685e-03
   b3  4.981099209058e-04    b4 -4.184102479407e-05    b5  3.054358926267e-06
   b6 -1.328567638366e-07    b7  8.974535105058e-10    b8  1.010269574757e-10
    Tmin 1.00e-01   <sv>(Tmin) 1.18e-05   <sv>max 1.18e-05   Error 2.16e-11
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.1.4a $   e + H(n=1) \rightarrow e + H(n=3)$}


\begin{small}\begin{verbatim}
   b0 -3.113714569232e+01    b1  1.170494035550e+01    b2 -5.598117886823e+00
   b3  1.668467661343e+00    b4 -3.186788446245e-01    b5  3.851704802605e-02
   b6 -2.845199866183e-03    b7  1.171512424827e-04    b8 -2.059295818495e-06
    Tmin 1.58e+00   <sv>(Tmin) 2.32e-12   <sv>max 6.09e-09   Error 3.54e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.1.4b $   e + H(n=2) \rightarrow e + H(n=3)$}


\begin{small}\begin{verbatim}
   b0 -1.515830911091e+01    b1  1.923956400537e+00    b2 -9.275338417712e-01
   b3  3.370367299915e-01    b4 -8.758162223598e-02    b5  1.409066167839e-02
   b6 -1.325225954526e-03    b7  6.672025878086e-05    b8 -1.387615199713e-06
    Tmin 1.58e-01   <sv>(Tmin) 9.92e-12   <sv>max 2.00e-06   Error 4.99e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.1.5 $   e + H(1s) \rightarrow e + H^+ + e$}


\begin{small}\begin{verbatim}
   b0 -3.271396786375e+01    b1  1.353655609057e+01    b2 -5.739328757388e+00
   b3  1.563154982022e+00    b4 -2.877056004391e-01    b5  3.482559773737e-02
   b6 -2.631976175590e-03    b7  1.119543953861e-04    b8 -2.039149852002e-06
    Tmin 2.00e+00   <sv>(Tmin) 7.22e-12   <sv>max 3.11e-08   Error 1.71e-05
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 2.1.6 $   e + H(2s) \rightarrow e + H^+ + e$}


\begin{small}\begin{verbatim}
   b0 -1.973476726029e+01    b1  3.992702671457e+00    b2 -1.773436308973e+00
   b3  5.331949621358e-01    b4 -1.181042453190e-01    b5  1.763136575032e-02
   b6 -1.616005335321e-03    b7  8.093908992682e-05    b8 -1.686664454913e-06
    Tmin 3.98e-01   <sv>(Tmin) 8.87e-12   <sv>max 1.71e-07   Error 7.10e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.1.7 $   e + H(n=3) \rightarrow e + H^+ + e$}


\begin{small}\begin{verbatim}
   b0 -1.566968719411e+01    b1  1.719661170920e+00    b2 -8.365041963678e-01
   b3  2.642794957304e-01    b4 -6.527754894629e-02    b5  1.066883130107e-02
   b6 -1.041488149422e-03    b7  5.457216484634e-05    b8 -1.177539827071e-06
    Tmin 1.26e-01   <sv>(Tmin) 2.00e-12   <sv>max 6.80e-07   Error 9.85e-05

     A more extensive analytic formula for all n > 2 is given in the text.
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.1.8 $  e + H^+ \rightarrow H(1s) + hv $}
general formula: see original text. Here:  added fit to rate for recomb into 1s ground state

\begin{small}\begin{verbatim}
   b0 -2.95894689000e+01     b1 -0.529779950000e+00    b2 -0.005968130000e+00
   b3 -0.00033543090e+00     b4 -0.003004446800e+00    b5 -0.000470231100e+00
   b6  0.00025139600e+00     b7 -2.776281210000e-05    b8  9.833670340000e-07
    Tmin 1.00e-01    Tmax=1.00e+04
\end{verbatim}\end{small}


\subsection{
Reaction 2.1.8a $  e + H^+ \rightarrow H(2s) + hv $}
general formula: see original text. Here:  added fit to rate for recomb into 2s excited state

\begin{small}\begin{verbatim}
   b0 -3.14497513000e+01     b1 -0.525649298000e+00    b2 -0.011206549700e+00
   b3 -0.00823278120e+00     b4 -0.002464058500e+00    b5  0.000284729200e+00
   b6  5.62007081000e-05     b7 -9.251862920000e-06    b8  3.544559600000e-07
    Tmin 1.00e-01    Tmax=1.00e+04
\end{verbatim}\end{small}



\subsection{
Reaction 2.1.8b $  e + H^+ \rightarrow H(2p) + hv $}
general formula: see original text. Here:  added fit to rate for recomb into 2p excited state

\begin{small}\begin{verbatim}
   b0 -3.06473715000e+01     b1 -0.653170766000e+00    b2 -0.068667509300e+00
   b3 -0.01770596520e+00     b4  0.000560929000e+00    b5  0.001091531300e+00
   b6 -0.00020918050e+00     b7  1.546343080000e-05    b8 -4.228481280000e-07
    Tmin 1.00e-01    Tmax=1.00e+04
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.1a $  e + H_2(v=0) \rightarrow e + H_2(v=1)$}


\begin{small}\begin{verbatim}
   b0 -2.017212494454e+01    b1  9.563952280637e-01    b2 -6.931474225637e-01
   b3  1.673671529631e-01    b4 -3.228762898855e-02    b5  5.838603222226e-03
   b6 -8.580542691302e-04    b7  7.456311623168e-05    b8 -2.666978300757e-06
    Tmin 1.58e-01   <sv>(Tmin) 5.83e-12   <sv>max 2.60e-09   Error 2.55e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.1b $  e + H_2(v=0) \rightarrow e + H_2(v=2)$}


\begin{small}\begin{verbatim}
   b0 -2.265507686305e+01    b1  2.239943592222e+00    b2 -1.099426577160e+00
   b3  2.339027647223e-01    b4 -2.528511103871e-02    b5  6.851302489620e-04
   b6  1.253426182224e-04    b7 -1.253475051672e-05    b8  3.545892878015e-07
    Tmin 3.98e-01   <sv>(Tmin) 5.93e-12   <sv>max 7.07e-10   Error 2.74e-07
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.2 $e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2(B^1\Sigma_u^+2p\sigma)$}






%        1 +         *  1 +
%e + H (X S ) T e + H (B S 2ps)
%     2    g         2    u








\begin{small}\begin{verbatim}
   b0 -3.081902926338e+01    b1  1.038866780735e+01    b2 -4.259768348687e+00
   b3  1.181228673120e+00    b4 -2.277513907465e-01    b5  2.900576728856e-02
   b6 -2.287591474628e-03    b7  1.004346442778e-04    b8 -1.869930069131e-06
    Tmin 2.00e+00   <sv>(Tmin) 9.88e-12   <sv>max 1.47e-08   Error 9.52e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.3 $e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2(C^1\Pi_u2p\pi) $}






%        1 +         *  1
%e + H (X S ) T e + H (C < 2p!)
%     2    g         2    u







\begin{small}\begin{verbatim}
   b0 -3.348199796300e+01    b1  1.371702271009e+01    b2 -5.922607900694e+00
   b3  1.709719148860e+00    b4 -3.505232830275e-01    b5  4.834376067841e-02
   b6 -4.131406425550e-03    b7  1.948388368131e-04    b8 -3.854278715563e-06
    Tmin 2.00e+00   <sv>(Tmin) 3.59e-12   <sv>max 1.39e-08   Error 8.14e-05
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 2.2.4 $e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2(E,F^1\Sigma_g^+)$}






%        1 +         *    1 +
%e + H (X S ) T e + H (E,F S )
%     2    g         2      g








\begin{small}\begin{verbatim}
   b0 -3.646589741675e+01    b1  1.430361969329e+01    b2 -6.074430521073e+00
   b3  1.677305768580e+00    b4 -3.128705597349e-01    b5  3.805424730473e-02
   b6 -2.860085821803e-03    b7  1.199641410078e-04    b8 -2.142231851104e-06
    Tmin 3.16e+00   <sv>(Tmin) 5.27e-12   <sv>max 2.23e-09   Error 2.11e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.5 $e + H_2(X^1\Sigma_g^+) \rightarrow  e + H_2(b^3\Sigma_u^+, a^3\Sigma_g^+, c^3\Pi_u) \rightarrow
e + H(1s) + H(1s)$}






%        1 +         *  3 +   3 +       3
%e + H (X S ) T e + H (b S , a S , and c < ) T
%     2    g         2    u     g         u
%
%
%             T e + H(1s) + H(1s)





\begin{small}\begin{verbatim}
   b0 -2.787217511174e+01    b1  1.052252660075e+01    b2 -4.973212347860e+00
   b3  1.451198183114e+00    b4 -3.062790554644e-01    b5  4.433379509258e-02
   b6 -4.096344172875e-03    b7  2.159670289222e-04    b8 -4.928545325189e-06
    Tmin 1.26e+00   <sv>(Tmin) 6.91e-12   <sv>max 9.81e-09   Error 5.94e-07
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.6 $e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2(1s\sigma_g,nl\lambda|^1\Lambda) \rightarrow e +  H(1s) + H(2s)$}






%        1 +         *           1                  *
%e + H (X S ) T e + H (1ss , nPg| G) T e + H(1s) + H (2s)
%     2    g         2    g








\begin{small}\begin{verbatim}
   b0 -3.454175591367e+01    b1  1.412655911280e+01    b2 -6.004466156761e+00
   b3  1.589476697488e+00    b4 -2.775796909649e-01    b5  3.152736888124e-02
   b6 -2.229578042005e-03    b7  8.890114963166e-05    b8 -1.523912962346e-06
    Tmin 2.51e+00   <sv>(Tmin) 7.88e-12   <sv>max 6.92e-09   Error 2.74e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.7 $ e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2(2p\sigma_u, nl\lambda|Q_2^1\Pi_u) \rightarrow e + H(2p) + H(2s)$}






%        1 +         *             1           *        *
%e + H (X S ) T e + H (2ps ; nPg|Q  < ) T e + H (2p) + H (2s)
%     2    g         2    u       2  u








\begin{small}\begin{verbatim}
   b0 -4.794288960529e+01    b1  2.629649351119e+01    b2 -1.151117702256e+01
   b3  2.991954880790e+00    b4 -4.949305181578e-01    b5  5.236320848415e-02
   b6 -3.433774290547e-03    b7  1.272097387363e-04    b8 -2.036079507592e-06
    Tmin 5.01e+00   <sv>(Tmin) 6.48e-12   <sv>max 1.31e-09   Error 3.76e-07
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.8 $e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2(2p\sigma_u;n=3) \rightarrow e + H(1s) + H(n=3)$}






%        1 +         *                          *
%e + H (X S ) T e + H (2ps ;n=3) T e + H(1s) + H (n=3)
%     2    g         2    u








\begin{small}\begin{verbatim}
   b0 -3.884976142596e+01    b1  1.520368281111e+01    b2 -6.078494762845e+00
   b3  1.535455119900e+00    b4 -2.628667482712e-01    b5  2.994456451213e-02
   b6 -2.156175515382e-03    b7  8.826547202670e-05    b8 -1.558890013181e-06
    Tmin 3.98e+00   <sv>(Tmin) 4.09e-12   <sv>max 7.73e-10   Error 6.05e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.9 $e + H_2(X^1\Sigma_g^+) \rightarrow e + H_2^+(v) + e$}






%        1 +         +
%e + H (X S ) T e + H (v) + e
%     2    g         2








\begin{small}\begin{verbatim}
   b0 -3.568640293666e+01    b1  1.733468989961e+01    b2 -7.767469363538e+00
   b3  2.211579405415e+00    b4 -4.169840174384e-01    b5  5.088289820867e-02
   b6 -3.832737518325e-03    b7  1.612863120371e-04    b8 -2.893391904431e-06
    Tmin 2.00e+00   <sv>(Tmin) 2.34e-12   <sv>max 5.18e-08   Error 6.45e-06
\end{verbatim}\end{small}







\newpage
\subsection{
Reaction 2.2.10 $e + H_2(X^1\Sigma_g^+) \rightarrow
e + [H_2^+(\Sigma_g, \Sigma_u) + e] \rightarrow e + H^+ + H(1s) + e$}






%         1 +          +
%e  + H (X S ) T e + [H (S  and S ) + e] T e + H + (1s) + e
%      2    g          2  g      u








\begin{small}\begin{verbatim}
   b0 -3.834597006782e+01    b1  1.426322356722e+01    b2 -5.826468569506e+00
   b3  1.727940947913e+00    b4 -3.598120866343e-01    b5  4.822199350494e-02
   b6 -3.909402993006e-03    b7  1.738776657690e-04    b8 -3.252844486351e-06
    Tmin 3.98e+00   <sv>(Tmin) 3.74e-12   <sv>max 2.89e-09   Error 4.61e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.11 $  e + H_2^+(v) \rightarrow e + H^+ + H^+ + e, (v=0\ldots 9)$}


\begin{small}\begin{verbatim}
   b0 -3.746192301092e+01    b1  1.559355031108e+01    b2 -6.693238367093e+00
   b3  1.981700292134e+00    b4 -4.044820889297e-01    b5  5.352391623039e-02
   b6 -4.317451841436e-03    b7  1.918499873454e-04    b8 -3.591779705419e-06
    Tmin 3.16e+00   <sv>(Tmin) 5.23e-12   <sv>max 9.06e-09   Error 2.26e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.12 $  e + H_2^+(v) \rightarrow e + H_2^+(2p\sigma_u) \rightarrow e + H^+ + H(1s), (v=0\ldots 9)$}


\begin{small}\begin{verbatim}
   b0 -1.781416067709e+01    b1  2.277799785711e+00    b2 -1.266868411626e+00
   b3  4.296170447419e-01    b4 -9.609908013189e-02    b5  1.387958040699e-02
   b6 -1.231349039470e-03    b7  6.042383126281e-05    b8 -1.247521040900e-06
    Tmin 2.00e-01   <sv>(Tmin) 1.23e-12   <sv>max 1.15e-07   Error 8.64e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.13 $ e + H_2^+(v) \rightarrow e + H_2^+(2p\pi_u) \rightarrow e + H^+ + H(n=2),  (v=0\ldots 9)$}






%     +           +*              +    *
%e + H (v) T e + H  (2p! ) T e + H  + H (n=2)   (v=0-9)
%     2           2     u








\begin{small}\begin{verbatim}
   b0 -3.408905929046e+01    b1  1.573560727511e+01    b2 -6.992177456733e+00
   b3  1.852216261706e+00    b4 -3.130312806531e-01    b5  3.383704123189e-02
   b6 -2.265770525273e-03    b7  8.565603779673e-05    b8 -1.398131377085e-06
    Tmin 2.00e+00   <sv>(Tmin) 5.03e-12   <sv>max 1.77e-08   Error 2.05e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.14 $  e + H_2^+(v) \rightarrow H(1s) + H(n)   (v=0\ldots 9, n \geq 2)$}


\begin{small}\begin{verbatim}
   b0 -1.670435653561e+01    b1 -6.035644995682e-01    b2 -1.942745783445e-08
   b3 -2.005952284492e-07    b4  2.962996104431e-08    b5  2.134293274971e-08
   b6 -6.353973401838e-09    b7  6.152557460831e-10    b8 -2.025361858319e-11
    Tmin 1.00e-01   <sv>(Tmin) 2.23e-07   <sv>max 2.23e-07   Error 3.30e-13
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.15 $  e + H_3^+ \rightarrow H + H + H$ or $\rightarrow H_2(v > 5) + H(n=2)$}


\begin{small}\begin{verbatim}
   b0 -1.700270758355e+01    b1 -4.050073042947e-01    b2  1.018733477232e-08
   b3 -1.695586285687e-08    b4  1.564311217508e-10    b5  1.979725412288e-09
   b6 -4.395545994733e-10    b7  3.584926377078e-11    b8 -1.024189019465e-12
    Tmin 1.00e-01   <sv>(Tmin) 1.05e-07   <sv>max 1.05e-07   Error 3.27e-15
\end{verbatim}\end{small}







\newpage
\subsection{
Reaction 2.2.16 $  e + H_3^+ \rightarrow e + H^+ + 2H$}


\begin{small}\begin{verbatim}
   b0 -3.078408636631e+01    b1  1.509421488513e+01    b2 -7.349167207324e+00
   b3  2.320966107642e+00    b4 -4.818077551719e-01    b5  6.389229162737e-02
   b6 -5.161880953089e-03    b7  2.303985092606e-04    b8 -4.344846146197e-06
    Tmin 1.26e+00   <sv>(Tmin) 9.46e-13   <sv>max 4.18e-07   Error 6.20e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.2.17 $  e + H_2(v \geq 4) \rightarrow (H_2^-) \rightarrow H^- + H$}


\begin{small}\begin{verbatim}
   b0 -1.774398466232e+01    b1 -6.207038732492e-01    b2 -2.811412695673e-01
   b3  2.540958044519e-02    b4  6.643467825225e-03    b5 -8.877629159412e-04
   b6 -3.705776394283e-04    b7  9.313511559362e-05    b8 -5.995758360037e-06
    Tmin 1.00e-01   <sv>(Tmin) 1.58e-08   <sv>max 2.70e-08   Error 4.67e-07
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.1a $e + He(1s^21S) \rightarrow e + He(1s^12p^11P)$}






%         2 1            *      1
%e + He(1s | S) T e  + He (1s2p| P)









\begin{small}\begin{verbatim}
   b0 -4.076450793433e+01    b1  1.847216050626e+01    b2 -7.553534847500e+00
   b3  1.936036716566e+00    b4 -3.278509524847e-01    b5  3.627243238755e-02
   b6 -2.509995616613e-03    b7  9.829302307697e-05    b8 -1.659516418994e-06
    Tmin 3.98e+00   <sv>(Tmin) 7.72e-12   <sv>max 6.23e-09   Error 1.17e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.1b $e + He(1s^21S) \rightarrow e + He(1s^13p^11P)$}






%         2 1           *      1
%e + He(1s | S) T e + He (1s3p| P)









\begin{small}\begin{verbatim}
   b0 -4.439802014466e+01    b1  2.170928173941e+01    b2 -9.582182742745e+00
   b3  2.631183876455e+00    b4 -4.687644097236e-01    b5  5.361959275824e-02
   b6 -3.786601021417e-03    b7  1.500190728471e-04    b8 -2.548241584846e-06
    Tmin 5.01e+00   <sv>(Tmin) 5.50e-12   <sv>max 1.55e-09   Error 1.10e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.2 $e + He(1s^21S) \rightarrow e + He(1s^12s^11S)$}






%         2 1           *      1
%e + He(1s | S) T e + He (1s2s| S)









\begin{small}\begin{verbatim}
   b0 -3.944902284550e+01    b1  1.801440475215e+01    b2 -7.941287139217e+00
   b3  2.108879073816e+00    b4 -3.656365579422e-01    b5  4.130418209599e-02
   b6 -2.921666597766e-03    b7  1.171506777488e-04    b8 -2.027094391374e-06
    Tmin 3.16e+00   <sv>(Tmin) 2.84e-12   <sv>max 7.92e-10   Error 4.16e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.3a $  e + He(1s^21S) \rightarrow e + He(1s^12s^13S)$}


\begin{small}\begin{verbatim}
   b0 -3.907389635096e+01    b1  1.922614839789e+01    b2 -9.704341826798e+00
   b3  3.077375531860e+00    b4 -6.879793654863e-01    b5  1.062748336765e-01
   b6 -1.074378374967e-02    b7  6.372192184143e-04    b8 -1.676476511183e-05
    Tmin 3.16e+00   <sv>(Tmin) 4.52e-12   <sv>max 2.53e-10   Error 8.14e-10
\end{verbatim}\end{small}







\newpage
\subsection{
Reaction 2.3.3b $  e + He(1s^21S) \rightarrow e + He(1s^12p^13P)$}


\begin{small}\begin{verbatim}
   b0 -4.126478834982e+01    b1  2.115462440402e+01    b2 -1.037798544679e+01
   b3  3.223448557463e+00    b4 -7.047523358686e-01    b5  1.058143518376e-01
   b6 -1.030712489010e-02    b7  5.837301581720e-04    b8 -1.454656422289e-05
    Tmin 3.98e+00   <sv>(Tmin) 8.87e-12   <sv>max 3.32e-10   Error 8.73e-10
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.3c $  e + He(1s^21S) \rightarrow e + He(1s^13s^13S)$}


\begin{small}\begin{verbatim}
   b0 -4.403421631102e+01    b1  2.245729554242e+01    b2 -1.077239790242e+01
   b3  3.245104419002e+00    b4 -6.897865199057e-01    b5  1.022237988347e-01
   b6 -1.003860681229e-02    b7  5.860847901785e-04    b8 -1.537517028977e-05
    Tmin 5.01e+00   <sv>(Tmin) 5.43e-12   <sv>max 9.25e-11   Error 7.14e-10
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.3d $  e + He(1s^21S) \rightarrow e + He(1s^13p^13P)$}


\begin{small}\begin{verbatim}
   b0 -4.364496383346e+01    b1  2.269089069271e+01    b2 -1.084808588246e+01
   b3  3.247690604813e+00    b4 -6.828905628843e-01    b5  9.957070020879e-02
   b6 -9.564409022565e-03    b7  5.429268148822e-04    b8 -1.376622041888e-05
    Tmin 5.01e+00   <sv>(Tmin) 9.95e-12   <sv>max 1.79e-10   Error 6.08e-10
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.4a $  e + He(1s^12s^13S) \rightarrow e + He(1s^12s^11S)$}


\begin{small}\begin{verbatim}
   b0 -1.744584533214e+01    b1  7.146118553487e-01    b2 -4.873579904205e-01
   b3  1.481188090592e-01    b4 -3.507761998312e-02    b5  5.690374429946e-03
   b6 -5.623763509155e-04    b7  3.001973812574e-05    b8 -6.601806234046e-07
    Tmin 1.00e-01   <sv>(Tmin) 1.46e-11   <sv>max 3.80e-08   Error 5.08e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.4b $  e + He(1s^12s^13S) \rightarrow e + He(1s^12p^11P)$}


\begin{small}\begin{verbatim}
   b0 -1.844735966200e+01    b1  1.427274973351e+00    b2 -8.091153742158e-01
   b3  2.487008240878e-01    b4 -5.643723514177e-02    b5  8.601493865150e-03
   b6 -8.023972821093e-04    b7  4.085320629082e-05    b8 -8.650886326975e-07
    Tmin 1.58e-01   <sv>(Tmin) 3.93e-12   <sv>max 2.52e-08   Error 4.76e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.4c $  e + He(1s^12s^11S) \rightarrow e + He(1s^12p^13P)$}


\begin{small}\begin{verbatim}
   b0 -1.615322214290e+01    b1  1.433777584524e-01    b2 -2.487826648613e-01
   b3  7.026918912149e-02    b4 -1.553687005936e-02    b5  2.421396865761e-03
   b6 -2.348531854752e-04    b7  1.243991031364e-05    b8 -2.729353858047e-07
    Tmin 1.00e-01   <sv>(Tmin) 4.15e-09   <sv>max 9.87e-08   Error 8.49e-06
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 2.3.4d $  e + He(1s^12p^13P) \rightarrow e + He(1s^12p^11P)$}


\begin{small}\begin{verbatim}
   b0 -1.799224192385e+01    b1  5.839648278021e-03    b2 -1.939973920965e-01
   b3  5.349246643243e-02    b4 -1.150308510199e-02    b5  1.759192625459e-03
   b6 -1.689530419550e-04    b7  8.909865872231e-06    b8 -1.951982101314e-07
    Tmin 1.00e-01   <sv>(Tmin) 1.76e-09   <sv>max 1.53e-08   Error 4.25e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.5a $  e + He(1s^12s^11S) \rightarrow e + He(1s^12p^11P)$}


\begin{small}\begin{verbatim}
   b0 -1.421481564800e+01    b1  9.816324588875e-01    b2 -3.700239299608e-01
   b3  9.320731611434e-02    b4 -2.517642644099e-02    b5  4.899403741414e-03
   b6 -5.506956047085e-04    b7  3.192647759391e-05    b8 -7.407861678228e-07
    Tmin 1.00e-01   <sv>(Tmin) 1.01e-09   <sv>max 1.78e-06   Error 7.22e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.5b $  e + He(1s^12s^13S) \rightarrow e + He(1s^12p^13P)$}


\begin{small}\begin{verbatim}
   b0 -1.524234054303e+01    b1  1.457459036199e+00    b2 -6.089961105515e-01
   b3  1.908341260995e-01    b4 -4.902955652013e-02    b5  8.357212748265e-03
   b6 -8.436990703093e-04    b7  4.535984449474e-05    b8 -9.983744250475e-07
    Tmin 1.00e-01   <sv>(Tmin) 3.98e-12   <sv>max 1.15e-06   Error 1.38e-04
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.6a $  e + He(1s^12s^11S) \rightarrow e + He(1s^13p^11P)$}


\begin{small}\begin{verbatim}
   b0 -2.012491737344e+01    b1  2.975868118455e+00    b2 -1.241263834768e+00
   b3  4.133514681102e-01    b4 -1.015874512196e-01    b5  1.570108000623e-02
   b6 -1.424919814936e-03    b7  6.934961916285e-05    b8 -1.396714673826e-06
    Tmin 3.16e-01   <sv>(Tmin) 4.88e-12   <sv>max 7.94e-08   Error 9.99e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.6b $  e + He(1s^12s^13S) \rightarrow e + He(1s^13p^13P)$}


\begin{small}\begin{verbatim}
   b0 -2.168967273514e+01    b1  3.469927386366e+00    b2 -1.500284971036e+00
   b3  4.514495446931e-01    b4 -9.830380729357e-02    b5  1.412098625701e-02
   b6 -1.235528152366e-03    b7  5.912904162725e-05    b8 -1.182410155429e-06
    Tmin 3.98e-01   <sv>(Tmin) 2.79e-12   <sv>max 1.86e-08   Error 2.22e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.7a $  e + He(1s^12p^11P) \rightarrow e + He(1s^13d^11D)$}


\begin{small}\begin{verbatim}
   b0 -1.685934192513e+01    b1  2.084943159821e+00    b2 -8.554198255397e-01
   b3  2.987507152419e-01    b4 -8.260619461169e-02    b5  1.427561766421e-02
   b6 -1.419997912094e-03    b7  7.446342219961e-05    b8 -1.594736923452e-06
    Tmin 1.58e-01   <sv>(Tmin) 2.29e-12   <sv>max 6.12e-07   Error 6.74e-05
\end{verbatim}\end{small}








\newpage
\subsection{
Reaction 2.3.7b $  e + He(1s^12s^13P) \rightarrow e + He(1s^13d^13D)$}


\begin{small}\begin{verbatim}
   b0 -1.733661165939e+01    b1  2.317215831044e+00    b2 -9.924882089292e-01
   b3  3.415918344358e-01    b4 -9.030135166591e-02    b5  1.508647305121e-02
   b6 -1.468232978539e-03    b7  7.588691677324e-05    b8 -1.608841144485e-06
    Tmin 2.00e-01   <sv>(Tmin) 5.66e-12   <sv>max 4.46e-07   Error 6.51e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.9 $   e + He(1s^21S) \rightarrow e + He^+ + e$}


\begin{small}\begin{verbatim}
   b0 -4.409864886561e+01    b1  2.391596563469e+01    b2 -1.075323019821e+01
   b3  3.058038757198e+00    b4 -5.685118909884e-01    b5  6.795391233790e-02
   b6 -5.009056101857e-03    b7  2.067236157507e-04    b8 -3.649161410833e-06
    Tmin 3.16e+00   <sv>(Tmin) 1.83e-12   <sv>max 2.46e-08   Error 1.06e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.10a $ e + He(1s^12s^11S) \rightarrow e + He^+(1s) + e$}


\begin{small}\begin{verbatim}
   b0 -2.043240580802e+01    b1  4.673025479860e+00    b2 -2.068053911581e+00
   b3  6.103799741884e-01    b4 -1.268205164080e-01    b5  1.740804412692e-02
   b6 -1.474132011694e-03    b7  6.914279610834e-05    b8 -1.368015031384e-06
    Tmin 3.98e-01   <sv>(Tmin) 1.72e-12   <sv>max 2.04e-07   Error 3.70e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.10b $  e + He(1s^12p^11P) \rightarrow e + He^+(1s) + e$}


\begin{small}\begin{verbatim}
   b0 -1.946719737710e+01    b1  4.039554859050e+00    b2 -1.792264505398e+00
   b3  5.357588980704e-01    b4 -1.142854169815e-01    b5  1.614022386298e-02
   b6 -1.401937207088e-03    b7  6.717110442234e-05    b8 -1.352531071210e-06
    Tmin 3.16e-01   <sv>(Tmin) 1.07e-12   <sv>max 2.61e-07   Error 4.96e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.10c $  e + He(1s^12s^13S) \rightarrow e + He^+(1s) + e$}


\begin{small}\begin{verbatim}
   b0 -2.061635956597e+01    b1  5.212998266179e+00    b2 -2.421560769610e+00
   b3  7.237890101587e-01    b4 -1.480837244899e-01    b5  1.981796970055e-02
   b6 -1.635383361916e-03    b7  7.495465496705e-05    b8 -1.454005255301e-06
    Tmin 5.01e-01   <sv>(Tmin) 7.17e-12   <sv>max 2.12e-07   Error 2.71e-05
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.10d $ e + He(1s^12p^13P) \rightarrow e + He^+(1s) + e$}


\begin{small}\begin{verbatim}
   b0 -1.988624861383e+01    b1  4.310402355871e+00    b2 -1.896654131474e+00
   b3  5.547033134672e-01    b4 -1.146241097190e-01    b5  1.568822815337e-02
   b6 -1.326558850059e-03    b7  6.217750779265e-05    b8 -1.229838359991e-06
    Tmin 3.98e-01   <sv>(Tmin) 5.08e-12   <sv>max 2.34e-07   Error 3.01e-05
\end{verbatim}\end{small}







\newpage
\subsection{
Reaction 2.3.12 $  e + He(1s^1nl^1 \{2S+1\}L) \rightarrow e + He^+(nl) + e$}


\begin{small}\begin{verbatim}
   b0 -6.896861656133e+01    b1  4.483212792736e+01    b2 -1.838301143477e+01
   b3  4.508647323762e+00    b4 -7.148481765711e-01    b5  7.375319623123e-02
   b6 -4.780158615887e-03    b7  1.766513036839e-04    b8 -2.837371604097e-06
    Tmin 7.94e+00   <sv>(Tmin) 7.62e-12   <sv>max 5.15e-09   Error 1.12e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.13 $  e + He^+(1s) \rightarrow He(1s^1nl^1 \{2S+1\}L) + hv$}

       See text for analytic formulas.

\newpage
\subsection{
Reaction 2.3.14 $  e + He^+(1s) \rightarrow e + He^+(2p)$}


\begin{small}\begin{verbatim}
   b0 -5.731132225657e+01    b1  3.618757468205e+01    b2 -1.568012557533e+01
   b3  4.060438624043e+00    b4 -6.700744538238e-01    b5  7.100638013026e-02
   b6 -4.682434354620e-03    b7  1.749898327054e-04    b8 -2.831521166310e-06
    Tmin 5.01e+00   <sv>(Tmin) 2.96e-12   <sv>max 1.37e-08   Error 1.24e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.15 $  e + He^+(1s) \rightarrow e + He^+(2s)$}


\begin{small}\begin{verbatim}
   b0 -5.754975783112e+01    b1  3.459060731107e+01    b2 -1.462527320845e+01
   b3  3.680688204381e+00    b4 -5.969493660071e-01    b5  6.279719136636e-02
   b6 -4.138222038101e-03    b7  1.551309719300e-04    b8 -2.522897333444e-06
    Tmin 6.31e+00   <sv>(Tmin) 4.41e-12   <sv>max 1.23e-09   Error 1.19e-06
\end{verbatim}\end{small}

\newpage
\subsection{
Reaction 2.3.19 $  e + He^+(1s) \rightarrow e + He^{++} + e$}


\begin{small}\begin{verbatim}
   b0 -6.871040990212e+01    b1  4.393347632635e+01    b2 -1.848066993568e+01
   b3  4.701626486759e+00    b4 -7.692466334492e-01    b5  8.113042097303e-02
   b6 -5.324020628287e-03    b7  1.975705312221e-04    b8 -3.165581065665e-06
    Tmin 7.94e+00   <sv>(Tmin) 2.62e-12   <sv>max 4.01e-09   Error 1.04e-06
\end{verbatim}\end{small}

\newpage

\subsection{
Reaction 3.1.8 $  p + H(1s) \rightarrow H(1s) + p$}

added by DR: single parameter Maxwellian rate coeff., vs. $T_p$, for neutral target at rest,
obtained from corresponding fit for Beam-Maxwellian rate coeff. evaluated at $E_b =0.1$ eV
and then verified by independent integration of cross section with proper low energy asymptotics.

\begin{small}\begin{verbatim}
   b0 -1.850280000000E+01    b1  3.708409000000E-01    b2  7.949876000000E-03
   b3 -6.143769000000E-04    b4 -4.698969000000E-04    b5 -4.096807000000E-04
   b6  1.440382000000E-04    b7 -1.514243000000E-05    b8  5.122435000000E-07
\end{verbatim}\end{small}

\subsection{
Reaction 3.2.3 $  p + H_2(v=0) \rightarrow H(1s) + H_2^+$}

Note:  Ground state H2 only.

added by DR: single parameter Maxwellian rate coeff., vs. $T_p$, for neutral target at rest,
obtained from corresponding fit for Beam-Maxwellian rate coeff. evaluated at $E_b =0.1$ eV
and then verified by independent integration of cross section with proper low energy asymptotics.

\begin{small}\begin{verbatim}
   b0 -2.440996809955E+01    b1  2.552627389749E+00    b2 -2.608194219039E+00
   b3  1.347571390219E+00    b4 -3.646182244708E-01    b5  5.938400660590E-02,
   b6 -5.795480327782E-03    b7  3.075899232458E-04    b8 -6.769294455276E-06,

\end{verbatim}\end{small}

\newpage




\subsection{
Reaction 7.1.1 $   e + H^- \rightarrow e + H(1s) + e$}


\begin{small}\begin{verbatim}
   b0 -1.801849334273e+01    b1  2.360852208681e+00    b2 -2.827443061704e-01
   b3  1.623316639567e-02    b4 -3.365012031363e-02    b5  1.178329782711e-02
   b6 -1.656194699504e-03    b7  1.068275202678e-04    b8 -2.631285809207e-06
    Tmin 1.26e-01   <sv>(Tmin) 7.72e-12   <sv>max 9.73e-07   Error 3.51e-03
\end{verbatim}\end{small}







\newpage
\subsection{
Reaction 7.1.2 $   e + H^- \rightarrow e + H^+ + 2e$}


\begin{small}\begin{verbatim}
   b0 -3.637051952368e+01    b1  1.586803736621e+01    b2 -6.478287148158e+00
   b3  1.735140500106e+00    b4 -3.233529702765e-01    b5  4.020531565638e-02
   b6 -3.114827827749e-03    b7  1.347768741748e-04    b8 -2.478586915713e-06
    Tmin 2.51e+00   <sv>(Tmin) 4.61e-12   <sv>max 2.15e-08   Error 3.47e-06
\end{verbatim}\end{small}







\newpage
\section{H.3   DOUBLE POLYNOMIAL FITS FOR $<\sigma v>$}

\subsection{
Reaction 3.1.1 $ p + H(1s) \rightarrow p + H(2p)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -6.261494333673e+01  1.976921673516e+01 -4.770700042332e+00
     1      2.417692686638e+01 -1.641857278453e+01  5.395012240434e+00
     2     -4.051480211975e+00  4.191026443943e+00 -2.252096048936e+00
     3     -1.318153914548e+00  1.189223903948e-01  4.211072262111e-01
     4      7.528061358848e-01 -2.607978652180e-01 -2.386725153241e-02
     5     -1.498666287447e-01  5.494605745283e-02 -3.642074979445e-03
     6      1.512983951035e-02 -5.414151972843e-03  6.902343394169e-04
     7     -7.735934229437e-04  2.658505260322e-04 -4.272194199546e-05
     8      1.590699544686e-05 -5.245923671227e-06  9.478841315945e-07

    E Index         3                   4                   5
  T Index
     0      1.033248569152e+00 -2.868779139503e-01  6.404381294137e-02
     1     -1.414868849757e+00  3.184423304843e-01 -4.982800665252e-02
     2      7.292508717933e-01 -1.433443925906e-01  1.696153624540e-02
     3     -1.843635318950e-01  3.265971640208e-02 -2.763613623053e-03
     4      2.201347577554e-02 -3.551163806974e-03  2.007525885427e-04
     5     -5.612540938735e-04  4.481699611261e-05  2.535074888925e-06
     6     -1.334876998570e-04  2.919499398918e-05 -1.991423479045e-06
     7      1.298404615938e-05 -2.701941401993e-06  1.791270932567e-07
     8     -3.581309543014e-07  7.633070244335e-08 -5.593302645030e-09

    E Index         6                   7                   8
  T Index
     0     -8.140654835343e-03  5.192124519721e-04 -1.297112781664e-05
     1      4.662131405403e-03 -2.320827027679e-04  4.724538772162e-06
     2     -1.171374695689e-03  4.320048440550e-05 -6.523542632649e-07
     3      9.516447719628e-05  4.017247431177e-07 -7.031689068197e-08
     4      2.320428113156e-06 -6.344720465694e-07  1.688277259644e-08
     5      8.398201633252e-08 -4.021594027671e-08  1.420992975620e-09
     6     -1.026348613432e-07  1.519024137139e-08 -3.851106645960e-10
     7      5.539305326395e-09 -8.915090538633e-10  1.877667458640e-11
     8     -8.712370707504e-12  1.172349575278e-11 -1.236556517200e-13

     Error  4.08e-03 (D)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.1.2 $   p + H(1s) \rightarrow p + H(2s)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -3.303672309056e+01  5.435398491796e-02 -4.479069874895e-01
     1      8.129573868895e-02 -1.573070446304e-01 -2.343645075304e-01
     2     -1.367357596276e+00  1.264162602757e-01  9.132454530131e-02
     3      2.430769064611e-01 -4.277967668065e-03  4.379389784137e-02
     4      1.762729645847e-01 -1.171278439692e-02 -2.284640793483e-02
     5     -6.257579731175e-02  3.045403958595e-03  4.069924950563e-03
     6      8.093824710704e-03 -3.259338404156e-04 -3.654555742323e-04
     7     -4.766590709264e-04  1.630335031310e-05  1.697015649467e-05
     8      1.073880975629e-05 -3.135178689449e-07 -3.290603109143e-07

    E Index         3                   4                   5
  T Index
     0     -6.207816515028e-02  4.982680171938e-02  2.631060067396e-03
     1      4.641882710210e-02  7.584683292302e-03 -1.878798454594e-03
     2     -2.504726147521e-02  3.623287819690e-03 -5.425414507567e-04
     3     -3.802802560195e-03 -4.458407685510e-03  1.053772036026e-03
     4      4.085275116537e-03  6.304577672385e-04 -2.393639075300e-04
     5     -8.856894051785e-04  6.116944101767e-05  8.195766073173e-06
     6      8.857371143951e-05 -1.967353079496e-05  2.374701722762e-06
     7     -4.353073546873e-06  1.500381004201e-06 -2.478107830550e-07
     8      8.576165925108e-08 -3.781894053698e-08  6.945366389669e-09

    E Index         6                   7                   8
  T Index
     0     -2.180659228486e-03  2.245818225902e-04 -7.072385408498e-06
     1      2.999568075912e-05  1.180308123781e-05 -5.753191579259e-07
     2      7.217756265772e-05 -5.369814852090e-06  1.555461051039e-07
     3     -8.298313802105e-05  1.948415887525e-06  1.941860942555e-08
     4      2.472786370494e-05 -1.023360259850e-06  1.277393659635e-08
     5     -2.180680441264e-06  1.728454123757e-07 -4.691407260680e-09
     6     -3.745411947057e-08 -1.145030836069e-08  5.454860678474e-10
     7      1.282096306376e-08  2.790689700798e-10 -2.878902181247e-11
     8     -4.240491240271e-10 -1.382267062457e-12  6.143782726250e-13

     Error  4.49e-03 (D)
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 3.1.3 $   p + H(2s) \rightarrow p + H(2p)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -9.990724901145e+00  5.351348305631e-01  4.939529241653e-02
     1      6.537727443011e-01 -5.280296904194e-01  6.425969893761e-02
     2     -1.241140027113e-01  2.060077489360e-01 -7.862588561762e-02
     3      7.149154773117e-03 -4.485819636159e-02  2.658545734784e-02
     4     -5.339018890395e-03  6.460674060103e-03 -3.577827264905e-03
     5      1.800856199793e-03 -6.601657449132e-04  8.937792817252e-05
     6     -2.467032039166e-04  4.579703537623e-05  2.480990637873e-05
     7      1.545051869941e-05 -1.863242109937e-06 -2.397125514853e-06
     8     -3.690040224068e-07  3.246974149460e-08  6.587817957450e-08

    E Index         3                   4                   5
  T Index
     0     -5.106541840021e-02 -1.828656123929e-03  3.278050583806e-03
     1      3.146872034794e-02 -7.747008551462e-03 -2.009436212555e-05
     2     -1.590857166173e-03  6.697068316092e-03 -1.587286144423e-03
     3     -2.091225617309e-03 -1.807442248515e-03  5.583369851577e-04
     4      6.191341147148e-04  1.098333544712e-04 -5.443789910797e-05
     5     -1.018025884107e-04  3.338304419913e-05 -3.089670487553e-06
     6      1.151440883472e-05 -6.871587246464e-06  8.975741200024e-07
     7     -7.605187577154e-07  4.906237903385e-07 -5.574178438230e-08
     8      2.067476350932e-08 -1.254526895853e-08  1.104305607237e-09

    E Index         6                   7                   8
  T Index
     0     -5.540100092190e-04  3.801593003417e-05 -9.608738344988e-07
     1      1.517188390097e-04 -1.513420504861e-05  4.584486596613e-07
     2      1.684564123048e-04 -8.692146674273e-06  1.773890443608e-07
     3     -6.883882904255e-05  4.004504488417e-06 -9.090763486841e-08
     4      7.663155026086e-06 -4.749223957327e-07  1.111022258304e-08
     5     -7.483785818283e-08  2.292140559850e-08 -8.177571335015e-10
     6     -1.732595885303e-08 -3.335002305887e-09  1.547780692175e-10
     7     -1.171822397960e-09  4.663773505803e-10 -1.825227169097e-11
     8      1.095408126793e-10 -1.896445830085e-11  6.805323199305e-13

     Error  1.02e-03 (C)
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 3.1.6 $   p + H(1s) \rightarrow p + H^+ + e$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -1.617454916209e+02  1.767238902030e+01 -4.334843983767e+01
     1      1.021458246570e+02 -7.102574692619e+01  3.855259623260e+01
     2     -5.712267930902e+01  4.246688953154e+01 -1.316883030631e+01
     3      2.140540272484e+01 -1.128638171243e+01  2.145592145856e+00
     4     -4.767517412803e+00  1.661679851896e+00 -1.467281287038e-01
     5      6.293295208376e-01 -1.476754423056e-01 -2.915256218527e-03
     6     -4.858173640838e-02  8.175790218529e-03  1.092542891192e-03
     7      2.031177914273e-03 -2.732531913524e-04 -6.205102802216e-05
     8     -3.557982934756e-05  4.398387454014e-06  1.158798945435e-06

    E Index         3                   4                   5
  T Index
     0      2.464254915383e+01 -5.439093405254e+00  5.959975304236e-01
     1     -1.283426276878e+01  2.357085001656e+00 -2.391382925527e-01
     2      2.369698902002e+00 -2.961732508220e-01  2.789277301925e-02
     3     -1.506665823159e-01 -9.917174972226e-04  8.562387824450e-05
     4     -8.144926683660e-03  1.935894665907e-03 -1.340759667335e-04
     5      2.231505500086e-03 -1.679264493005e-05 -5.927455645560e-06
     6     -2.210941355372e-04  5.532386419162e-08  5.820264508685e-07
     7      1.310924337643e-05 -1.121430499351e-06  7.694068657107e-08
     8     -3.431837053957e-07  5.960280736984e-08 -4.972708712807e-09

    E Index         6                   7                   8
  T Index
     0     -3.361958123977e-02  8.706597041685e-04 -6.359765062372e-06
     1      1.289667246580e-02 -3.140899683782e-04  1.742836004704e-06
     2     -1.858739201548e-03  7.343984485463e-05 -1.235536456998e-06
     3      9.235982885753e-05 -8.601564864429e-06  2.257852760280e-07
     4      9.875232214392e-06 -6.467790579320e-07  1.608335682237e-08
     5     -1.680823118052e-06  1.734797315767e-07 -3.855914336143e-09
     6      3.019916624608e-08  2.523651535182e-09 -3.556222618473e-10
     7      6.889325889968e-09 -1.719633613108e-09  7.627265694554e-11
     8     -3.171970185702e-10  7.332933714195e-11 -2.960493966948e-12

     Error  2.51e-03 (C)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.1.8 $   p + H(1s) \rightarrow H(1s) + p$}

original fit from Springer book replaced by this one, which has better
consistency with cross section, hence: better energy conservation

\begin{small}\begin{verbatim}
        E-Index:     0                     1                     2
 T-Index:
        0   -1.831670498376D+01    1.650239332070D-01    5.025740610454D-02
        1    2.143624996483D-01   -1.067658289373D-01   -5.304993033743D-03
        2    5.139117192662D-02    9.536923957409D-03   -1.306075129405D-02
        3   -9.896180369559D-04    6.315097684976D-03    2.655464630308D-03
        4   -2.495327546080D-03   -1.265503371044D-03    7.569269700468D-04
        5   -2.417046684097D-05   -6.945512319613D-05   -2.956984088728D-04
        6    1.177406072793D-04    3.698501620365D-05    3.424317896619D-05
        7   -1.483036457978D-05   -3.348172574417D-06   -1.527018819072D-06
        8    5.351909441226D-07    9.728230870242D-08    1.676354786072D-08

        E-Index:     3                     4                     5
 T-Index:
        0    5.288358515136D-03   -2.437122342843D-03   -4.461891214720D-04
        1    8.289383645942D-03   -9.698773663345D-05   -4.470180279338D-04
        2   -1.033166370333D-03    1.280464204775D-03   -8.453294908907D-05
        3   -1.365781346175D-03   -1.859939123743D-04    1.237942304972D-04
        4    2.756946036257D-04   -1.107375149384D-04   -7.217379426085D-06
        5    2.318277483195D-05    3.704494397140D-05   -6.066558692480D-06
        6   -9.815693511794D-06   -4.285719813022D-06    1.169257650609D-06
        7    8.362050692462D-07    2.058392726953D-07   -7.463594884928D-08
        8   -2.237567830699D-08   -3.081685803820D-09    1.450862501121D-09

        E-Index:     6                     7                     8
 T-Index:
        0    1.731631548110D-04   -1.588434781959D-05    4.482291414386D-07
        1    7.944326905066D-05   -5.303688417551D-06    1.235167254501D-07
        2   -3.040874906105D-05    4.747888095498D-06   -1.923953750574D-07
        3   -1.588253432932D-05    6.603560345800D-07   -1.970606344918D-09
        4    5.769971321188D-06   -6.717311113584D-07    2.440961351104D-08
        5   -4.951573401626D-07    1.437520597154D-07   -6.998724470004D-09
        6   -4.968953461875D-10   -1.618948982477D-08    9.440094842562D-10
        7    5.924370389093D-10    1.078208689229D-09   -6.619767848464D-11
        8    4.434231893204D-11   -3.324377862622D-11    1.935019679501D-12

 Max. rel. Error:   1.1026 %
 Mean rel. Error:   0.3105 %

\end{verbatim}\end{small}


\newpage
\subsection{
Reaction 3.1.9 $   p + H(1s) \rightarrow H(2p) + p$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -7.537230406957e+01  4.362515351094e+01 -1.318797741915e+01
     1      5.056939990348e+01 -4.322632990301e+01  1.243803991192e+01
     2     -2.304556023867e+01  1.808673367993e+01 -5.041889107660e+00
     3      5.946693576057e+00 -4.192991836651e+00  1.150647211570e+00
     4     -9.025227545139e-01  5.941171802341e-01 -1.616667927236e-01
     5      8.062506740891e-02 -5.340479630862e-02  1.424698941315e-02
     6     -3.996458180607e-03  3.028277898563e-03 -7.611581001083e-04
     7      9.092787501258e-05 -1.009830499229e-04  2.216348373380e-05
     8     -4.227552753922e-07  1.538300832396e-06 -2.615703495579e-07

    E Index         3                   4                   5
  T Index
     0      3.884832686395e-01  6.956399122965e-01 -1.768051294154e-01
     1     -6.391999122917e-01 -4.102677587957e-01  1.022299957977e-01
     2      4.302521809170e-01  6.674825725277e-02 -1.905495347022e-02
     3     -1.437283377093e-01  4.745169406603e-03  8.000515536149e-04
     4      2.533878850824e-02 -2.550521752939e-03  1.202073413278e-04
     5     -2.271818162002e-03  2.517099528196e-04 -1.115096374756e-05
     6      7.750647375638e-05 -3.466368199953e-06  1.352159519053e-07
     7      1.503739282859e-06 -7.169612925965e-07 -3.978675907993e-09
     8     -1.204847091978e-07  2.957975348352e-08  7.777167529587e-10

    E Index         6                   7                   8
  T Index
     0      1.957698184804e-02 -1.056851602712e-03  2.265661905063e-05
     1     -1.064957247532e-02  5.395365812293e-04 -1.089046627301e-05
     2      1.819440410123e-03 -8.006107003062e-05  1.352840661769e-06
     3     -9.926992183313e-05  4.294899850373e-06 -6.488121891471e-08
     4      6.513242953616e-06 -1.107878363495e-06  3.840860903452e-08
     5     -1.478504972220e-06  2.121938496244e-07 -7.452662892489e-09
     6      1.959691983490e-08 -4.994907944039e-09  2.384601530335e-10
     7      1.365715388161e-08 -1.203216169780e-09  3.140684652583e-11
     8     -6.927312822621e-10  6.265289730204e-11 -1.756983474278e-12

     Error  2.14e-03 (C)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.1.10 $  p + H(1s) \rightarrow H(2s) + p$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -9.454040572046e+01  3.575745803548e+01 -1.510443829941e+01
     1      6.768817040733e+01 -5.227279271076e+01  1.701370184857e+01
     2     -3.843706771660e+01  2.980450196644e+01 -8.131009677919e+00
     3      1.385221298623e+01 -9.039653668981e+00  2.086424489113e+00
     4     -3.117564250516e+00  1.631432036287e+00 -3.080742439399e-01
     5      4.327242290244e-01 -1.819412845040e-01  2.620862225175e-02
     6     -3.575580797373e-02  1.236067989017e-02 -1.200955067032e-03
     7      1.606326046639e-03 -4.707337881721e-04  2.380595128998e-05
     8     -3.014539201968e-05  7.726558074630e-06 -5.572946409399e-08

    E Index         3                   4                   5
  T Index
     0      4.295083359171e+00 -5.229601897556e-01 -7.946315775931e-03
     1     -3.003110377892e+00  3.010370634031e-01 -1.508174268564e-02
     2      9.231651795395e-01 -3.487948145308e-02  1.651938581961e-03
     3     -1.650992173822e-01 -7.573668823425e-03  1.643120830451e-03
     4      1.839941901217e-02  1.873700049273e-03 -3.898508080526e-04
     5     -1.170843781709e-03 -7.837602630428e-05  1.901716727239e-05
     6      2.536771557591e-05 -8.991629432058e-06  1.917169241407e-06
     7      1.205300240917e-06  8.541173405977e-07 -2.062752779297e-07
     8     -5.817548248007e-08 -1.874443584825e-08  4.932865323528e-09

    E Index         6                   7                   8
  T Index
     0      7.914390432835e-03 -6.838905496435e-04  1.882232072017e-05
     1      5.550437127230e-05  2.964326783525e-05 -9.736741374779e-07
     2     -6.142591967279e-04  6.119831154619e-05 -1.838162822528e-06
     3     -7.419534566620e-06 -7.945476516010e-06  3.130407892340e-07
     4      2.719285839940e-05 -8.813515513714e-07  1.079647425709e-08
     5     -2.516543465515e-06  1.865515247748e-07 -5.301524876773e-09
     6     -7.319251234821e-08 -5.372098865883e-09  3.196679636762e-10
     7      1.560273243360e-08 -3.793947135803e-10 -2.054614693679e-12
     8     -4.284893236218e-10  1.548062509417e-11 -1.558508528883e-13

     Error  2.70e-03 (C)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.1.11a $ p + H(n=2) \rightarrow H(n=2) + p$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -1.719825327366e+01  1.884984890020e-01  6.897051389182e-02
     1      2.142580064300e-01 -9.872388055616e-02 -3.940258746400e-03
     2      5.168472844325e-02  6.212920647036e-03 -9.888896994201e-03
     3     -1.048694623894e-02  6.029698215976e-03  1.504715422531e-03
     4     -1.391648927155e-03 -9.288450680283e-04  5.238686379254e-04
     5      1.062236858414e-03 -1.207901919277e-04 -1.467630362018e-04
     6     -1.941489579494e-04  3.746697774137e-05  1.105904477472e-05
     7      1.443503540040e-05 -3.003621079325e-06 -1.018783959628e-07
     8     -3.830825345601e-07  8.083955156001e-08 -1.150674668496e-08

    E Index         3                   4                   5
  T Index
     0     -1.572342769599e-02 -3.026782383076e-03  2.133841357975e-03
     1      7.386092651403e-03 -2.707096061380e-04 -3.315460371996e-04
     2     -1.514031260298e-04  7.422527656251e-04 -9.788494576192e-05
     3     -1.084990452398e-03 -2.534332965992e-05  6.638160972083e-05
     4      1.397189710440e-04 -6.198909026340e-05  4.565982508704e-07
     5      2.978558026688e-05  1.074474230594e-05 -2.854550682552e-06
     6     -7.191352563366e-06 -2.116398505416e-07  3.026311807218e-07
     7      5.019583257618e-07 -5.860162734729e-08 -4.086656000107e-09
     8     -1.160924102260e-08  3.001361914394e-09 -3.647228557972e-10

    E Index         6                   7                   8
  T Index
     0     -3.794323219371e-04  2.766697866894e-05 -7.245291602834e-07
     1      6.222275341197e-05 -4.353916183620e-06  1.095768172868e-07
     2     -1.538008374846e-06  8.506156759757e-07 -3.579248331944e-08
     3     -1.070825967335e-05  6.727768972585e-07 -1.517922643230e-08
     4      1.624804729003e-06 -1.835711031271e-07  6.039716625198e-09
     5      1.266431527284e-07  1.074561840233e-08 -7.130630889442e-10
     6     -2.451278913609e-08 -4.162807697535e-10  6.485611244670e-11
     7      4.087633684476e-11  1.064004947231e-10 -5.907545942925e-12
     8      5.848501246633e-11 -6.316916199588e-12  2.360870657000e-13

     Error  5.81e-04 (B)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.1.11b $  p + H(n=3) \rightarrow H(n=3) + p$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -1.564176694793e+01  1.700998335355e-01  4.947885926277e-02
     1      2.232010663420e-01 -1.049739713449e-01 -2.908751470450e-03
     2      5.316235880113e-02  7.036341129098e-03 -1.117747362624e-02
     3     -4.935673795010e-03  6.200377256109e-03  1.303552526033e-03
     4     -1.741592426003e-03 -1.023534361944e-03  6.993209254704e-04
     5      4.843336390075e-04 -1.026575078128e-04 -1.690721678970e-04
     6     -4.393060568249e-05  3.646643689823e-05  1.129769317091e-05
     7      1.066531598161e-06 -3.043044894680e-06  2.706113202831e-09
     8      2.083548419270e-08  8.441512078238e-08 -1.618789305180e-08

    E Index         3                   4                   5
  T Index
     0      3.480696525110e-03 -2.016588092927e-03 -2.304544529246e-04
     1      7.235971573222e-03 -4.237602215706e-04 -2.525856005478e-04
     2     -2.219063125013e-04  8.910349218491e-04 -1.240905152629e-04
     3     -1.007225809037e-03 -5.690437985817e-06  5.076337989874e-05
     4      1.326302857329e-04 -8.434009637807e-05  6.519707374655e-06
     5      2.567668892391e-05  1.430883419261e-05 -3.208617580385e-06
     6     -6.607411884531e-06 -3.382705306787e-07  2.749197577537e-07
     7      4.871162221333e-07 -6.897801542295e-08 -1.416282255917e-09
     8     -1.204005789548e-08  3.636288208820e-09 -4.076090686778e-10

    E Index         6                   7                   8
  T Index
     0      1.218034746095e-04 -1.302517417161e-05  4.404350923087e-07
     1      4.862602710052e-05 -3.343139362692e-06  8.182936615708e-08
     2     -2.780251764272e-07  8.939610410070e-07 -3.949474200870e-08
     3     -7.792361018067e-06  4.473546907095e-07 -8.802476545107e-09
     4      9.878685208347e-07 -1.545621666271e-07  5.588732113261e-09
     5      9.561811139849e-08  1.702219787538e-08 -9.641507489238e-10
     6     -1.646787390856e-08 -1.115049016888e-09  8.683886799640e-11
     7      4.716863630756e-11  8.023274024363e-11 -4.773160877761e-12
     8      3.777088131426e-11 -3.347579230007e-12  1.292746807996e-13

     Error  1.54e-04 (A)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.2.1a $  p + H_2(j=0) \rightarrow p + H_2(j'), (j' \geq 2)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -1.931976581025e+01 -1.131727838595e-02  5.564692006285e-02
     1      1.780878236605e-01 -1.304342119382e-01 -2.977647895678e-02
     2     -2.541254437243e-02  2.555760073023e-02 -1.343274859600e-02
     3     -4.673484115780e-02  7.858332235684e-03  3.183062244762e-03
     4     -1.146770335720e-03 -1.657368695811e-03  7.282634108198e-04
     5      2.889570096820e-03 -5.065872411962e-05 -1.009959155222e-04
     6     -5.181754952484e-04  1.639669433305e-05 -2.569913821108e-05
     7      3.889651963743e-05  3.837821202667e-07  4.649279483411e-06
     8     -1.107229000254e-06 -7.670491474577e-08 -1.956375986525e-07

    E Index         3                   4                   5
  T Index
     0      4.612780090544e-02 -2.004969108653e-02 -5.405622666261e-03
     1      2.598050022977e-02  1.347793245045e-03 -2.528774951362e-03
     2     -2.445543192015e-03  2.818570059181e-03 -4.999237741132e-05
     3     -3.596822533950e-03  2.532346636968e-04  4.009000053692e-04
     4      2.613056855048e-04 -2.483817325793e-04  1.398464524064e-07
     5      1.042472672998e-04  2.267800856786e-06 -1.589742168453e-05
     6     -8.619281945578e-06  7.897307131770e-06  8.582336209267e-07
     7     -7.536640398566e-07 -9.405159896274e-07  1.327216559054e-07
     8      6.639899136555e-08  3.236749066622e-08 -9.607318326503e-09

    E Index         6                   7                   8
  T Index
     0      2.191546075602e-03 -2.320194246052e-04  8.008357976190e-06
     1      4.600974334650e-04 -3.107626515638e-05  6.945270043940e-07
     2     -1.748459008343e-04  2.776052578344e-05 -1.206654268341e-06
     3     -9.738076845118e-05  7.572697075882e-06 -1.827758690708e-07
     4      1.815503467330e-05 -2.855321802747e-06  1.239043759009e-07
     5      1.897116878857e-06  9.701076200284e-08 -1.311379859022e-08
     6     -4.399860357799e-07  2.641401745588e-08  9.621252004735e-11
     7      1.171108373785e-08 -1.727778312454e-09  2.797736054220e-11
     8      5.928009302898e-10 -5.140400246008e-13 -1.647139266864e-13

     Error  2.98e-03 (D)
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 3.2.1b $  p + H_2(j=1) \rightarrow p + H_2(j'), (j' \geq 3)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -1.973243992807e+01  1.247414117614e-01  9.226482332314e-02
     1      1.829696809063e-01 -1.297428942606e-01 -4.048210910881e-02
     2     -3.965576412456e-02  3.618197482242e-02 -9.421328372950e-03
     3     -4.313466950038e-02 -2.291104293914e-03  6.559525504445e-03
     4      9.636266519704e-04 -2.918601086415e-03 -4.932567471708e-04
     5      2.253096845378e-03  1.405510037846e-03 -2.369615891213e-04
     6     -4.356551994020e-04 -2.600932648209e-04  5.724350136902e-05
     7      3.282766964094e-05  2.127068115091e-05 -4.867932845087e-06
     8     -9.076785125326e-07 -6.411159887874e-07  1.475347595640e-07

    E Index         3                   4                   5
  T Index
     0     -3.714490319222e-02 -1.356114029701e-02  4.100083713039e-03
     1      2.971894544949e-02  1.876669259108e-03 -3.322968917828e-03
     2     -1.981651027277e-03  1.569164989146e-03 -3.053099313902e-04
     3     -1.090766391534e-03 -4.420842120460e-04  3.568181091302e-04
     4      5.013178555056e-04 -3.266081392759e-05 -3.038322725843e-05
     5     -2.533635465343e-04  4.489607178747e-05 -1.262675526559e-06
     6      5.665115351398e-05 -1.000727087071e-05 -4.278214878688e-07
     7     -5.233684321566e-06  9.078582661039e-07  1.038286804798e-07
     8      1.702995300347e-07 -2.952394683317e-08 -4.770640084428e-09

    E Index         6                   7                   8
  T Index
     0     -3.666387513519e-04  1.083946601986e-05  1.351070637014e-08
     1      6.903747113211e-04 -5.754069299179e-05  1.739402046218e-06
     2      1.988204507361e-05  3.731257202030e-07 -6.182586349800e-08
     3     -8.469119247598e-05  8.182865454249e-06 -2.786434350401e-07
     4      8.613590729944e-06 -8.986091403746e-07  3.310895101467e-08
     5      6.220415471942e-07 -1.315998111932e-07  6.286616924397e-09
     6      2.197126754622e-08  1.839451977445e-08 -1.214916175628e-09
     7     -2.062547364677e-08  1.216554321342e-10  5.337970791360e-11
     8      1.119243083769e-09 -5.101049613696e-11 -1.189621855444e-13

     Error  2.05e-03 (C)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.2.2 $   p + H_2(v=0) \rightarrow p + H_2(v > 0)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -2.329087453007e+01  5.834682857859e-01  3.016206818784e-01
     1      2.119794074231e+00 -4.707130034299e-01 -1.627052975735e-01
     2      4.378420793629e-02  7.098659965089e-02 -1.538726713612e-03
     3     -1.212485645824e-01  1.716068200911e-02  1.234418739201e-02
     4     -6.784743989202e-05 -3.554071145865e-03 -1.963491271592e-03
     5      6.091207437528e-03 -5.334937961855e-04  2.680505429999e-06
     6     -1.035395322074e-03  1.771858360014e-04  2.137128521413e-05
     7      6.956622116761e-05 -1.519815181883e-05 -1.689036732606e-06
     8     -1.714843775518e-06  4.355820063409e-07  4.019682578322e-08

    E Index         3                   4                   5
  T Index
     0      2.566603966328e-02 -2.256516571421e-02 -5.628180168021e-04
     1      2.772025396684e-02  1.100571275815e-02 -3.271820121481e-03
     2     -8.406926164519e-03 -1.645206696492e-03  1.346715958215e-03
     3     -3.779824694550e-03  9.007565031801e-04 -2.318342461147e-04
     4      1.849557056204e-03 -4.387553829325e-04  4.379338463619e-05
     5     -3.000343967886e-04  8.809999443469e-05 -8.221671799210e-06
     6      2.287377536516e-05 -8.300877832833e-06  8.352812135871e-07
     7     -7.931460846045e-07  3.626282328864e-07 -3.748271128306e-08
     8      8.837549978855e-09 -5.713862092713e-09  5.406617870326e-10

    E Index         6                   7                   8
  T Index
     0      7.740619846564e-04 -8.045484752448e-05  2.526516293312e-06
     1      3.282645173821e-04 -1.405235013910e-05  2.050808638586e-07
     2     -2.333687223953e-04  1.660986465802e-05 -4.315116954882e-07
     3      3.388077149363e-05 -2.302170766555e-06  5.814386667558e-08
     4     -1.679616585635e-06 -5.915996895685e-09  1.292933101414e-09
     5      2.043346638977e-07  3.266439560921e-09  3.038024520814e-11
     6     -3.882583129136e-08  2.553655884029e-09 -1.293452258893e-10
     7      2.558173370326e-09 -2.723495529714e-10  1.327159233871e-11
     8     -4.963660570583e-11  7.622204418800e-12 -3.884869166334e-13

     Error  3.04e-03 (D)

    Error is improved to 8.94e-04 (B) if only values of <sv> for T > 1 eV are
    considered.
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.2.3 $   p + H_2 \rightarrow H(1s) + H_2^+$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -2.393090018673e+01  6.248759475696e-01  4.860672617319e-02
     1      1.497880823202e+00 -1.321184618254e+00  1.610180305377e-01
     2     -1.108848312589e+00  1.026939763848e+00 -2.764437632008e-01
     3      2.723796545755e-01 -3.349189897157e-01  1.525831234833e-01
     4      2.721877464232e-02  4.328258310611e-02 -4.172607648071e-02
     5     -1.779177173774e-02  4.465034873018e-04  6.494173133750e-03
     6      2.547195398346e-03 -6.602886969983e-04 -5.936946344163e-04
     7     -1.581068390892e-04  6.000753124589e-05  2.989789198510e-05
     8      3.720016363224e-06 -1.724843689004e-06 -6.403267693113e-07

    E Index         3                   4                   5
  T Index
     0     -1.200688114292e-01  8.087736504737e-03  9.460417081363e-03
     1      1.165310493854e-01 -3.963918450387e-02  4.451468403951e-03
     2     -3.948109106588e-02  3.853676685634e-02 -9.097709483121e-03
     3     -9.592981926094e-03 -1.131614493158e-02  3.519316476081e-03
     4      1.001163900824e-02  3.016020168360e-04 -4.649867654705e-04
     5     -2.726517864643e-03  3.947434451322e-04 -3.560364682888e-06
     6      3.516907384191e-04 -7.253981468239e-05  6.007588925145e-06
     7     -2.210901325776e-05  5.074761954649e-06 -4.890225279817e-07
     8      5.443461456508e-07 -1.285040546716e-07  1.225908917355e-08

    E Index         6                   7                   8
  T Index
     0     -2.128651089328e-03  1.685181886244e-04 -4.665309226730e-06
     1     -1.304738719348e-04 -8.714697396102e-06  4.796574269551e-07
     2      1.042066219239e-03 -5.955686719189e-05  1.358749516236e-06
     3     -4.463914380371e-04  2.672110767494e-05 -6.218012239798e-07
     4      7.356430658399e-05 -4.797055206851e-06  1.159195338618e-07
     5     -4.585211534749e-06  4.292978331848e-07 -1.209703556619e-08
     6     -1.866842996766e-08 -2.383240469589e-08  9.353713300206e-10
     7      1.067090708836e-08  1.188959741308e-09 -5.741789281748e-11
     8     -1.967393094286e-10 -3.854014407618e-11  1.748544462760e-12

     Error  7.17e-03 (D)

    Error is improved to 2.24e-03 (C) if only values of <sv> for T > 1 eV are
    considered.
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.2.4a $  p + D_2 \rightarrow D^+ + HD, (\mbox{or} H + D)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -2.111896543160e+01 -1.025538356060e-01 -1.465668919808e-01
     1     -6.219092009914e-01  6.936787446352e-02  9.499279319950e-02
     2     -1.215025308696e-01  8.780031887817e-03 -4.821837782776e-03
     3      6.815442586718e-02 -1.525104088494e-02 -7.956267907252e-03
     4      2.752449038333e-03  1.225019378208e-03  1.085462645581e-03
     5     -5.750611656794e-03  1.232968333824e-03  3.447823950790e-04
     6      1.125377790650e-03 -3.422288971501e-04 -1.018650054891e-04
     7     -8.919363340228e-05  3.365851906238e-05  9.449139307317e-06
     8      2.601744783012e-06 -1.162845386047e-06 -3.033572820292e-07

    E Index         3                   4                   5
  T Index
     0     -1.856546171568e-02  1.365853496631e-02 -3.826961311141e-04
     1     -1.160097875790e-03 -9.106571030308e-03  1.473315037711e-03
     2      4.849238242696e-03  7.525239416510e-04 -7.495029297215e-04
     3      1.124986687656e-03  5.331715821535e-04 -1.190706225054e-04
     4     -6.853757310073e-04 -1.075209684417e-04  9.573379729918e-05
     5     -5.896278139458e-05  3.476245629170e-06 -5.875969746146e-06
     6      4.848804836962e-05 -7.966497740323e-08 -2.512498875224e-06
     7     -6.135496085718e-06  9.456855386541e-08  3.985794665381e-07
     8      2.408475811630e-07 -6.748305167707e-09 -1.666573853398e-08

    E Index         6                   7                   8
  T Index
     0     -3.727957061966e-04  4.748991519766e-05 -1.698399806385e-06
     1     -1.495473343687e-05 -9.835840608225e-06  4.860991365689e-07
     2      1.403289748223e-04 -1.067949058111e-05  2.955867761367e-07
     3      5.146965646887e-06  3.731108583161e-07 -2.546014093405e-08
     4     -1.739495667153e-05  1.302457212236e-06 -3.566296705821e-08
     5      1.552565062442e-06 -1.430402446135e-07  4.485383482007e-09
     6      4.667259306147e-07 -3.425538256234e-08  9.189075599465e-10
     7     -8.312637284424e-08  6.615368641527e-09 -1.889019472636e-10
     8      3.654557715832e-09 -2.995367307547e-10  8.734664246336e-12

     Error  7.28e-03 (D)

    Error is improved to 6.67e-04 (B) if only values of <sv> for T > 1 eV are
    considered.
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.2.4b $  p + D_2 \rightarrow D + HD^+$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -2.529005922309e+01  3.371688551898e-01  4.693918630510e-02
     1      1.881570344354e+00 -5.113434583372e-01 -5.273216405018e-02
     2     -8.814004836556e-01  2.968842541690e-01  3.441039128935e-02
     3      1.691850902103e-01 -8.619057072559e-02 -5.980460778885e-02
     4     -6.652054410222e-02  1.093768968050e-02  5.059893495850e-02
     5      2.240305503202e-02  2.436569548502e-04 -1.818236207409e-02
     6     -3.819487238341e-03 -2.196174841406e-04  3.110816934408e-03
     7      3.069356789436e-04  2.140188150215e-05 -2.512796010299e-04
     8     -9.328627869191e-06 -6.680477536797e-07  7.694384931049e-06

    E Index         3                   4                   5
  T Index
     0      1.384303400933e-02  2.197297492088e-02 -5.238094233772e-03
     1     -5.260928525467e-02 -1.183131187811e-02  1.230475793211e-02
     2      1.331208476230e-02 -6.086729631519e-03 -3.440498761785e-03
     3      2.992464843607e-02  6.494689656712e-03 -5.095348269685e-03
     4     -2.273638325874e-02 -4.060667412372e-03  4.212401093393e-03
     5      6.836786141131e-03  1.468739824255e-03 -1.329242365115e-03
     6     -1.028059797546e-03 -2.651119233481e-04  2.067742478703e-04
     7      7.612976218275e-05  2.242650259038e-05 -1.567120609980e-05
     8     -2.199089655518e-06 -7.103958561240e-07  4.597541185577e-07

    E Index         6                   7                   8
  T Index
     0     -2.589041456721e-03  5.971878512503e-04 -2.960695486568e-05
     1      2.243312170048e-04 -5.598084624364e-04  4.754533831647e-05
     2      8.268141028700e-04  3.941921240841e-05 -1.101845343079e-05
     3      9.066019513957e-04 -6.629895278703e-05  2.061740481891e-06
     4     -9.043842324620e-04  7.471396669600e-05 -1.946743502969e-06
     5      2.869803101647e-04 -2.489904593762e-05  7.165571176206e-07
     6     -4.325324514439e-05  3.772514035078e-06 -1.135486249420e-07
     7      3.158371725991e-06 -2.722540885633e-07  8.321982058577e-09
     8     -8.960027960892e-08  7.591855363103e-09 -2.323959696375e-10

     Error  1.18e-04 (A)

    <sv> < 1.0e-11 for E > 100 eV for the entire T range considered here.  The
    fit gives unphysical values for E > 100 eV in this range and should not be
    used there.
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.2.5 $   p + H_2 \rightarrow p + H_2^+(v) + e, (v \leq 9)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -5.367225610927e+01  8.561616047237e+00  1.816558609991e+00
     1      1.788157706832e+01 -6.286008716933e+00 -1.245074165012e+00
     2     -4.732013902744e+00  1.828154334899e+00  2.297272982398e-01
     3      5.202644682964e-01 -2.797342414213e-01  3.359419100500e-02
     4      3.521809500536e-02  3.001478994199e-02 -2.022030104793e-02
     5     -1.648514003195e-02 -3.511706068001e-03  3.466696529491e-03
     6      1.922206340707e-03  3.867557051749e-04 -2.971236668059e-04
     7     -1.035405866079e-04 -2.470578459133e-05  1.298468816782e-05
     8      2.203112678635e-06  6.255426859518e-07 -2.312060025019e-07

    E Index         3                   4                   5
  T Index
     0     -1.522333614377e+00  3.759529679375e-01 -4.786079082066e-02
     1      1.069094789286e+00 -2.542196973682e-01  3.177817178124e-02
     2     -2.574312651499e-01  6.235010781304e-02 -7.498165815343e-03
     3      1.396148560079e-02 -5.455674772716e-03  7.627828208046e-04
     4      4.167002536339e-03 -2.961138095159e-04 -1.989496685088e-05
     5     -7.713464611496e-04  9.296859682627e-05 -4.390690629457e-06
     6      4.630325714231e-05 -6.209296988115e-06  7.802446823898e-07
     7     -5.951650262538e-07  1.040160519423e-07 -6.013540281517e-08
     8     -2.277567397969e-08  2.205724295105e-09  1.764776882153e-09

    E Index         6                   7                   8
  T Index
     0      3.386576601010e-03 -1.260406274176e-04  1.909653870707e-06
     1     -2.284002706788e-03  9.015781280225e-05 -1.528190392357e-06
     2      4.874507232153e-04 -1.603249117471e-05  2.009004806425e-07
     3     -4.735379021213e-05  9.681751756528e-07  9.137775800355e-09
     4      5.017190961057e-06 -3.312351285579e-07  7.657715805259e-09
     5     -5.449234862617e-07  8.306829849916e-08 -3.008901804950e-09
     6     -9.036886465169e-09 -6.038768586675e-09  3.127724512237e-10
     7      5.701208151560e-09 -2.749357161379e-12 -1.065774817217e-11
     8     -2.564871978479e-10  9.360384058829e-12  2.125011883790e-14

     Error  7.60e-05 (A)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.2.6 $   p + H_2^+(v) \rightarrow p + H(1s) + H^+$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -3.503949588630e+01  3.596223868947e-03  5.850451146780e-01
     1      3.056567004229e+00  3.101537521281e-01 -3.802213472822e-01
     2      6.995656851497e-01 -1.714310765924e-01  4.075164360191e-02
     3     -2.282773440449e-01  2.456336476294e-02  2.462515616912e-02
     4      2.032409655024e-02  4.693764706073e-03 -8.013907630788e-03
     5      7.333965699110e-04 -2.072064243724e-03  9.248040165878e-04
     6     -3.031298255102e-04  2.853271682462e-04 -4.190818382811e-05
     7      2.353662179363e-05 -1.783778591788e-05  1.188782788257e-07
     8     -6.209682283669e-07  4.280148575920e-07  2.898023610900e-08

    E Index         3                   4                   5
  T Index
     0      9.474524219612e-02 -3.938575923140e-02  4.666084706751e-03
     1     -4.164890965970e-02  3.732884150575e-02 -5.553031214904e-03
     2      6.345887908944e-04 -7.388540130210e-03  2.215252505302e-03
     3     -1.163184524936e-03 -8.552780029379e-04 -6.842088086239e-05
     4      9.714618199968e-04  3.399582328819e-04 -7.945188972850e-05
     5     -1.686569365114e-04 -1.260646704530e-05  9.272036136361e-06
     6      9.494328352046e-06 -3.548328747232e-06  3.006199198249e-07
     7      3.338996422125e-08  3.705771699362e-07 -8.431446572047e-08
     8     -1.257918518905e-08 -1.036436256550e-08  3.078907880655e-09

    E Index         6                   7                   8
  T Index
     0     -3.236705187942e-04  1.538536999072e-05 -3.695652391342e-07
     1      2.646628484405e-04  3.287941538949e-06 -4.204509688663e-07
     2     -2.704279067013e-04  1.508871496609e-05 -3.179547222229e-07
     3      4.711638356898e-05 -4.822026376406e-06  1.518903664812e-07
     4      4.045609876795e-06  1.545451740861e-07 -1.283734364199e-08
     5     -1.248629759318e-06  6.544957875539e-08 -1.110642504800e-09
     6      3.221166999732e-08 -5.258665703836e-09  1.800452602126e-10
     7      5.927769241279e-09 -5.999414332265e-11 -4.977523706425e-12
     8     -2.953243500461e-10  1.037093087158e-11 -6.464182493927e-14

     Error  4.86e-04 (B)
\end{verbatim}\end{small}







\newpage
\subsection{
Reaction 3.3.1 $   p + He \rightarrow H + He^+$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -3.353816664129e+01 -4.586784908436e-01  1.594898247008e-01
     1      1.781370892516e+00  6.891694453609e-01 -1.611575823430e-01
     2      6.707672251154e-01 -3.169866636164e-01  7.765165360131e-02
     3     -7.477930071091e-02  3.350898800561e-02 -3.392131794663e-02
     4     -8.381713330773e-02  1.622059625803e-02  1.247636271907e-02
     5      2.694989933554e-02 -5.889292565221e-03 -2.789567626468e-03
     6     -3.290961646690e-03  8.008575628447e-04  3.401335910688e-04
     7      1.824292103062e-04 -5.051648761026e-05 -2.091692923886e-05
     8     -3.841146748130e-06  1.228049521583e-06  5.084397192524e-07

    E Index         3                   4                   5
  T Index
     0      1.993834571954e-01 -2.908726266195e-02 -4.587782047584e-03
     1     -1.491282657121e-01  4.812768747296e-02 -3.997981241748e-03
     2      2.652950675220e-02 -2.159277544971e-02  5.139425409123e-03
     3      8.474034802338e-03  2.748759961113e-03 -1.420567682255e-03
     4     -5.507438871028e-03  5.154609993383e-04  1.065291472218e-04
     5      1.293406768681e-03 -2.021983674764e-04  1.031174122595e-05
     6     -1.563868173318e-04  2.528045360094e-05 -1.979594316338e-06
     7      9.545486229202e-06 -1.444453762830e-06  9.506598262937e-08
     8     -2.317334470853e-07  3.187947009859e-08 -1.162138178659e-09

    E Index         6                   7                   8
  T Index
     0      1.233562953962e-03 -8.959520538477e-05  2.153885795280e-06
     1     -1.453386884233e-04  3.438904204074e-05 -1.235017420599e-06
     2     -5.776151273370e-04  3.150136684703e-05 -6.720649580897e-07
     3      2.214493222620e-04 -1.503183655470e-05  3.810469912151e-07
     4     -2.770978822291e-05  2.235082592688e-06 -6.269566270205e-08
     5      8.328481121158e-07 -1.256070804240e-07  4.314925565866e-09
     6      5.230582879539e-08  2.635177963503e-09 -1.574479246009e-10
     7     -8.519235005422e-10 -2.264396092848e-10  9.108750391681e-12
     8     -1.347103798052e-10  1.468879806508e-11 -4.188673847162e-13

     Error  1.58e-03 (C)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.3.2 $   p + He \rightarrow p + He^+ + e$}

\begin{small}\begin{verbatim}
    E Index             0                   1                   2
  T Index
       0         -3.513975817234e+01  -5.242917555404e-01  -3.826194904402e-01
       1         -5.385780070980e-01   7.943799641890e-02   1.983252146365e-01
       2          9.035205217957e-01   1.231698104678e-01  -4.512064453109e-02
       3          6.154592887522e-02  -4.082389668808e-02   8.492939132060e-03
       4         -8.683888520960e-02   1.363524072485e-03  -6.877816557895e-04
       5          1.850283102315e-02   1.065556461944e-03  -1.981157465961e-04
       6         -1.829730723913e-03  -1.792886431140e-04   5.180204798722e-05
       7          8.903233974874e-05   1.133222476812e-05  -4.281190983076e-06
       8         -1.723417501407e-06  -2.598637070808e-07   1.212392744890e-07

    E Index             3                   4                   5
  T Index
       0          1.749071804038e-01   3.379968769905e-02  -1.684873318946e-02
       1         -2.966737668036e-02  -2.195230807923e-02   7.987671929803e-03
       2         -2.632395045040e-02   9.106381567773e-03  -1.220083366385e-03
       3          4.950008931722e-03  -2.125790233999e-03   2.856685316297e-04
       4          1.539732094359e-03   1.989843795364e-05  -8.201311837293e-05
       5         -5.591852085968e-04   8.588977130038e-05   6.771413834410e-06
       6          6.660694317589e-05  -1.557623357777e-05   6.328328243704e-07
       7         -3.537756092409e-06   1.101685345092e-06  -1.130645655532e-07
       8          7.093957802151e-08  -2.828418079985e-08   4.145168773820e-09

    E Index             6                   7                   8
  T Index
       0          2.235958862320e-03  -1.282599958804e-04   2.760095475019e-06
       1         -1.078408322383e-03   6.664182706070e-05  -1.576989885173e-06
       2          1.013506718990e-04  -5.755496123590e-06   1.585191024717e-07
       3         -1.436171240398e-05   5.512329277872e-08   1.055695620784e-08
       4          1.095726116510e-05  -4.861620705084e-07   5.080813644487e-09
       5         -1.907336915250e-06   1.057876163056e-07  -1.372842995387e-09
       6          7.169146469455e-08  -4.866671700650e-09   1.446148171715e-11
       7          5.780678333429e-09  -2.912824978296e-10   1.171657019875e-11
       8         -3.562927197437e-10   2.049378727457e-11  -5.867221352941e-13

       Error 1.18e-04
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.3.6a $  p + He(1s^12s^11S) \rightarrow H(2s) + He^+(1s)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
      0     -2.545206891667e+01  4.087721421944e-01  1.586491378549e-01
      1      2.913542861083e+00 -4.603441740870e-01 -1.538179897348e-01
      2     -2.751712354111e-01  1.679980585979e-01  4.131633234926e-02
      3     -2.633545354224e-02 -1.567302034710e-02 -4.520967162781e-04
      4      8.622940210562e-03 -3.336538128570e-03 -8.260874599039e-04
      5     -2.300706825690e-04  8.171653956449e-04 -4.965497872141e-05
      6     -1.125479569857e-04 -5.470534020950e-05  3.466402080937e-05
      7      1.223862287149e-05  4.510736761276e-07 -3.432193506153e-06
      8     -3.807538916669e-07  4.917383484449e-08  1.058745036988e-07

    E Index         3                   4                   5
  T Index
      0      5.058971318815e-02 -3.791312599700e-03 -3.833049897763e-03
      1      5.222489871516e-03  1.003438746972e-02 -1.168850382452e-03
      2     -1.641664176824e-02 -4.107214837202e-03  1.967371773324e-03
      3      3.430116367838e-03  2.838382928506e-04 -4.209650788467e-04
      4     -9.020143604576e-05  1.347016172889e-04 -4.958012853527e-06
      5      1.188821428901e-05 -3.313627492240e-05  8.279160796936e-06
      6     -1.041943673755e-05  3.202234108937e-06 -5.675677716610e-07
      7      1.271716123512e-06 -1.476246727512e-07 -1.066910658350e-08
      8     -4.477991722400e-08  2.709447373704e-09  1.358296626830e-09

    E Index         6                   7                   8
  T Index
      0      7.950734542136e-04 -5.885681325041e-05  1.541378919766e-06
      1     -5.579601385349e-05  1.353899796842e-05 -5.122850004231e-07
      2     -2.673125550197e-04  1.566853623054e-05 -3.415999363201e-07
      3      7.898192930901e-05 -5.854327119904e-06  1.562313674827e-07
      4     -4.094959727394e-06  5.353989855247e-07 -1.913396611346e-08
      5     -6.413236333283e-07  4.848646930188e-09  8.121470593220e-10
      6      3.608129963110e-08  5.274666256825e-10 -8.954629500955e-11
      7      4.563092914087e-09 -4.419337156204e-10  1.449959132985e-11
      8     -2.914831320408e-10  2.266195254549e-11 -6.387372749942e-13

     Error  2.14e-04 (A)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.3.6b $  p + He(1s^12s^13S) \rightarrow H(2s) + He^+(1s)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -3.122938685456e+01  4.028257956860e-01  2.334348862506e-01
     1      4.307517366770e+00 -1.334773437980e-01 -2.727882564258e-01
     2     -2.361736602090e-02 -1.432708434183e-01  1.201423191752e-01
     3     -2.081939800843e-01  9.945616177435e-02 -2.709414076376e-02
     4      4.838048334741e-02 -2.358233412220e-02  4.734052652172e-03
     5     -4.823009462310e-03  2.401135023266e-03 -8.658412840062e-04
     6      1.881322513534e-04 -6.847646462892e-05  1.174757836154e-04
     7      1.638221308510e-06 -4.485862371494e-06 -8.367996886287e-06
     8     -2.228643990360e-07  2.485885176817e-07  2.302713313337e-07

    E Index         3                   4                   5
  T Index
     0      9.957171612712e-02 -1.023449426184e-02 -4.496822279877e-03
     1     -6.164153370524e-02  3.370797060231e-02 -3.319571865630e-03
     2      1.135420376951e-02 -1.984294955107e-02  4.774462913892e-03
     3      6.080332812779e-04  3.775623225478e-03 -1.322011971814e-03
     4     -1.366781281246e-03  1.119535101746e-04  8.050305381600e-05
     5      4.843193058320e-04 -1.376705233410e-04  1.437228606346e-05
     6     -7.634853296888e-05  1.971646855797e-05 -2.212285070187e-06
     7      5.557461570216e-06 -1.186541505079e-06  9.199979549866e-08
     8     -1.522032174656e-07  2.678514729721e-08 -6.757808737035e-10

    E Index         6                   7                   8
  T Index
     0      9.241247688814e-04 -6.358490712348e-05  1.525433983093e-06
     1     -8.936775061168e-05  2.722213770738e-05 -1.020668178963e-06
     2     -5.033398600438e-04  2.498282187124e-05 -4.741136942425e-07
     3      1.886421813109e-04 -1.237062202523e-05  3.083020170351e-07
     4     -2.071452083937e-05  1.798870106702e-06 -5.365052965492e-08
     5      8.302103147893e-08 -9.892824420452e-08  4.289062541986e-09
     6      7.058025912797e-08  4.738735970150e-09 -2.878639826635e-10
     7      1.761485514114e-09 -6.097061454789e-10  2.321326366521e-11
     8     -2.771866976517e-10  2.928170189987e-11 -8.892938915985e-13

     Error  3.14e-04 (B)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.3.7a $  p + He(1s^12p^11P) \rightarrow H(2p) + He^+(1s)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -2.096277724233e+01  2.908363629618e-01  1.344210657325e-01
     1      1.838253461492e+00 -3.440722063330e-01 -1.075733974740e-01
     2     -1.504683700198e-01  1.391168674341e-01  1.407833937250e-02
     3     -1.988914332352e-02 -1.827777489629e-02  6.303582937881e-03
     4      5.224868789594e-03 -1.503338958950e-03 -1.588632341093e-03
     5      7.903708169506e-05  6.281421973346e-04 -5.706206467996e-06
     6     -1.088955465421e-04 -5.979073448137e-05  3.124053598819e-05
     7      1.035977420345e-05  2.110596750983e-06 -3.069558569915e-06
     8     -3.067244916001e-07 -1.576601346659e-08  9.145348279705e-08

    E Index         3                   4                   5
  T Index
     0      2.643049515080e-02 -5.367852119278e-03 -1.337347909674e-03
     1      1.130230128759e-02  6.583514261893e-03 -1.227749129234e-03
     2     -1.376123125770e-02 -8.644040120194e-04  1.013028508387e-03
     3      2.150624640205e-03 -4.951984366580e-04 -1.010346550533e-04
     4      2.568647734327e-04  1.217005674709e-04 -2.937286287021e-05
     5     -7.591611145466e-05 -1.357219951533e-06  4.933729396290e-06
     6      3.384790316520e-06 -1.821787693981e-06  5.718370339432e-08
     7      2.181939775695e-07  1.762529764553e-07 -4.223388769976e-08
     8     -1.459318779306e-08 -5.010568584481e-09  1.790351359196e-09

    E Index         6                   7                   8
  T Index
     0      3.643627994364e-04 -2.927921977642e-05  8.016074291976e-07
     1      4.333172602701e-05  3.531045210401e-06 -2.066151687336e-07
     2     -1.589309518095e-04  1.005180995389e-05 -2.313721814532e-07
     3      3.299776657730e-05 -2.892265994707e-06  8.406596588342e-08
     4      1.370261783588e-06  9.004843536308e-08 -6.389625540292e-09
     5     -7.078827921616e-07  3.342727890413e-08 -3.633168197949e-10
     6      1.974622062662e-08 -1.472504522071e-09  1.736212449338e-11
     7      4.174185414825e-09 -2.207503317650e-10  5.469661760878e-12
     8     -2.233522764425e-10  1.319988966081e-11 -3.154892040215e-13

     Error  1.32e-04 (A)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 3.3.7b $  p + He(1s^12p^13P) \rightarrow H(2p) + He^+(1s)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -1.990230529818e+01  2.522093890961e-01  1.239244757420e-01
     1      1.500741968514e+00 -2.951590494714e-01 -9.430103505170e-02
     2     -1.124864006941e-01  1.201976126897e-01  7.788712358907e-03
     3     -1.795417514240e-02 -1.603483373300e-02  7.712444722040e-03
     4      5.194941686189e-03 -1.383721748856e-03 -1.777603361970e-03
     5     -2.042833130770e-04  6.021103147616e-04  2.064037010474e-05
     6     -5.295363277471e-05 -6.246797487185e-05  2.744322340445e-05
     7      6.198420111343e-06  2.646123676389e-06 -2.758240361873e-06
     8     -1.960046743830e-07 -3.649994467826e-08  8.182448832297e-08

    E Index         3                   4                   5
  T Index
     0      1.742021976180e-02 -5.521806381035e-03 -4.054669219838e-04
     1      1.218926273762e-02  5.820172532684e-03 -1.295775597112e-03
     2     -1.191866922435e-02 -1.362329499044e-04  7.107218103516e-04
     3      1.549234171092e-03 -6.809505756955e-04  9.404549508879e-07
     4      3.665320868067e-04  1.165229196925e-04 -3.679801125361e-05
     5     -1.010994386303e-04  7.956025749673e-06  3.831718379904e-06
     6      7.717708517072e-06 -3.365265395665e-06  2.479212041233e-07
     7     -1.385756782677e-07  2.808607980980e-07 -5.087249153750e-08
     8     -3.853798064799e-09 -7.625575723278e-09  1.871480566627e-09

    E Index         6                   7                   8
  T Index
     0      1.843910580845e-04 -1.594987619980e-05  4.473710134751e-07
     1      7.954619252281e-05  7.572338624031e-08 -1.024950580103e-07
     2     -1.181843011735e-04  7.615476962452e-06 -1.763379176652e-07
     3      1.702222446329e-05 -1.814838357759e-06  5.703526185010e-08
     4      3.068724996897e-06 -5.005474959780e-08 -2.339128601417e-09
     5     -7.153412104701e-07  4.200855361511e-08 -7.453854004436e-10
     6      1.745775447721e-08 -2.506978553877e-09  6.748855851556e-11
     7      3.524103509748e-09 -9.220739545880e-11  5.381508915908e-13
     8     -1.806607060530e-10  7.993276670629e-12 -1.381625354747e-13

     Error  1.18e-04 (A)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 4.2.1 $H_2^+(v) + H(1s) \rightarrow H_2^+(2p\sigma_u) + H(1s) \rightarrow H^+ + H + H(1s), (v=0\ldots 9)$}






% +                    +*
%H (1ss ;v) + H(1s) T H  (2ps ) + H(1s)
% 2    g               2     u
%
%                      +
%                   T H  + H + H(1s), (v=0-9)





\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -3.332967494942e+02  1.433058540744e+02 -2.947284166509e+01
     1      2.408101998902e+02 -1.362501559544e+02  2.801041076177e+01
     2     -8.996254988743e+01  5.285412858800e+01 -1.040643658208e+01
     3      2.113931204200e+01 -1.101441118819e+01  1.881216179150e+00
     4     -3.311192105349e+00  1.359065776894e+00 -1.560567106434e-01
     5      3.429437857518e-01 -1.029838658966e-01  1.219202707337e-03
     6     -2.241037042190e-02  4.809469933342e-03  7.390343876677e-04
     7      8.329672118744e-04 -1.335338145990e-04 -4.892703647590e-05
     8     -1.338140072499e-05  1.818158167900e-06  9.766334115013e-07

    E Index         3                   4                   5
  T Index
     0      4.969309555880e+00 -8.148122128593e-01  9.323059658335e-02
     1     -2.474427836778e+00  1.543035928035e-01 -3.251763597742e-02
     2      5.085589872685e-01  6.361992438909e-02 -2.591606323191e-03
     3     -5.077119677970e-02 -1.852297452693e-02  1.600942164119e-03
     4     -2.033265136901e-03  9.718962378108e-04  8.040301331558e-06
     5      1.601047711063e-03  6.336414922385e-05 -3.788387994691e-05
     6     -2.320531548991e-04  2.588021875832e-06  3.001128191660e-06
     7      1.473207837914e-05 -1.282873408948e-06  9.991541256156e-09
     8     -3.535181371877e-07  5.620757041266e-08 -5.034820677719e-09

    E Index         6                   7                   8
  T Index
     0     -5.854170815799e-03  1.656707831222e-04 -1.178234924866e-06
     1      5.085816021807e-03 -3.411499000615e-04  8.295196911491e-06
     2     -1.089685945002e-03  1.132751576739e-04 -3.266248682724e-06
     3      3.805592017920e-05 -8.847884634595e-06  2.721236736970e-07
     4      7.171822512541e-07 -7.530004219739e-07  3.651109616529e-08
     5      1.786513937009e-06  9.799503679830e-08 -6.480643645772e-09
     6     -2.271952317871e-07  1.029652468585e-09  2.338178917351e-10
     7      4.685569702988e-09 -2.668266102694e-10  4.756847923643e-12
     8      2.048241675655e-10  1.327375467275e-12 -2.566621089266e-13

     Error  1.64e-02 (D)
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 4.3.1 $   H_2^+ + H_2 \rightarrow H_2 + H_2^+$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -2.013143517466e+01  1.875197914224e-01  6.865479604288e-02
     1      2.643458086299e-01 -1.177247941077e-01 -6.758032286178e-03
     2      7.295645990688e-02  6.053418575149e-03 -1.068656224307e-02
     3     -1.022454343675e-02  7.350954380641e-03  6.814213275702e-04
     4     -4.801198168030e-03 -1.111612877392e-03  8.373319888351e-04
     5      1.141613586234e-03 -1.371389288760e-04 -1.733761953296e-04
     6     -3.388853048483e-05  4.426148343648e-05  9.992317920676e-06
     7     -6.418225985394e-06 -3.652063962019e-06  1.351312819077e-07
     8      3.555592819527e-07  1.012701361110e-07 -1.993091213299e-08

    E Index         3                   4                   5
  T Index
     0      6.246595384100e-03 -5.017891372102e-03 -3.907644829287e-04
     1      8.585003721992e-03 -3.261863407467e-04 -3.322528542186e-04
     2     -9.371235639464e-04  9.735708783528e-04 -9.933049259228e-05
     3     -8.156435157073e-04  2.903991825737e-05  3.223596225946e-05
     4      1.392977576749e-04 -9.316910697276e-05  8.814981236658e-06
     5      1.602610140599e-05  1.464235749797e-05 -2.944711701791e-06
     6     -5.333970870280e-06 -2.999105886511e-07  2.275612517364e-07
     7      4.285396408056e-07 -7.184302986068e-08 -3.265552364687e-10
     8     -1.131561847140e-08  3.678869095972e-09 -3.639982258214e-10

    E Index         6                   7                   8
  T Index
     0      2.786239030986e-04 -2.942576591004e-05  9.352275354690e-07
     1      6.015471216449e-05 -4.039435357369e-06  9.730479674748e-08
     2     -6.786246802840e-06  1.438327767305e-06 -5.530742535057e-08
     3     -5.199055182831e-06  2.852443990256e-07 -4.825480212106e-09
     4      6.675626166047e-07 -1.325441927019e-07  5.012529587757e-09
     5      6.365231650682e-08  1.872976659964e-08 -1.014883015867e-09
     6     -1.173422836715e-08 -1.364602870139e-09  9.566404348683e-11
     7      1.585228996542e-10  6.431866226702e-11 -4.507074278992e-12
     8      2.056662091085e-11 -1.804254277469e-12  9.042973335167e-14

     Error  2.58e-04 (A)
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 4.3.2 $   H_2^+ + H_2 \rightarrow H_2^+ + H_2^+ + e$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
       0     -3.361709356815e+01  2.069962590009e+00 -9.010533538327e-01
       1      2.233317520475e+00 -2.726590828625e+00  1.643915864856e+00
       2     -7.287181470383e-01  1.661423051779e+00 -1.025272729232e+00
       3      4.891752418641e-01 -5.973230637071e-01  3.079590537141e-01
       4     -1.587248070170e-01  1.357406226261e-01 -4.995160576771e-02
       5      2.786295111792e-02 -1.954886177187e-02  4.482229513351e-03
       6     -2.710661372128e-03  1.714035434070e-03 -2.108888570649e-04
       7      1.370951998574e-04 -8.287462331299e-05  4.245802696647e-06
       8     -2.813882491422e-06  1.685813575983e-06 -1.243788238044e-08

    E Index         3                   4                   5
  T Index
       0     4.757423977733e-01 -1.173499542871e-01  1.574858380323e-02
       1    -5.767723646300e-01  1.225177255213e-01 -1.583053141876e-02
       2     3.012750644438e-01 -5.027357052159e-02  5.155737495648e-03
       3    -7.997349646419e-02  1.082475428239e-02 -7.031584157104e-04
       4     1.041402498039e-02 -1.202077056853e-03  4.396765142500e-05
       5    -4.121930331601e-04  2.634686881556e-05 -1.954016523336e-06
       6    -4.475697526351e-05  9.018648895762e-06  4.809988527180e-08
       7     5.227237760667e-06 -9.414336727644e-07  1.246197373405e-08
       8    -1.530261560799e-07  2.877226549741e-08 -8.668284019609e-10

    E Index         6                   7                   8
  T Index
       0    -1.166206787765e-03  4.383027530849e-05 -6.348470910454e-07
       1     1.209069864044e-03 -4.994507398820e-05  8.566470175705e-07
       2    -3.336823259195e-04  1.297196226977e-05 -2.351485202412e-07
       3     1.145932327551e-05  8.141233815222e-07 -2.868358002582e-08
       4     5.587705467605e-06 -6.600350475588e-07  2.019835260065e-08
       5    -3.033359082874e-07  6.422702166049e-08 -2.757788924867e-09
       6    -6.552590854175e-08  1.043541445947e-09  1.156250997817e-10
       7     6.735598908536e-09 -3.714404901163e-10  1.840510894514e-12
       8    -1.644678010990e-10  1.198441513399e-11 -1.614965817473e-13

    Error 1.62e-04
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 4.3.3 $   H_2^+ + H_2 \rightarrow H_3^+ + H$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
      0     -2.094582001426e+01 -2.903671854391e-01 -1.484602213957e-01
      1     -3.908059227757e-01  5.612290953081e-02  7.311639731340e-02
      2     -1.406586222305e-01  3.034165415227e-02 -1.768280719269e-02
      3     -2.329090939587e-02 -3.655835575292e-03 -8.362574927676e-04
      4      4.478632359998e-03 -2.378407903866e-03  1.315628515286e-03
      5      1.028607802560e-03  4.205001381642e-04 -1.125270518181e-04
      6     -3.155447765047e-04  1.597095151191e-05 -2.355907533211e-05
      7      2.828211032630e-05 -6.662911839399e-06  3.842898711627e-06
      8     -8.646163087099e-07  3.261593568923e-07 -1.473565567371e-07

    E Index         3                   4                   5
  T Index
      0     -7.788282133984e-02 -2.716693083523e-02  2.888660862916e-03
      1      5.829061271518e-02  7.552808963242e-03 -9.437914641041e-03
      2     -5.709689089835e-03  7.796493173156e-03  2.150949138545e-03
      3     -4.779241336163e-03 -1.812406227884e-03  7.881163019295e-04
      4      8.267929702836e-04 -4.230180219524e-04 -2.567042908792e-04
      5      1.289639680255e-04  1.253485982824e-04  8.799819972454e-06
      6     -3.554580445806e-05 -6.132110996274e-06  2.803562696685e-06
      7      2.286178560056e-06 -4.109569999864e-07 -2.529649414563e-07
      8     -3.749876424917e-08  2.926978739503e-08  5.144928119898e-09

    E Index         6                   7                   8
  T Index
      0      1.962991371294e-03 -2.537688817604e-04  3.167927580722e-06
      1     -9.682436127328e-04  6.252187020332e-04 -4.847265436175e-05
      2     -5.832002101739e-04 -9.096057686629e-05  1.497380403845e-05
      3      1.857587010565e-04 -5.555787804993e-05  2.979712834131e-06
      4      2.408905813848e-05  1.512607065092e-05 -1.688827943562e-06
      5     -1.011644205055e-05 -1.202093866229e-06  2.611308007476e-07
      6      8.619910002153e-07  1.741997695030e-08 -1.925603640419e-08
      7     -2.042542214746e-08  1.432103401478e-09  7.102441362723e-10
      8     -9.824207587793e-11 -3.870509135647e-11 -1.074647099491e-11

     Error  1.90e-04 (A)

    <sv> < 1.0e-11 for E > 50 eV for the entire T range considered here.  The
    fit gives unphysical values for E > 50 eV in this range and should not be
    used there.
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 4.4.1 $    H_2^+ + He \rightarrow H_2^+ + He^+ + e$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -4.309726141841e+01  6.475006995833e+00 -1.883249802835e-01
     1      1.281172385125e+01 -7.243378485529e+00  5.043373334075e-01
     2     -5.890999853236e+00  3.579212080875e+00 -4.030617651034e-01
     3      1.885032038426e+00 -1.033881853032e+00  1.536625297945e-01
     4     -3.859849765629e-01  1.929288495908e-01 -3.246664649774e-02
     5      5.040064801144e-02 -2.379010323165e-02  4.018297415320e-03
     6     -4.013079090991e-03  1.869730413126e-03 -2.907360932536e-04
     7      1.755528395798e-04 -8.421826651094e-05  1.143340331457e-05
     8     -3.214596451062e-06  1.641069021089e-06 -1.897006152308e-07

    E Index         3                   4                   5
  T Index
     0     -6.707987015268e-01  2.639446649402e-01 -4.723560827520e-02
     1      5.831511375074e-01 -2.063394187655e-01  3.239770290912e-02
     2     -1.771129376316e-01  6.192783929198e-02 -8.167418547801e-03
     3      1.742222425989e-02 -8.070784446837e-03  9.406258713749e-04
     4      1.606419041683e-03  1.581892175211e-04 -3.508868395189e-05
     5     -4.700427633330e-04  7.455005712397e-05 -5.328157796217e-06
     6      3.265369551305e-05 -8.049211111537e-06  1.040817302013e-06
     7     -4.917056270388e-07  2.951503045367e-07 -7.703466212797e-08
     8     -1.671870630370e-08 -2.615761487320e-09  2.128865104658e-09

    E Index         6                   7                   8
  T Index
     0      4.533392612738e-03 -2.256809803213e-04  4.569435145102e-06
     1     -2.763842540794e-03  1.247895466478e-04 -2.344043545995e-06
     2      5.254335475410e-04 -1.537799120839e-05  1.331837837243e-07
     3     -3.856233447220e-05 -4.156140436365e-07  5.034959925043e-08
     4      3.791183556963e-06 -2.366231626960e-07  5.992973459021e-09
     5     -5.795596041141e-07  9.708186393302e-08 -3.488558225848e-09
     6      4.399518745143e-10 -7.685681194865e-09  3.468947174405e-10
     7      5.520600090967e-09  1.762439907887e-11 -9.396171756462e-12
     8     -2.654154152549e-10  1.103963564691e-11 -8.957193708196e-14

     Error  8.31e-05 (A)
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 5.2.1 $   He^+ + H_2 \rightarrow He^+ + H^+ + e$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -3.713019551543e+01  4.513880809792e+00  4.465734536727e-01
     1      7.312992983242e+00 -4.230698925401e+00  3.363491931239e-01
     2     -1.404602569517e+00  1.574352939860e+00 -4.712948306828e-01
     3      8.465714459741e-02 -2.805696953923e-01  1.811965461049e-01
     4      3.001601051201e-02  1.978938422099e-02 -3.599941390452e-02
     5     -9.026893259159e-03  9.283132403167e-04  4.476205535455e-03
     6      1.077346431372e-03 -2.592422590385e-04 -3.727829206896e-04
     7     -6.008751203326e-05  1.667265275798e-05  1.918105806793e-05
     8      1.276481720290e-06 -3.728072837540e-07 -4.453576012678e-07

    E Index         3                   4                   5
  T Index
     0     -2.439394070482e-01  4.439220456707e-03  7.345794340485e-03
     1      2.216628364304e-01 -5.119093601500e-02  1.943198225007e-03
     2     -8.374208591879e-03  2.953035366897e-02 -6.222917082325e-03
     3     -3.500869288503e-02 -2.890323734594e-03  2.024599123408e-03
     4      1.278467857143e-02 -1.232540236931e-03 -1.666275826514e-04
     5     -2.115580254273e-03  3.444824743426e-04 -1.323145031233e-05
     6      1.909506623157e-04 -3.388660283649e-05  2.315290984180e-06
     7     -9.201901683360e-06  1.408112739218e-06 -6.069498647130e-08
     8      1.865212152535e-07 -1.872002189577e-08 -1.479591373403e-09

    E Index         6                   7                   8
  T Index
     0     -1.199883122444e-03  7.929882485919e-05 -1.987990204346e-06
     1      4.465865599601e-04 -5.004811416214e-05  1.512094392826e-06
     2      5.950227580914e-04 -2.787837758738e-05  5.190549973795e-07
     3     -2.984004616508e-04  1.902451334721e-05 -4.579503385483e-07
     4      4.481020441245e-05 -3.425924289459e-06  9.026683813135e-08
     5     -2.146946788021e-06  2.383193769092e-07 -6.906305571460e-09
     6      6.088037548996e-09 -7.326969450051e-09  2.239693051242e-10
     7     -4.353244789583e-09  4.457527394302e-10 -9.398012612903e-12
     8      3.962791753244e-10 -2.513406814921e-11  5.068098237861e-13

     Error  8.03e-04 (B)
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 5.2.2 $   He^+ + H_2 \rightarrow He + H^+$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -3.617851314340e+01  8.245563741195e-01  1.415890461293e-01
     1      6.564887398262e-01 -3.337749950700e-01 -1.008073891739e-03
     2      9.531332794256e-02 -1.931877094955e-02 -2.177569825223e-02
     3     -1.790261298028e-02  2.362156898359e-02  2.481269859100e-03
     4      7.873069533268e-03  2.305021543232e-05  1.062397303161e-03
     5      1.625577954098e-03 -1.341341170672e-03 -2.453799729668e-04
     6     -6.243925896235e-04  2.389932224800e-04  1.310149299938e-05
     7      5.723897329155e-05 -1.662664310436e-05  4.255519558344e-07
     8     -1.690364064992e-06  4.200646087287e-07 -3.882714153340e-08

    E Index         3                   4                   5
  T Index
     0     -5.245109545409e-02  2.574263879790e-03  5.081113179086e-03
     1      2.353864809890e-02 -8.611685556552e-04 -1.235953005371e-03
     2      6.296784545643e-03  8.056466799286e-04 -4.422528088809e-04
     3     -3.194145659097e-03  5.097167452777e-05  1.492942136767e-04
     4     -2.226509858382e-04 -7.132717180757e-05  1.590997815012e-05
     5      2.171893645658e-04 -1.504822330128e-06 -7.627038293158e-06
     6     -3.205058255713e-05  3.153131057610e-06  5.374886487540e-07
     7      1.892187997659e-06 -3.671662723350e-07  1.240410469109e-08
     8     -3.981815711162e-08  1.257613148417e-08 -1.559147916406e-09

    E Index         6                   7                   8
  T Index
     0     -1.105146703191e-03  8.466844977067e-05 -2.264180150260e-06
     1      2.385360257195e-04 -1.708395525986e-05  4.375864733045e-07
     2      5.451070303994e-05 -2.660983244927e-06  4.244385976642e-08
     3     -2.350969502990e-05  1.328072187288e-06 -2.480965060631e-08
     4     -5.247303578452e-08 -1.381151133836e-07  6.646376709202e-09
     5      7.408427546841e-07 -8.825036538220e-10 -1.353868832823e-09
     6     -6.764350122786e-08 -8.407299219054e-10  1.978309478483e-10
     7     -5.125341539638e-10  2.770888875227e-10 -1.654942575020e-11
     8      1.599391141086e-10 -1.434870919386e-11  5.493012109985e-13

     Error  6.06e-04 (B)
\end{verbatim}\end{small}





\newpage
\subsection{
Reaction 5.2.3 $   He^+ + H_2 \rightarrow He + H^+ + H$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -3.569345457680e+01  5.467675953787e+00 -1.525452874272e+00
     1      6.602257860447e+00 -5.860473216356e+00  2.567792367148e+00
     2     -1.802030727618e+00  2.776708580765e+00 -1.456435131755e+00
     3      5.980682857428e-01 -7.669462419521e-01  3.877769522782e-01
     4     -1.515033763091e-01  1.355123344697e-01 -5.328079168644e-02
     5      2.273923829034e-02 -1.552431054752e-02  3.680122521552e-03
     6     -1.950876085219e-03  1.107193551999e-03 -9.861964956657e-05
     7      8.879641773477e-05 -4.427419374545e-05 -8.643444105803e-07
     8     -1.662550081283e-06  7.525447749722e-07  5.761680732896e-08

    E Index         3                   4                   5
  T Index
     0      7.645781657996e-01 -2.285145605072e-01  3.561471492616e-02
     1     -7.921692885504e-01  1.791134818786e-01 -2.709395158440e-02
     2      3.727025613660e-01 -5.373124189344e-02  4.827265290690e-03
     3     -9.180531536723e-02  9.188213414014e-03  8.930961476819e-05
     4      1.152256687649e-02 -1.182322907825e-03 -1.868126294929e-05
     5     -5.961207420320e-04  1.152911876232e-04 -1.321659022007e-05
     6     -7.612968632797e-06 -6.066035684733e-06  1.527361008857e-06
     7      1.816255353042e-06  4.628107113547e-08 -1.127225337804e-08
     8     -4.462116763253e-08  5.201413577832e-09 -2.441066078656e-09

    E Index         6                   7                   8
  T Index
     0     -3.040755662326e-03  1.357901348722e-04 -2.481641682718e-06
     1      2.495321136581e-03 -1.249516606345e-04  2.598469347617e-06
     2     -3.006881501965e-04  1.324810154101e-05 -3.023835422188e-07
     3     -9.701225760383e-05  7.510874054331e-06 -1.880555391455e-07
     4      1.703238064971e-05 -1.506318180829e-06  4.324855274434e-08
     5      1.049002267297e-07  7.987013573220e-08 -3.751370813720e-09
     6     -4.649027875076e-08 -8.266614643058e-09  4.561224301361e-10
     7     -9.674327862739e-09  1.432037876831e-09 -5.371138414560e-11
     8      6.786765390955e-10 -6.724210849363e-11  2.191944328954e-12

     Error  3.75e-04 (B)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 5.3.1 $   He^+ + He \rightarrow He + He^+$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -1.992795874184e+01  1.866121633782e-01  5.632774905403e-02
     1      2.342319832717e-01 -1.085479286023e-01 -5.796164637185e-03
     2      5.150488618567e-02  5.502643799842e-03 -1.070448355458e-02
     3     -4.457831664145e-03  6.751016280248e-03  1.348104812381e-03
     4     -1.543592188979e-03 -9.368501420643e-04  6.678034019800e-04
     5      3.127935819690e-04 -1.564547327374e-04 -1.638591652038e-04
     6     -1.478649318411e-05  4.454044051200e-05  1.091423551219e-05
     7     -4.796924334410e-07 -3.559977035839e-06  1.429006251276e-08
     8      3.623344342191e-08  9.673665606073e-08 -1.626046817162e-08

    E Index         3                   4                   5
  T Index
     0     -1.523524839309e-03 -2.153750537851e-03  3.308881419986e-04
     1      7.964340512260e-03 -2.259674261582e-04 -3.444207072047e-04
     2     -2.811049856343e-04  8.802921038196e-04 -1.198248793959e-04
     3     -1.009960297392e-03 -2.397230757181e-05  5.675989835329e-05
     4      1.271484361215e-04 -7.802314691135e-05  5.096915155186e-06
     5      2.743635453507e-05  1.364264736037e-05 -3.146182664420e-06
     6     -6.757942983709e-06 -3.524476702306e-07  2.858958575343e-07
     7      4.890540879010e-07 -6.293604516614e-08 -2.702231414235e-09
     8     -1.188613673713e-08  3.383446775161e-09 -3.684509743141e-10

    E Index         6                   7                   8
  T Index
     0     -1.293912998397e-05 -4.067520041201e-07  2.451185017055e-08
     1      6.164032099379e-05 -4.156975252360e-06  1.009896955766e-07
     2     -7.766013174537e-07  9.213287306897e-07 -4.014244306169e-08
     3     -8.581799112319e-06  4.932159877322e-07 -9.746139175914e-09
     4      1.122093772403e-06 -1.600545758983e-07  5.662679103625e-09
     5      9.721160837100e-08  1.677569938034e-08 -9.661966135256e-10
     6     -1.739320039203e-08 -1.179041806243e-09  9.352212060009e-11
     7      5.123073994873e-11  9.702183602739e-11 -5.755013542991e-12
     8      3.976640871840e-11 -4.096335085504e-12  1.667878217006e-13

     Error  2.36e-05 (A)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 5.3.2 $   He^+ + He \rightarrow He^+ + He^+ + e$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -6.749257304678e+01  3.080627051012e+01 -1.145813141153e+01
     1      4.329467261355e+01 -4.031602483159e+01  1.707905481142e+01
     2     -2.016026525056e+01  2.231984392732e+01 -1.017738982563e+01
     3      5.878320131150e+00 -6.882901423348e+00  3.201825080229e+00
     4     -1.137799010228e+00  1.302313958330e+00 -5.884044412402e-01
     5      1.450552810169e-01 -1.555507288279e-01  6.537275456166e-02
     6     -1.155793628115e-02  1.147650951410e-02 -4.329368714852e-03
     7      5.167930765975e-04 -4.781324647004e-04  1.576230053609e-04
     8     -9.839244996808e-06  8.600494351291e-06 -2.434988045802e-06

    E Index         3                   4                   5
  T Index
     0      3.388015690088e+00 -7.536552992052e-01  1.094516886818e-01
     1     -4.478579850964e+00  8.066021028840e-01 -9.979059856890e-02
     2      2.509824455963e+00 -3.656980663805e-01  3.191586604783e-02
     3     -7.552669555755e-01  9.255840851869e-02 -4.641142473768e-03
     4      1.311191744239e-01 -1.402143172466e-02  3.427843990627e-04
     5     -1.323051154888e-02  1.229786796421e-03 -2.028911469770e-05
     6      7.369414642692e-04 -5.269558335123e-05  1.766303852396e-06
     7     -1.928032791874e-05  3.603057782872e-07 -1.010518517671e-07
     8      1.339321812560e-07  3.028039050683e-08  1.838236320858e-09

    E Index         6                   7                   8
  T Index
     0     -9.463880450938e-03  4.398620168160e-04 -8.450244877636e-06
     1      7.955955791002e-03 -3.617178669983e-04  7.048366766523e-06
     2     -1.586656930186e-03  3.830211108983e-05 -2.609071874454e-07
     3     -1.294999476918e-04  2.388282840962e-05 -7.277202967312e-07
     4      6.774806939936e-05 -6.211048957431e-06  1.613570924718e-07
     5     -4.743973580278e-06  3.064327230164e-07 -4.853224348333e-09
     6     -3.419422565839e-07  4.593362543917e-08 -1.743858127735e-09
     7      5.170772455352e-08 -5.600340502767e-09  1.859063429189e-10
     8     -1.602801532247e-09  1.701252086315e-10 -5.520060744854e-12

     Error  1.35e-03 (C)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 6.1.1 $   He^{++} + H(1s) \rightarrow He^{++} + H(2p)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -3.128291192763e+01 -3.861939808947e-01 -2.544645152942e+00
     1     -6.826991894490e-01 -8.408347453138e-01  2.629943082927e-01
     2     -1.441334316248e+00  1.422092876991e-01  2.002181867767e-01
     3      3.169981863524e-01  1.363426173469e-01 -3.622433372588e-02
     4      1.440567980361e-01 -5.023547473715e-02 -2.472425668256e-03
     5     -5.309434904043e-02  6.625411757408e-03  1.347168808606e-03
     6      6.713712881021e-03 -3.657613813881e-04 -1.801819884810e-04
     7     -3.836344721605e-04  4.833466842639e-06  1.173107765224e-05
     8      8.388799849538e-06  1.548286845930e-07 -3.101524382401e-07

    E Index         3                   4                   5
  T Index
     0      4.669451368190e-01  2.917550661840e-01 -1.053780859061e-01
     1      9.881934763967e-02 -5.354197329704e-02  9.617629874772e-03
     2     -2.373167102469e-02 -1.943544641502e-02  6.728262805201e-03
     3     -2.125279295018e-02  8.196892532228e-03 -1.126751334420e-03
     4      5.090021728980e-03 -1.140089320112e-03  6.794493424970e-05
     5     -8.841712146365e-05  1.628036645708e-05 -8.948432185115e-06
     6     -6.309125180824e-05  1.390057420949e-05  5.519228022295e-07
     7      5.917408932712e-06 -1.490516597840e-06  5.820616731175e-08
     8     -1.596933841423e-07  4.769562622033e-08 -4.561904992676e-09

    E Index         6                   7                   8
  T Index
     0      1.364529328613e-02 -8.022046090155e-04  1.802849723372e-05
     1     -8.611117374892e-04  3.908664672328e-05 -7.212446215523e-07
     2     -9.041409091166e-04  5.666864142514e-05 -1.373057978697e-06
     3      7.645412457648e-05 -2.667684868645e-06  4.124172622729e-08
     4      7.368858127714e-06 -1.106305479253e-06  3.817455135007e-08
     5      5.678884593513e-07  4.642154492296e-08 -3.598042180209e-09
     6     -1.911269421448e-07  6.044313534001e-09  1.456318833459e-10
     7      3.639779928913e-09  6.910541467229e-11 -2.002452819345e-11
     8      3.328417422480e-10 -2.908652620490e-11  1.180447220494e-12

     Error  9.47e-04 (B)
\end{verbatim}\end{small}

A more extensive analytic formula for all $n >= 2$ is given in the text.




\newpage
\subsection{
Reaction 6.1.3 $   He^{++} + H(1s) \rightarrow He^{++} + H^+ + e$}

\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
       0    -3.213525339461e+01  4.048855987534e-01 -1.459217274977e+00
       1     8.616833916021e-01 -6.950245301215e-01 -5.645946950077e-01
       2    -1.516319957636e+00 -3.812512076134e-01  1.893299195739e-01
       3     1.006874043269e-01  2.037666264960e-01  2.977523227454e-02
       4     1.821009470616e-01 -1.888567920879e-03 -1.257914490683e-02
       5    -5.204900520164e-02 -1.011975370629e-02  1.459518537491e-03
       6     6.024060604719e-03  1.811281409653e-03 -1.071747691134e-04
       7    -3.279965879464e-04 -1.255314364414e-04  6.740808642651e-06
       8     6.955537637694e-06  3.158339223563e-06 -2.201431842876e-07

    E Index         3                   4                   5
  T Index
       0     1.832446087964e-01  1.820448886287e-01 -5.894612068336e-02
       1     1.997861354267e-01  2.296013792400e-02 -1.598128574471e-02
       2     2.287526434742e-02 -2.230595108739e-02  5.497523259018e-03
       3    -3.596233294198e-02  4.420728440672e-03  3.823858799635e-04
       4     3.554216072576e-03 -5.852198392288e-04 -1.045811648109e-05
       5     8.588876790382e-04  2.884916307632e-06 -3.389979591571e-05
       6    -1.914502607375e-04  1.361700778479e-05  3.642721103256e-06
       7     1.338794701145e-05 -1.635502392200e-06 -3.684855814169e-08
       8    -3.236734300402e-07  5.702927636593e-08 -4.938860692978e-09

    E Index         6                   7                   8
  T Index
       0     7.308767351095e-03 -4.181939938771e-04  9.207950478799e-06
       1     2.380832450865e-03 -1.504225027785e-04  3.547002873170e-06
       2    -6.993554812224e-04  4.516232482147e-05 -1.154715783315e-06
       3    -1.099529103897e-04  7.543892418062e-06 -1.708252421708e-07
       4     1.672568631267e-05 -1.836430836869e-06  6.080236805727e-08
       5     2.793668955085e-06  3.838407710178e-08 -6.689521714938e-09
       6    -3.804617509593e-07 -2.464497412799e-09  8.281161472560e-10
       7     5.704885906583e-10  1.543017124482e-09 -8.445486242553e-11
       8     7.699246994125e-10 -8.580250216262e-11  3.189523199623e-12

    Error 1.32e-03
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 6.1.6 $   He^{++} + H \rightarrow He^+(n=2) + H^+$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -2.684068918587e+01  1.077159851869e+00  1.611434095003e-01
     1      5.117541237230e-01 -3.292088112707e-01  4.193651221864e-02
     2      1.598500363509e-01 -3.812957840397e-02 -2.103399170458e-02
     3      1.228188346785e-02  1.765620781249e-02 -4.556545487291e-03
     4     -4.554467900719e-03  9.457132816015e-04  1.645608151050e-03
     5     -2.778583050511e-04 -7.305848198936e-04  4.612991944463e-05
     6      1.538644839183e-04  8.140980182115e-05 -4.793549304493e-05
     7     -1.499611384855e-05 -3.278119258256e-06  4.727047352918e-06
     8      4.697369923421e-07  3.332532647980e-08 -1.433575769997e-07

    E Index         3                   4                   5
  T Index
     0     -1.941671951055e-02 -3.364587603920e-03  1.137572625288e-03
     1      1.365931518647e-02 -3.060504283824e-03 -2.183962062545e-04
     2      5.585565653003e-03  7.325879113415e-04 -3.247877168930e-04
     3     -1.963806169076e-03  5.344561040129e-04  1.955747622998e-05
     4     -2.070478545640e-04 -1.384142733303e-04  3.281664341316e-05
     5      9.376080341880e-05 -4.104939830509e-06 -4.823335474719e-06
     6     -6.580665188724e-06  3.695002531601e-06 -2.170325944322e-07
     7     -8.828451438638e-08 -3.495383517796e-07  6.589695469087e-08
     8      1.452542457751e-08  1.021940844352e-08 -2.746221662026e-09

    E Index         6                   7                   8
  T Index
     0     -1.030059621084e-04  1.662587903156e-06  9.868838320179e-08
     1      1.038012581189e-04 -9.397899971402e-06  2.755750977475e-07
     2      3.172192984549e-05 -9.448677346635e-07 -3.817181255094e-09
     3     -1.514747820761e-05  1.426520725713e-06 -4.189371841853e-08
     4     -1.906464376446e-06 -4.474317916254e-08  4.942196257155e-09
     5      7.911914689813e-07 -4.216279314031e-08  6.314000693621e-10
     6     -3.184743031465e-08  3.644605422841e-09 -9.468908601909e-11
     7     -4.423644969643e-09  9.850791365204e-11  1.012931336353e-13
     8      2.722901729050e-10 -1.217986052601e-11  2.087076950595e-13

     Error  3.45e-04 (B)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 6.2.1 $   He^{++} + H_2 \rightarrow He^{++} + H_2^+(v) + e$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -3.740458528875e+01  4.819839382288e+00 -1.368722314416e+00
     1      3.697794623317e+00 -4.260575420078e+00  2.274586443382e+00
     2     -1.952883135699e-01  1.519624000877e+00 -1.186623344815e+00
     3      4.006262224030e-02 -2.914307027385e-01  2.640808145769e-01
     4     -4.786632316714e-02  3.732741697654e-02 -2.125640108014e-02
     5      1.435334952996e-02 -4.126872601223e-03 -1.316704448334e-03
     6     -1.857371914077e-03  3.915654055393e-04  3.686192037472e-04
     7      1.126777142893e-04 -2.328456641412e-05 -2.488855854519e-05
     8     -2.637987783791e-06  5.796033701332e-07  5.770496917262e-07

    E Index         3                   4                   5
  T Index
     0      5.415964848279e-01 -1.558092591583e-01  2.673033645460e-02
     1     -7.477112914979e-01  1.630231019898e-01 -2.322732220110e-02
     2      3.996652574630e-01 -7.388600606929e-02  8.214102149542e-03
     3     -9.703573952883e-02  1.783463570481e-02 -1.705433511392e-03
     4      8.833454031367e-03 -2.009464031032e-03  2.249935053360e-04
     5      5.248086049074e-04 -8.919967388651e-06 -1.246262891020e-05
     6     -1.737291298205e-04  2.577341999196e-05 -9.482137841850e-07
     7      1.300558673415e-05 -2.344702491575e-06  1.629428614542e-07
     8     -3.314156416545e-07  6.741539632029e-08 -5.955349313768e-09

    E Index         6                   7                   8
  T Index
     0     -2.578884501918e-03  1.294681717674e-04 -2.635783475569e-06
     1      2.040440748140e-03 -9.909710584927e-05  2.022083060567e-06
     2     -5.623626152450e-04  2.244646297525e-05 -4.065894891850e-07
     3      7.664104809530e-05 -8.191992528308e-07 -2.753294486929e-08
     4     -9.861657413217e-06 -9.995859937832e-08  1.424254131071e-08
     5      1.395191641953e-06 -3.685926734937e-08 -5.729382287379e-10
     6     -9.379121901004e-08  7.777171419994e-09 -1.213248180319e-10
     7     -2.275396327537e-10 -4.097026715756e-10  1.086349587424e-11
     8      1.692734428835e-10  4.442825612279e-12 -2.196742224277e-13

     Error  1.95e-04 (A)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 6.3.1 $   He^{++} + He \rightarrow He + He^{++}$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -2.087067966395e+01  1.770710917672e-01  5.286663352724e-02
     1      2.094653607929e-01 -1.035630036136e-01 -1.587484833047e-03
     2      4.515569927112e-02  7.753021609986e-03 -1.172352137681e-02
     3     -2.156818929353e-03  5.844613611271e-03  1.584520908151e-03
     4     -1.034417290024e-03 -9.988691720266e-04  6.430330809960e-04
     5      6.711410038952e-05 -9.039725081170e-05 -1.686928979307e-04
     6      1.634228365980e-05  3.360212044374e-05  1.244878523706e-05
     7     -2.018162243333e-06 -2.811596499823e-06 -1.289872750639e-07
     8      5.700761275390e-08  7.785762968811e-08 -1.168383579394e-08

    E Index         3                   4                   5
  T Index
     0     -4.108533645663e-03 -1.682325393036e-03  6.311322867200e-04
     1      6.980778548791e-03 -4.701965411677e-04 -2.345754812673e-04
     2      7.248911771056e-05  8.809460604163e-04 -1.426429587991e-04
     3     -1.074296069145e-03 -1.654629083347e-05  5.761893046505e-05
     4      1.311854988163e-04 -7.851442095351e-05  5.422244523002e-06
     5      2.782958218572e-05  1.353549005040e-05 -3.148005712744e-06
     6     -6.878943315863e-06 -3.391029687238e-07  2.812067777116e-07
     7      5.026743092262e-07 -6.291522264312e-08 -2.775917122056e-09
     8     -1.243441979051e-08  3.348779288410e-09 -3.430378749002e-10

    E Index         6                   7                   8
  T Index
     0     -1.034343472222e-04  8.284373934314e-06 -2.585107151364e-07
     1      4.656851963845e-05 -3.237799181386e-06  7.973037168095e-08
     2      3.719681370598e-06  5.772787018529e-07 -3.063528285547e-08
     3     -8.884055251880e-06  5.210682232168e-07 -1.062878498510e-08
     4      1.051027365170e-06 -1.540544793432e-07  5.483293214541e-09
     5      1.019425830844e-07  1.607622514801e-08 -9.352273349479e-10
     6     -1.692119208451e-08 -1.156062045162e-09  9.051243592979e-11
     7      8.794108865463e-11  8.904209111206e-11 -5.320379447337e-12
     8      3.429943174964e-11 -3.505937279725e-12  1.434656878037e-13

     Error  1.09e-04 (A)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 6.3.2 $   He^{++} + He \rightarrow He^{++} + He^+ + e$}

\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
       0    -3.357512088469e+01  2.481002270207e-01 -2.844754225626e-01
       1     2.132558452382e-01 -2.898782569957e-02 -8.859152207456e-02
       2    -7.629285367047e-01 -1.246031034296e-02  4.339076002927e-02
       3     5.899289086465e-02  3.450829479956e-03  1.171516743657e-02
       4     9.617944830667e-02  8.115543683934e-04 -8.351029524143e-03
       5    -2.754369102041e-02 -5.252894338980e-04  1.845370884466e-03
       6     3.193662877844e-03  9.140552891498e-05 -2.084303350442e-04
       7    -1.743435861477e-04 -6.732493173329e-06  1.209578227317e-05
       8     3.702563187159e-06  1.817766164959e-07 -2.844186742354e-07

    E Index         3                   4                   5
  T Index
       0    -5.040226778288e-02  3.354002274183e-02 -1.866620628241e-03
       1     1.729393805563e-02  4.254520286926e-03 -1.601440080094e-03
       2    -3.393002840651e-03  1.091192986540e-03 -4.407674396150e-04
       3    -1.741588094600e-03 -1.275836278696e-03  3.728086620067e-04
       4     1.074669748613e-03  1.010631022949e-04 -4.311397774907e-05
       5    -2.123309981019e-04  2.130784765152e-05 -3.112264677191e-06
       6     1.979855424701e-05 -3.124685666404e-06  7.997641396203e-07
       7    -8.939845877979e-07  9.995018170226e-08 -4.204213158284e-08
       8     1.584012353330e-08  7.506298931854e-10  5.227401148548e-10

    E Index         6                   7                   8
  T Index
       0    -4.168527021261e-04  5.230828266632e-05 -1.675138710355e-06
       1     1.850932900121e-04 -9.312584153371e-06  1.726529087665e-07
       2     5.983672818341e-05 -3.329152402921e-06  6.553879080128e-08
       3    -3.777955894029e-05  1.581526045462e-06 -2.076968820260e-08
       4     5.700910741004e-06 -3.693703626455e-07  9.504432686918e-09
       5    -1.055200072961e-07  4.925799326252e-08 -2.289228094874e-09
       6    -4.220795463450e-08 -3.412218769390e-09  2.463341794395e-10
       7     3.190991837665e-09  1.145196210456e-10 -1.210616102483e-11
       8    -5.846914988817e-11 -1.673892090785e-12  2.258466544149e-13

    Error 8.04e-05
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 7.2.1 $   p + H^- \rightarrow p + H + e$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -5.820131282154e+01 -4.418295075826e-01  1.273789037973e+00
     1      7.921427713311e+00  4.771816683717e-01 -3.122978202046e-02
     2      2.729868361636e+00 -1.003942758610e+00 -1.263868632256e-01
     3     -1.702566612373e+00  5.785696129573e-01 -4.732954195668e-03
     4      3.973780588321e-01 -1.478528997647e-01  1.158502169314e-02
     5     -4.870825299595e-02  1.969477666027e-02 -2.123634522072e-03
     6      3.236718833237e-03 -1.407103305708e-03  1.493109405401e-04
     7     -1.084755026674e-04  4.998674210260e-05 -3.376656915211e-06
     8      1.396208954849e-06 -6.620153170835e-07 -2.627392847530e-08

    E Index         3                   4                   5
  T Index
     0      1.527207940425e+00 -7.536424630223e-01  1.439466388013e-01
     1     -7.888775801865e-01  3.288138016027e-01 -5.784931758231e-02
     2      1.435920376766e-01 -3.733709098912e-02  5.120254991289e-03
     3     -1.244717631219e-02 -8.125405039157e-04  5.304019788343e-04
     4      1.217335613258e-03  1.744838040179e-05 -6.302890522722e-05
     5     -1.652073669891e-04  7.132512952865e-05 -7.166374800128e-06
     6      9.210684173413e-06 -6.258784083367e-06  9.976414798586e-07
     7      1.518653946410e-07 -5.285593274691e-09 -1.618019219414e-08
     8     -1.935457835554e-08  1.017637467796e-08 -9.682272656474e-10

    E Index         6                   7                   8
  T Index
     0     -1.390229840299e-02  6.747109860492e-04 -1.308869018310e-05
     1      5.240004832333e-03 -2.411772118083e-04  4.478567757510e-06
     2     -4.068737543562e-04  1.774870848760e-05 -3.291488867455e-07
     3     -5.311181815494e-05  1.788414701774e-06 -8.455601658664e-09
     4      8.167685239892e-06 -4.004411200193e-07  6.703922705847e-09
     5     -2.654278454630e-08  4.575052609148e-08 -1.985275499541e-09
     6     -3.804512852913e-08 -3.484409058380e-09  2.245422239581e-10
     7      1.247165282825e-09  1.121719496535e-10 -9.065883281241e-12
     8      1.821912346903e-11 -3.038200599319e-13  7.144344819156e-14

     Error  5.01e-04 (B)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 7.2.2 $   p + H^- \rightarrow H(n=2) + H(1s)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -2.009840732855e+01  2.945311019841e-01  6.747596918807e-02
     1      5.206452202262e-01 -1.774365164859e-01 -1.065938217336e-02
     2      1.523257622741e-01  9.772247255291e-03 -1.671909485907e-02
     3      2.453955732425e-02  1.021908459294e-02  2.438519414977e-03
     4     -6.480928896115e-03 -1.242525298942e-03  1.015757625636e-03
     5     -1.975172853627e-03 -2.672450143654e-04 -2.328706013052e-04
     6      5.435998708470e-04  6.631970392344e-05  9.462039923651e-06
     7     -4.472026617583e-05 -4.970789806324e-06  8.120583670855e-07
     8      1.251083879369e-06  1.282034444684e-07 -5.184939728768e-08

    E Index         3                   4                   5
  T Index
     0      5.281180712235e-02  1.853075990865e-03 -5.214983547816e-03
     1      8.534567745269e-03 -2.015642900438e-04 -1.875060648516e-04
     2     -2.499942893968e-03  1.198848516168e-03  5.837864405510e-05
     3     -2.108370566003e-03 -8.621652320901e-05  1.290879800077e-04
     4      2.995184004525e-04 -1.140789673124e-04 -3.180399692215e-06
     5      7.043847826279e-05  2.122349981883e-05 -5.763532119771e-06
     6     -1.718398943085e-05 -4.277037568906e-07  6.826848999792e-07
     7      1.233759362312e-06 -1.215395288499e-07 -1.469076279075e-08
     8     -2.971450478059e-08  6.283704324845e-09 -5.567626168906e-10

    E Index         6                   7                   8
  T Index
     0      9.106146930077e-04 -6.179659482888e-05  1.518671797497e-06
     1      2.166774591691e-05 -7.154959806623e-07  3.341578770132e-10
     2     -4.532942700372e-05  4.566989804119e-06 -1.425164722921e-07
     3     -1.884472793311e-05  1.063634324920e-06 -2.098030063540e-08
     4      3.691852062324e-06 -3.822422186488e-07  1.207671501711e-08
     5      2.097347343793e-07  2.744685327018e-08 -1.629591430987e-09
     6     -4.961730812520e-08 -1.574040495320e-09  1.647011369051e-10
     7      3.375069155440e-10  2.528285218582e-10 -1.407865804427e-11
     8      1.064408722092e-10 -1.331534803275e-11  5.209521592110e-13

     Error  9.91e-04 (B)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 7.2.3 $   p + H^- \rightarrow H(n=3) + H(1s)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -1.708169812006e+01 -1.310597645979e-01 -2.016054239030e-02
     1     -1.098675942533e-01  8.969312492472e-02 -1.001934703492e-02
     2     -2.424453483379e-02 -7.668315551548e-03  1.118173178217e-02
     3      8.542779858410e-03 -5.728980402850e-03 -1.374395114022e-03
     4      7.546932951352e-04  1.282616012621e-03 -5.242666757105e-04
     5     -4.460619874465e-04 -6.407045514906e-06  1.627184981581e-04
     6      5.689498536274e-05 -2.131881433227e-05 -1.769191253093e-05
     7     -3.155262052836e-06  2.122673795556e-06  8.581432797541e-07
     8      6.668405706096e-08 -6.364778304060e-08 -1.541736278733e-08

    E Index         3                   4                   5
  T Index
     0      8.964903471778e-03  6.442616660302e-04 -4.660365148908e-04
     1     -5.890144705724e-03  1.384217913807e-03  1.779238684618e-05
     2     -1.257344700418e-03 -6.729866629037e-04  2.054778233488e-04
     3      1.029305874211e-03 -5.123704753586e-05 -4.411992401625e-05
     4     -1.091263631596e-04  5.650953446193e-05 -4.197841783909e-06
     5     -2.000801209847e-05 -7.808493438675e-06  1.772154859168e-06
     6      5.122279431664e-06  1.659419345620e-07 -1.384458129532e-07
     7     -3.925060139873e-07  3.050794133610e-08  1.377776084081e-09
     8      1.041255114173e-08 -1.512980436877e-09  1.332411705243e-10

    E Index         6                   7                   8
  T Index
     0      6.370816676015e-05 -3.782683702643e-06  8.609188888839e-08
     1     -3.013382774299e-05  2.954660809114e-06 -8.931384100116e-08
     2     -2.315115305809e-05  1.190025285551e-06 -2.326585429997e-08
     3      9.037770228405e-06 -6.768442086761e-07  1.812120616012e-08
     4     -5.411932096608e-07  8.415741816738e-08 -2.978331246224e-09
     5     -9.596489328029e-08 -2.035464169710e-09  2.147130564694e-10
     6      1.037345875045e-08  1.399052051710e-11 -1.531475772097e-11
     7     -1.232733782717e-11 -2.816042650663e-11  1.402510343416e-12
     8     -1.732775970924e-11  1.621564942355e-12 -5.400526340307e-14

     Error  1.23e-05 (A)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 7.3.1 $   H^- + H(1s) \rightarrow H(1s) + H^-(1s)$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -2.446549884269e+01  2.282921659881e-01  6.932259053475e-02
     1      2.634131317967e-01 -1.250144616925e-01 -6.564104931024e-03
     2      5.739515657001e-02  1.401243736042e-02 -1.370769740386e-02
     3     -3.083480423288e-03  5.762622642079e-03  1.641868158109e-03
     4     -2.155324535935e-03 -1.741051127171e-03  8.917026172582e-04
     5      7.685873715096e-05  1.906770746936e-04 -1.497853929999e-04
     6      8.087530514888e-05 -1.359658266200e-05 -9.370283912465e-06
     7     -1.201616211995e-05  9.404454583406e-07  2.798537842077e-06
     8      4.838440948297e-07 -3.591774662931e-08 -1.280487901835e-07

    E Index         3                   4                   5
  T Index
     0     -1.460337641019e-02 -1.148284334186e-03  1.888298450789e-03
     1      1.034238130425e-02 -1.160529409915e-04 -6.554701103747e-04
     2     -1.631710543681e-03  1.504466063314e-03 -1.492959802239e-04
     3     -1.158102233053e-03 -1.500016779601e-04  1.333539925260e-04
     4      3.323370760750e-04 -1.435851350450e-04  8.827631680416e-08
     5     -3.852538752998e-05  3.638688148903e-05 -5.971816791477e-06
     6      5.240710288295e-06 -2.673369866914e-06  5.756054051438e-07
     7     -6.106253322733e-07  3.599735795836e-09  9.761611536846e-09
     8      2.617375100182e-08  4.349591668816e-09 -1.894102703596e-09

    E Index         6                   7                   8
  T Index
     0     -5.048413591687e-04  5.442003557424e-05 -2.119938012240e-06
     1      1.312358086468e-04 -1.025406435973e-05  2.930874591340e-07
     2     -1.535700264182e-05  3.028402252514e-06 -1.223371130502e-07
     3     -2.335914959456e-05  1.720243174222e-06 -4.737046201928e-08
     4      4.695207254022e-06 -5.743305788389e-07  2.072162215301e-08
     5      1.312086122421e-07  3.381300299186e-08 -1.846446053198e-09
     6     -4.928206213204e-08  1.359692653300e-09  7.095887472625e-12
     7     -9.446355577370e-10  1.324857300193e-11  1.212840280599e-12
     8      2.250181340057e-10 -1.085735441577e-11  1.640670966131e-13

     Error  2.16e-03 (C)
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 7.3.2a $  H^- + H \rightarrow H_2^-(\Sigma_g) \rightarrow H + H + e$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -2.060381621916e+01  5.309100960058e-01  1.392829074695e-01
     1      7.588123099350e-01 -3.576940273729e-01 -1.987510302857e-02
     2      6.731769657604e-02  4.484233894719e-02 -2.733782810986e-02
     3     -2.921355392156e-02  1.482283181415e-02  5.906948645836e-03
     4     -8.146699299025e-04 -3.643845685721e-03  9.773942210504e-04
     5      1.155948959822e-03 -2.087103325148e-05 -3.907609724337e-04
     6     -1.581407518895e-04  6.895932849865e-05  4.008820591876e-05
     7      8.836837813921e-06 -6.605304596227e-06 -1.507273917480e-06
     8     -1.822275438433e-07  1.936335851996e-07  1.172227886690e-08

    E Index         3                   4                   5
  T Index
     0     -2.102641710803e-02 -6.781349963009e-03  2.016215809719e-03
     1      2.668242766164e-02 -3.261461848245e-04 -1.366958646410e-03
     2     -1.554648294430e-03  2.123755455543e-03 -2.773916489042e-04
     3     -2.598822894319e-03 -1.875799348857e-04  1.758361880894e-04
     4      4.600843838170e-04 -1.448878357902e-04 -1.060700155439e-06
     5      2.315526538554e-05  3.237966723085e-05 -5.841079752828e-06
     6     -1.092581698940e-05 -2.012024682441e-06  6.606514619140e-07
     7      8.757818250078e-07 -1.331205306048e-08 -1.679915115556e-08
     8     -2.240888951133e-08  3.415505655444e-09 -3.436228509229e-10

    E Index         6                   7                   8
  T Index
     0     -2.021191702941e-04  8.841314274130e-06 -1.379541011203e-07
     1      2.452687401131e-04 -1.698794209121e-05  4.269734144618e-07
     2      9.627819846149e-07  1.668014583065e-06 -7.372505366253e-08
     3     -2.636740402205e-05  1.616979349290e-06 -3.621463869178e-08
     4      3.717760767389e-06 -3.932211297595e-07  1.249308982925e-08
     5      1.129239553545e-07  3.349164498023e-08 -1.726363311444e-09
     6     -3.323645378786e-08 -2.310130864690e-09  1.678089205296e-10
     7      7.727272538571e-11  2.259701266295e-10 -1.191390422294e-11
     8      8.001148282982e-11 -9.879026759786e-12  3.844676704391e-13

     Error  7.20e-05 (A
\end{verbatim}\end{small}






\newpage
\subsection{
Reaction 7.3.2b $  H^- + H \rightarrow H_2^-(\Sigma_g) \rightarrow H_2 + e$}


\begin{small}\begin{verbatim}
    E Index         0                   1                   2
  T Index
     0     -2.010720050130e+01  9.270256057913e-02  4.064624494679e-02
     1      1.269636887793e-01 -4.008719210304e-02 -1.212200218053e-02
     2      3.912641450862e-02 -4.922699464361e-03 -2.358617965735e-03
     3      2.444823703314e-03  3.862828408110e-03  6.245030315710e-05
     4     -1.375395363511e-03  9.136383818175e-05  3.424787531975e-04
     5      7.705307936032e-06 -2.452524870403e-04 -4.618148515540e-05
     6      2.808922151936e-05  4.232400689568e-05 -2.685853929702e-06
     7     -2.890778521667e-06 -2.902579165065e-06  7.058422006406e-07
     8      8.872270416775e-08  7.252699730279e-08 -2.925937563766e-08

    E Index         3                   4                   5
  T Index
     0      4.009352818185e-03 -1.538314339134e-03  6.474680671630e-06
     1      4.382832251342e-03  5.808750658711e-04 -3.518386094650e-04
     2     -9.020736846330e-04  3.801661661405e-04  1.342533092878e-05
     3     -3.877053574415e-04 -3.173212632597e-05  2.768229470146e-05
     4      3.970724372076e-05 -4.033536057563e-05  2.837106654166e-06
     5      2.083693473819e-05  7.210478132956e-06 -2.015504293252e-06
     6     -4.253675760089e-06 -4.555400231697e-08  1.858779383984e-07
     7      2.828822067547e-07 -5.462822668312e-08 -6.645063119276e-10
     8     -6.263750441883e-09  2.637137895225e-09 -3.152813312676e-10

    E Index         6                   7                   8
  T Index
     0      2.652929923557e-05 -2.559456729654e-06  7.459443536792e-08
     1      4.949650860383e-05 -2.957539611478e-06  6.557962278545e-08
     2     -1.447007766306e-05  1.557308263715e-06 -5.100926653114e-08
     3     -3.314905595837e-06  1.239094303050e-07 -3.472887336273e-10
     4      6.818837404440e-07 -9.934681425484e-08  3.579429434382e-09
     5      6.344059934988e-08  1.253846512396e-08 -7.317167395513e-10
     6     -1.179832220191e-08 -9.932172729863e-10  7.663678877930e-11
     7     -5.638246638305e-11  8.392102689376e-11 -4.907260382466e-12
     8      3.426087000167e-11 -3.525203792329e-12  1.448748836700e-13

     Error  2.06e-05 (A)
\end{verbatim}\end{small}

\newpage

\section{H.8 : Fits for $\langle\sigma \cdot v \cdot E_p \rangle (T_b) \ [cm^3/s
\cdot eV]$}

$E_p$ is a relevant energy related to the process, e.g. it may be the kinetic energy of the impacting electron or ion in eV,
or the radiation energy loss per reaction, etc.
In the present section (newly added to this database by DR)
the energy weighted rate is a function of temperature [eV] of the
impacting electron or ion.

The general expression for this type of incident particle energy weighted
rate, vs. temperature of the first particle $A$ involved in the collision process
and in which the second particle $B$ is at rest, reads:

$\langle\sigma v_A E_{A}\rangle(T_A) = kT_A \cdot \langle\sigma v_A\rangle \cdot
\left(3/2 + \frac{d \ln \langle\sigma v_A\rangle}{d \ln(kT_A)}\right)$

\newpage

\subsection{
Reaction 2.1.8  $  e + H^+ \rightarrow H(1s) + hv $}
general formula for rate: see original text. Here:  fit to rate for recomb into
1s ground state.
Then: take only the first 2 coeffs and derive the corresponding electron energy rate.


Do not use: This is a poor approximation at higher Te, as it only captures the low Te
behaviour (b1 approx -0.5, h1 approx 0.5).



\begin{small}\begin{verbatim}
   h0 -2.96197012800e+01     h1  0.470220050000e+00    h2  0.000000000000e+00
   h3  0000000000000e+00     h4  0.000000000000e+00    h5  0.000000000000e+00
   h6  0.00000000000e+00     h7  0.000000000000e+00    h8  0.000000000000e+00
\end{verbatim}\end{small}

\subsection{
Reaction 2.2.14   $e + H_2^+(v) \rightarrow H(1s) + H^*(n)   (v=0-9, n \ge 2) $
}
The energy weighting in this rate coefficient is done with the kinetic energy of
impacting electron.
The fit should result in

$\langle\sigma v_e E_{elec}\rangle(T_e) \approx 0.89 ~kT_e ~\langle\sigma v_e\rangle$,

i.e. low energy electrons are preferred in this reaction, rather than the average electrons with $3/2~kT_e$


\begin{small}\begin{verbatim}
   h0 -1.682072926000e+01    h1  3.964351525300e-01    h2 -2.501012514300e-11
   h3  1.066503238000e-11    h4  2.724261514100e-12    h5 -2.120710160500e-12
   h6  4.248055273200e-13    h7 -3.653955751100e-14    h8  1.187177640600e-15

\end{verbatim}\end{small}
\newpage
\begin{thebibliography}{99}
\bibitem{kn:Janev87} R.K. Janev, B. Langer et al.,  Springer Series on Atoms+Plasmas,
                   Vol 4, 1987
\bibitem{kn:Reiter92} D. Reiter, P. Bogen, U. Samm, Journal Nuclear Materials, Vol 196-198, 1992, 1059-1064
\end{thebibliography}
\end{document}
